\documentclass{../../large}
\usepackage{../../ikhanchoi}


\begin{document}
\title{Geometry}
\author{Ikhan Choi}
\maketitle
\tableofcontents

\part{Classical geometry}
\chapter{Euclidean geometry}

\section{Plane geometry}
\section{Solid geometry}
\section{Axiomatization}

\chapter{Non-Euclidean geometry}
\section{Absolute geometry}
axioms 1 to 4
\section{Spherical and elliptic geometry}
axioms 2 and 4
\section{Hyperbolic geometry}
axiomes 1 to 4

Models of hyperbolic geometry (metric description)
Elementary figures
Isometries
Length, volume, angle

\chapter{Non-metric geometry}
\section{Ordered and incidence geometry}
axioms 1 and 2
\section{Affine and projective geometry}
axioms 1,2,5
\section{Conformal and inversive geometry}






\part{Smooth surfaces}
\chapter{Smooth manifolds}
\section{Local coordinates}

\section{Space curves}

\section{Space surfaces}

%         선형독립    벡터들이 한점에서 주어졌을 때 ->
%         선형독립    벡터장이 근방에서 주어졌을 때 -> 일반적으론 2차원에서만
%         선형독립 가환벡터장이 근방에서 주어졌을 때 -> n차원 다돼
%         선형독립    직교벡터들이 한점에서 주어졌을 때
%         선형독립    직교벡터장이 근방에서 주어졌을 때
%         선형독립 직교가환벡터장이 근방에서 주어졌을 때
%             -> 곡률의 선, 점근곡선, 측지좌표

% preimage theorem

Reparametrizations

\begin{thm}
Let $S$ be a regular surface.
Let $v,w$ be linearly independent tangent vectors in $T_pS$ for a point $p\in S$.
Then, $S$ admits a parametrization $\alpha$ such that $\alpha_x|_p=v$ and $\alpha_y|_p=w$.
\end{thm}
\begin{thm}
Let $X,Y$ be linearly independent tangent vector fields on a regular surface $S$.
Then, $S$ admits a parametrization $\alpha$ such that $\alpha_x|_p$ and $\alpha_y|_p$ are parallel to $X|_p,Y|_p$ respectively for each $p\in S$.
\end{thm}
\begin{thm}
Let $X,Y$ be linearly independent tangent vector fields on a regular surface $S$.
If $\pd_XY=\pd_YX$, then $S$ admits a parametrization $\alpha$ such that $\alpha_x|_p=X|_p$ and $\alpha_y|_p=Y|_p$ for each $p\in S$.
\end{thm}

Let $S$ be a regular surface embedded in $\R^3$.
The inner product on $T_pS$ induced from the standard inner product of $\R^3$ can be represented not only as a matrix
\[\mat{1&0&0\\0&1&0\\0&0&1}\]
in the basis $\{(1,0,0),(0,1,0),(0,0,1)\}\subset\R^3$, but also as a matrix
\[\mat{\<\alpha_x,\alpha_x\>&\<\alpha_x,\alpha_y\>\\\<\alpha_y,\alpha_x\>&\<\alpha_y,\alpha_y\>}\]
in the basis $\{\alpha_x|_p,\alpha_y|_p\}\subset T_pS$.

\begin{defn}
\emph{Metric coefficients}
\begin{alignat*}{2}
\<\alpha_x,\alpha_x\>&=:g_{11}&\qquad
\<\alpha_x,\alpha_y\>&=:g_{12}\\
\<\alpha_y,\alpha_x\>&=:g_{21}&
\<\alpha_y,\alpha_y\>&=:g_{22}
\end{alignat*}
\end{defn}

\begin{thm}[Normal coordinates]
...?
\end{thm}




\subsection*{Differentiation of tangent vectors}

\begin{defn}
Let $\alpha:U\to\R^3$ be a regular surface.
The \emph{Gauss map} or \emph{normal unit vector} $\nu:U\to\R^3$ is a vector field on $\alpha$ defined by:
\[\nu(x,y):=\frac{\alpha_x\times \alpha_y}{\|\alpha_x\times \alpha_y\|}(x,y).\]
The set of vector fields $\{\alpha_x|_p,\alpha_y|_p,\nu|_p\}$ forms a basis of $T_p\R^3$ at each point $p$ on $\alpha$.
The Gauss map is uniquely determined up to sign as $\alpha$ changes.
\end{defn}

\begin{defn}[Gauss formula, $\Gamma_{ij}^k$, $L_{ij}$]
Let $\alpha:U\to\R^3$ be a regular surface.
Define indexed families of smooth functions $\{\Gamma_{ij}^k\}_{i,j,k=1}^2$ and $\{L_{ij}\}_{i,j=1}^2$ by the Gauss formula
\begin{alignat*}{2}
\alpha_{xx}&=:\Gamma_{11}^1\alpha_x+\Gamma_{11}^2\alpha_y+L_{11}\nu,&\qquad
\alpha_{xy}&=:\Gamma_{12}^1\alpha_x+\Gamma_{12}^2\alpha_y+L_{12}\nu,\\
\alpha_{yx}&=:\Gamma_{21}^1\alpha_x+\Gamma_{21}^2\alpha_y+L_{21}\nu,&
\alpha_{yy}&=:\Gamma_{22}^1\alpha_x+\Gamma_{22}^2\alpha_y+L_{22}\nu.
\end{alignat*}
The \emph{Christoffel symbols} refer to eight functions $\{\Gamma_{ij}^k\}_{i,j,k=1}^2$.
The Christoffel symbols and $L_{ij}$ \emph{do depend} on $\alpha$.
\end{defn}
We can easily check the symmetry $\Gamma_{ij}^k=\Gamma_{ji}^k$ and $L_{ij}=L_{ji}$.
Also,
\begin{align*}
\pd_XY
&=X^i\pd_i(Y^j\alpha_j)\\
&=X^i(\pd_iY^k)\alpha_k+X^iY^j\pd_i\alpha_j\\
&=\left(X^i\pd_iY^k+X^iY^j\Gamma_{ij}^k\right)\alpha_k+X^iY^jL_{ij}\nu.
\end{align*}

% Examples


\subsection*{Differentiation of normal vector}

The partial derivative $\pd_X\nu$ is a tangent vector field since
\[\<\pd_X\nu,\nu\>=\frac12\pd_X\<\nu,\nu\>=0.\]
Therefore, we can define the following useful operator.
\begin{defn}
Let $S$ be a regular surface embedded in $\R^3$.
The \emph{shape operator} is $\cS:\fX(S)\to\fX(S)$ defined as
\[\cS(X):=-\pd_X\nu.\]
\end{defn}
\begin{prop}
The shape operator is self-adjoint, i.e. symmetric.
\end{prop}
\begin{pf}
Recall that $\pd_XY-\pd_YX$ is a tangent vector field.
Then,
\[\<X,\cS(Y)\>=\<X,-\pd_Y\nu\>=\<\pd_YX,\nu\>=\<\pd_XY,\nu\>=\<\cS(X),Y\>.\qedhere\]
\end{pf}

% The reason of minus sign in the shape operator.

\begin{thm}
Let $\alpha:U\to\R^3$ be a regular surface and $\cS$ be the shape operator.
Then $\cS$ has the coordinate representation
\[\cS=\mat{g_{11}&g_{12}\\g_{21}&g_{22}}^{-1}\mat{L_{11}&L_{12}\\L_{21}&L_{22}}\]
with respect to the frame $\{\alpha_x,\alpha_y\}$ for tangent spaces.
In other words, if we let $X=X^i\alpha_i$ and $\cS(X)=\cS(X)^j\alpha_j$, then
\[\mat{\cS(X)^1\\\cS(Y)^2}=\mat{g_{11}&g_{12}\\g_{21}&g_{22}}^{-1}\mat{L_{11}&L_{12}\\L_{21}&L_{22}}\mat{X^1\\X^2}.\]
\end{thm}
\begin{pf}
Let $\cS(X)^j=\cS_i^jX_i$.
Then,
\[g_{ik}X^i\cS_j^kY^j=\<X,\cS(Y)\>=\<\pd_XY,\nu\>=X^iY^jL_{ij}\]
implies $g_{ik}\,\cS_j^k=L_{ij}$.
\end{pf}

% principal curvature
% mean curvature, gaussian curvature



% curvature tensor?





















\chapter{Fundamental forms}

\section{Riemannian metrics}

\section{Gaussian curvatures}
Theorema egregium
surfaces of constant gaussian curvature

% 제1기본형식, 크리스토펠: 
% 모양 연산자, 제2기본형식: 바인가르텐 이퀘이션

% 가우스곡률
\begin{defn}
Let $\alpha:U\to\R^3$ be a regular surface.
\begin{gather*}
E:=\<\alpha_x,\alpha_x\>=g_{11},\qquad F:=\<\alpha_x,\alpha_y\>=g_{12},\qquad G:=\<\alpha_y,\alpha_y\>=g_{22},\\
L:=\<\alpha_{xx},\nu\>=L_{11},\qquad M:=\<\alpha_{xy},\nu\>=L_{12},\qquad N:=\<\alpha_{yy},\nu\>=L_{22}.
\end{gather*}
\end{defn}


\begin{cor}
We have $GM-FN=EM-FL$, and the \emph{Weingarten equations}:
\begin{align*}
\nu_x&=\frac{FM-GL}{EG-F^2}\alpha_x+\frac{FL-EM}{EG-F^2}\alpha_y,\\
\nu_y&=\frac{FN-GM}{EG-F^2}\alpha_x+\frac{FM-EN}{EG-F^2}\alpha_y.
\end{align*}
\end{cor}



\begin{thm}
\[\Gamma_{ij}^l=\frac12g^{kl}(g_{ik,j}-g_{ij,k}+g_{kj,i}).\]
\end{thm}

\[\frac12(\log g)_x=\Gamma_{11}^1.\]

\[\nu_x\times\nu_y=K\sqrt{\det g}\ \nu.\]
\[\alpha_x\times\alpha_y=\sqrt{\det g}\ \nu\]
\[\<\nu_x\times\nu_y,\alpha_x\times\alpha_y\>=\det\mat{\<\nu_x,\alpha_x\>&\<\nu_x,\alpha_y\>\\\<\nu_y,\alpha_x\>&\<\nu_y,\alpha_y\>}=\det\mat{-L&-M\\-M&-N}=K\det g\]











\begin{prb}[Gaussian curvature formula]
\begin{parts}
\item
In general,
\[K=\frac{LN-M^2}{EG-F^2}.\]
\item
For orthogonal coordinates such that $F\equiv0$,
\[K=-\frac1{2\sqrt{\det g}}\left((\frac1{\sqrt{\det g}}E_y)_y+(\frac1{\sqrt{\det g}}G_x)_x\right).\]
\item
For $f(x,y,z)=0$,
\[K=-\frac1{|\nabla f|^4}\mat[v]{0&\nabla f\\\nabla f^T&\Hess(f)},\]
where $\nabla f$ denotes the gradient $\nabla f=(f_x,f_y,f_z)$.
\item(Beltrami-Enneper) If $\tau$ is the torsion of an asymptotic curve, then
\[K=-\tau^2.\]
\item(Brioschi) $E,F,G$ describes $K$.
\end{parts}
\end{prb}

\begin{pf}
(a) Clear.

(b)
We have $GM=EM$ and
\[\nu_x=-\frac LE\alpha_x-\frac MG\alpha_y,\qquad\nu_y=-\frac ME\alpha_x-\frac NG\alpha_y.\]
\[\nu_x\times\nu_y=\frac{LN-M^2}{EG}\alpha_x\times\alpha_y\]
After curvature tensors...

\end{pf}



\begin{prb}[Computation of Gaussian curvatures]
\begin{parts}
\item
(Monge's patch)
For $(x,y,f(x,y))$,
\[K=\frac{f_{xx}f_{yy}-f_{xy}^2}{(1+f_x^2+f_y^2)^2}.\]

\item
(Surface of revolution).
Let $\gamma(t)=(r(t),z(t))$ be a plane curve with $r(t)>0$.
If $t\mapsto(r(t),z(t))$ is a unit-speed curve, then
\[K=-\frac{r''}r.\]

\item
(Models of hyperbolic planes)
\end{parts}
\end{prb}
\begin{pf}
(b)
Let
\[\alpha(\theta,t)=(r(t)\cos\theta,r(t)\sin\theta,z(t))\]
be a parametrization of a surface of revolution.
Then,
\begin{align*}
\alpha_\theta&=(-r(t)\sin\theta,r(t)\cos\theta,0)\\
\alpha_t&=(r'(t)\cos\theta,r'(t)\sin\theta,z'(t))\\
\nu&=\frac1{\sqrt{r'(t)^2+z'(t)^2}}(z'(t)\cos\theta,z'(t)\sin\theta,-r'(t)),
\end{align*}
and
\begin{align*}
\alpha_{\theta\theta}&=(-r(t)\cos\theta,-r(t)\sin\theta,0)\\
\alpha_{\theta t}&=(-r'(t)\sin\theta,-r'(t)\cos\theta,0)\\
\alpha_{tt}&=(r''(t)\cos\theta,r''(t)\sin\theta,z''(t)).
\end{align*}
Thus we have
\[E=r(t)^2,\quad F=0,\quad G=r'(t)^2+z'(t)^2,\]
and
\[L=-\frac{r(t)z'(t)}{\sqrt{r'(t)^2+z'(t)^2}},\quad M=0,\quad N=\frac{r''(t)z'(t)-r'(t)z''(t)}{\sqrt{r'(t)^2+z'(t)^2}}.\]
Therefore,
\[K=\frac{LN-M^2}{EG-F^2}=\frac{z'(r'z''-r''z')}{r(r'^2+z'^2)^2}.\]
In particular, if $t\mapsto(r(t),z(t))$ is a unit-speed curve, then
\[K=-\frac{r''}r.\]
\end{pf}


% asymptotic curve -> hyperbolic
% line of curvature -> non-umbilic

% minimal surface
% 	회전곡면
% asymptotic curve
% 	Beltrami-Enneper
% ruled surface
% developable surface


\begin{prb}[Local isomorphism]
Surfaces of the same constant Gaussian curvature are locally isomorphic.
\end{prb}
\begin{pf}
Let
\[\mat{\|\alpha_r\|^2&\<\alpha_r,\alpha_t\>\\\<\alpha_t,\alpha_r\>&\|\alpha_t\|^2}=\mat{1&0\\0&h(r,t)^2}\]
be the first fundamental form for a geodesic coordinate chart along a geodesic curve so that $\alpha_{tt}$ and $\alpha_{rr}$ are normal to the surface.
Then,
\[K=-\frac{h_{rr}}h\]
is constant.
Also, since
\[\frac12(h^2)_r+\<\alpha_r,\alpha_{tt}\>=\<\alpha_{rt},\alpha_t\>+\<\alpha_r,\alpha_{tt}\>=\<\alpha_r,\alpha_t\>_t=0\]
implies $h_r=0$ at $r=0$, the function $f:r\mapsto h(r,t)$ satisfies the following initial value problem
\[f_{rr}=-Kf,\quad f(0)=1,\quad f'(0)=0.\]
Therefore, $h$ is uniquely determined by $K$.
\end{pf}



\chapter{}



% Global theory of curves
%  Isoperimetric inequality
%  Four vertex theorem
%  Ovals

% Global theory of surfaces
%  Minimal surfaces
%  classification of compact surfaces?
%  Hilbert theorem

% Total curvatures
%  Fary-Milnor
%  Fenchel
%  Gauss-Bonnet, euler characteristic













\part{Riemann surfaces}

\chapter{Riemann-Roch theorem}

Let $X$ be a compact Riemann surface.
Consider a vector space $\cM^\times(X)\cup\{0\}$.

\[L(D):=H^0(X,\cO(D))=\{f\in\cM^\times(X):(f)+D\ge0\}\cup\{0\}.\]


\[\mathrm{Div}(X)=H^0(X,\cM^\times/\cO^\times)=\Gamma(\cM^\times/\cO^\times).\]
\[\mathrm{Pic}(X)=H^1(X,\cO^\times).\]
First Chern class $H^1(X,\cO^\times)\to H^2(X,\Z)$.


\begin{prb}
Let $X$ be a compact Riemann surface.
A \emph{Weil divisor} $D$ on $X$ is an element of the free abelian group $\mathrm{Div}(X)$ generated by points of $X$.
By compactness of $X$, a meromorphic function $f\in\cM(X)$ gives rise to a divisor $(f):=\sum_{p\in X}\ord_p(f)p$.
Such a divisor is called a \emph{principal divisor}.

Let $D=\sum n_ip_i$ on $X$ be a Weil divisor on $X$.
Each point $P\in X$ has a meromorphic function $f$ on an open neighborhood $U$ of $P$ such that $(f)=D$ on $U$.
It implies that there is a collection $\{f_\alpha\}$ of meromorphic functions $f_\alpha$ defined on $U_\alpha$, where $\{U_\alpha\}$ is an open cover of $X$, such that $f_\alpha/f_\beta$ is a well-defined holomorphic functions on $U_\alpha\cap U_\beta$.
The collection $\{f_\alpha\}$ is called a \emph{Cartier divisor}.

A Cartier divisor defines a line bundle.
\end{prb}

\begin{prb}
Given $\{p_i\}_{i=1}^n$ points and $\{f_i\}_{i=1}^n$ principal parts, there is a meromorphic function $f$ with pre-described principal parts if and only if for every holomorphic 1-form $\omega$ we have $\sum_{i=1}^n\Res(f_i\omega,p_i)=0$.
\end{prb}

\begin{prb}
\[l(D)-l(K-D)=\deg(D)+1-g.\]
The genus can be defined by $g=h^0(X,\Omega^1)$.
For algebraic curves, it can be proved as follows:
Assuming the Serre duality, we have $\chi(D)=h^0(D)-h^1(D)=l(D)-l(K-D)$ and $\chi(0)=h^0(0)-h^1(0)=1-g$.
Then, the Riemann-Roch is boiled down to $\chi(D)=\deg(D)+\chi(0)$, which can be shown inductively.

However, we want to prove a compact Riemann surface is projective as an application of the Riemann-Roch theorem, we need to prove the Riemann-Roch theorem without theory of algebraic curves.
\begin{parts}
\item If $\deg D<0$, then $l(D)=0$.
\end{parts}
\end{prb}
\begin{pf}
(a)
Let $f\in L(D)\setminus\{0\}$.
Then, $(f)+D\ge0$ and $\deg(f)=0$ imply $\deg D\ge0$, which is a contradiction.

(b)
Let $D=0$.
Then, it follows from $l(K)=g$ and $l(0)=1$.

Let $D>0$.
We may assume $D=\sum_{i=1}^nn_ip_i$ with $n_i>0$. (why?)
Let
\[V_i:=\Bigl\{\sum_{k=-n_i}^{-1}c_k(z-p_i)^k:c_k\in\C\Bigr\}\]
and $V:=\bigoplus_{i=1}^nV_i$. (how can we define the principal part of $f$ on Riemann surface?)
Then, $\dim V=\deg D$.
Define $L(D)\to V$ by principal part at each point $p_i$.


\end{pf}

\begin{prb}[Embedding theorem]
Let $X$ be a compact Riemann surface.
The \emph{complete linear system} of a divisor $D$ on $X$ is
\[|D|:=\{(f)+D:f\in\cO(X)\}.\]
Then, $|D|$ can be identified with the projective space $(L(D)\setminus\{0\})/\C^\times=\CP^{l(D)-1}$.
Let $(f_i)_{i=0}^{l(D)-1}$ be a basis of $L(D)$.

For a linear system $\Delta$ of projective dimension $n-1$, we can take (how?) a basis $(f_i)_{i=0}^{n-1}$ such that the following map is well-defined:
\[X\setminus\mathrm{Bl}(\Delta)\to\CP^{n-1}:p\mapsto(f_0:\cdots:f_{n-1}).\]
\end{prb}


\chapter{Algebraic curves}

\section{}
multiplicities, Bezout theorem

\section{}
divisors, line bundles
euler characteristic
(tangent line bundle degree 2-2g, canonical line bundle 2g-2)
$L(D):=\Gamma(X,\cO(D))=H^0(X,\cO(D))$

Jacobian variety (moduli spaces....)


\begin{prb}[Chow theorem]
A complex submanifold of a projective space is algebraic.
\end{prb}


\chapter{Uniformization}

The uniformization theorem provides one philosophy to classify compact Riemann surfaces.
The universal covering is one of the three: the Riemann sphere, the complex plane, and the open unit disk.
Each compact Riemann surface is realized as a quotient of these model space with a properly discontinuous action.

\begin{itemize}
\item $g=0$: Riemann sphere (spherical) $\to$ Riemann sphere itself
\item $g=1$: complex plane (Euclidean) $\to$ elliptic curves
\item $g\ge2$: open unit disk (hyperbolic) $\to$ hyperbolic surfaces, classified by Fuchsian groups(with which properties?)
\end{itemize}


\iffalse
\section{Symmetry groups}
isometry, conformal, rigid motion, etc.
\section{Discrete subgroups}
continuous group actions?
(convex, locally finite) fundamental domains
tesselation, polygon theorem
Fuchsian and Kleinian
\fi




\part{Topological surfaces}


\chapter{Fundamental groups}

\section{Homotopy}
\begin{prb}
A \emph{homotopy of paths} is a continuous map $h:I\times I\to X$ such that $h(0,)=x_0$ and 
\begin{parts}
\item linear homotopy
\item reparametrization
\end{parts}
\end{prb}
\begin{prb}
The fundamental group is a group
composition
\end{prb}

\begin{prb}[Van Kampen theorem]
\end{prb}

\section{Covering spaces}

% a covering space is a fiber bundle which is a sheaf.

\begin{prb}[Unique path lifting property]
Let $p:Y\to X$ be a covering map.
For a path $\gamma:[0,1]\to X$ and a point $y_0\in Y$ such that $p(y_0)=\gamma(0)$, there is a unique lift $\tilde\gamma:I\to Y$ of $\gamma$ such that $\tilde\gamma(0)=y_0$.

As a corollary, if $\gamma_0$ and $\gamma_1$ are end-fixing homotopic and have lifts $\tilde\gamma_0$ and $\tilde\gamma_1$ such that $\tilde\gamma_0(0)=\tilde\gamma_1(0)$, then $\tilde\gamma_0$ and $\tilde\gamma_1$ are basepoint-preserving homotopic.

As a corollary, for $p(y_0)=x_0$, the induced map $p_*:\pi_1(Y,y_0)\to\pi_1(X,x_0)$ is injective.
\end{prb}
\begin{pf}

(Uniqueness)
The interval $[0,1]$ can be replaced to any connected set.

(Existence)
By the compactness of $[0,1]$, there is an increasing finite sequence $(t_i)_{i=0}^n$ such that
\[t_0=0,\quad t_n=1,\quad[t_i,t_{i+1}]\subset\gamma^{-1}(U_i),\qquad 0\le i<n,\]
where $U_i$ is trivializing $p$.


\end{pf}

\begin{prb}[Universal covering]
connected, locally path connected, semi-locally simply connected

\end{prb}

\begin{prb}[Classification of covering spaces]
connected, locally path connected, semi-locally simply connected

We say $p$ is \emph{regular} if $p_*(\pi_1(Y,y_0))$ is normal in $\pi_1(X,x_0)$.

$\pi_1(X,x_0)/p_*(\pi_1(Y,y_0))\to p^{-1}(x_0)$ is always injective, and bijective if $Y$ is path connected.
\end{prb}


Examples: $S^1$, $\RP^n$.



\chapter{Homology groups}
\section{Singular homology}

\begin{prb}[Eilenberg-Steenrod axioms]
\end{prb}


\section{Simplicial homology}

Simplicial homology is defined for simplicial complex, which is purely combinatorial.
The singular chain complex of a topological space is the most natural simplicial complex on it.
The simplicial homology of this is the singular homology as it is just the definition.

One can associate some other simplicial complexes by \emph{triangulations} to a topological space which are more convenient to compute the homology.
We now have to investigate which conditions make a simplicial complex generate same homology groups with singular homology.

Let $X$ be a simplicial complex.
A \emph{geometric realization} of $X$ is a topological space $|X|$ defined by....
For a topological space, a \emph{triangulation} is a homeomorphism from the geometric realization of a simplicial complex to the topological space.

\section{Cellular homology}

\section{Cohomology}




\chapter{Classification of surfaces}
\section{Combinatorial surfaces}

triangulation
orientability
euler characteristic
genus
connected sum



\end{document}