\documentclass{../crs}
\usepackage{../../ikany}

\title{Analysis 2 : General Topology}

\begin{document}
\maketitle
\tableofcontents

\frontmatter
\input{preface}

\mainmatter
\input{ch1}






% CHAPTER 2
\chapter{Continuity}

% SECTION 2-1
\section{Continuous functions}

\subsection{Various continuity}
continuity, Cauchy continuity, uniform continuity, 

Lipschitz continuity
\begin{ex}
An isometry between metric spaces is Lipschitz continuous with costant 1.
\end{ex}

\subsection{Sequential continuity}




\section{Continuous maps}

\subsection{Mono and epi}

\subsection{Subspaces and quotient spaces}

\subsection{Product space}

\subsection{Homeomorphisms}
continuous bijection
open map
how to show two spaces are not homeomorphic
- topological property: connected, compact


\section{Connectedness}

\subsection{Connected spaces}
component
\subsection{Path connected spaces}

\subsection{Locally connected spaces}

\subsection{Homotopy}













\chapter{Convergence}

\section{Nets}

product of two directed sets
projection is monotone final
uniformity is itself an upward directed set by reverse inclusion, like $\R_{\ge0}$.
cofinality and subsequence

eventuality filter, three definitions of subnets

\section{Sequences}
sequential spaces, first countable

\section{Completeness}
completion















\chapter{Compactness}


\begin{defn}
Let $X$ be a topological space.
A \emph{cover} of a subset $A\subset X$ is a collection $\{U_\alpha\}_{\alpha\in\cA}$ of subsets of $X$ such that $A\subset\bigcup_{\alpha\in\cA}U_\alpha$.
If $U_\alpha$ are all open, then it is called \emph{open cover}.
\end{defn}
\begin{defn}
Let $X$ be a topological space.
A subset $K\subset X$ is called \emph{compact} if every open cover of $K$ has a finite subcover.
\end{defn}
\begin{prop}
Let $X$ be a topological space with a basis $\mathcal{B}$.
A subset $K\subset X$ is compact if and only if every cover of the form $\{B_x\in\mathcal{B}\}_{x\in K}$ has a finite subcover.
\end{prop}
\begin{rmk}
Let $\cP$ be a property of a fuction $f\colon X\to Y$, such as continuity
If we say $f$ has $\cP$ at a point $x$, then it would implies that $x$ has a neighborhood $U$ such that 
\end{rmk}

\subsection{Properties of compactness}
\begin{thm}
Let $X$ and $Y$ be topological spaces.
For a continuous map $f\colon X\to Y$, the image $f(K)$ is compact for compact $K\subset X$.
\end{thm}

\begin{rmk}
This is why the term ``compact space'' is widely used.
\end{rmk}

\begin{cor}[The extreme value theorem]
A continuous function on a closed interval has a global maximum and
\end{cor}

Heine-Cantor,



\subsection{Characterizations of compactness}

\begin{rd}[column sep=large,row sep=large]
net compact \ar{d} & sequentially compact \ar{d} & \\
compact \ar{u}\ar{r} & countably compact \ar{r}\lds{l}{\parbox{10em}{\centering metrizable\\\emph{or} 2nd countable}}\rds{u}{sequential} & limit point compact \lds{l}{$T_1$}
\end{rd}






\section{Relative compactness}

\begin{prop}[?????]
Let $X$ be a locally compact Hausdorff space.
For a subset $A$ of $X$, the followings are all equivalent:
\begin{cond}
\item a uniformity on $X$ makes $A$ have compact completion,
\item the set $A$ has compact closure in $X$,
\item every uniformity on $X$ makes $A$ have compact completion.
\end{cond}
\end{prop}





\begin{defn}
A uniform space is called \emph{relatively compact} or \emph{precompact} if its completion is compact.
\end{defn}

The relative compactness is in particular useful in uniform spaces.
We might be able to say the familiar definition of relative compactness has come from the following proposition:
\begin{prop}
A subset of a complete uniform space, like Banach or Fr\'echet space, is relatively compact if and only if its closure is compact.
\end{prop}
\begin{pf}
In a complete uniform space, the completion can be charaterized as closure.
\end{pf}

The following two definitions are helpful when we need to check relative compactness.
\begin{defn}
A Cauchy space is called \emph{relatively Cauchy compact} if every net has a Cauchy subnet.
\footnote{There are three well-known different definitions: Willard subnet, Kelly subnet, and Aarnes-Anden{\ae}s subnet. However, since the existence of each subnet associated to a common eventuality filter is equivalent, there will be no conflicts among them. In this note, we define a subnet as the monotone cofinal function between the index sets. See Eric schechter's book [].}
\end{defn}
\begin{defn}
A uniform space is called \emph{totally bounded} if for every entourage $E$ there is a finite cover $\{U_i\}_i$ with $U_i\x U_i\subset E$ for each index $i$.
\end{defn}

\begin{thm}
Let $X$ be a uniform space.
The followings are all equivalent:
\begin{cond}
\item $X$ is relatively compact;
\item $X$ is relatively Cauchy compact;
\item $X$ is totally bounded.
\end{cond}
\end{thm}
\begin{pf}
Let $\tld X$ be the completion of $X$ and $\cU$ be the uniquely extended uniformity of $\tld X$ from $X$.

(1)$\impl$(2).
Every net in $X$ has a subnet that converges in $\tld X$.
The subnet is Cauchy.

(1)$\impl$(3).
Let $E\in\cU$.
Since $\{U:U\text{ is open in }\tld X,\ U\x U\subset E\}$ is an open cover of $\tld X$, there is a finite subcover $\{U_i\}_i$ of $\tld X$.
Then, $\{U_i\cap X\}_i$ is a finite cover of $X$ satisfying $(U_i\cap X)\x(U_i\cap X)\subset E$.

(2)$\impl$(1).
If we show $\tld X$ is also relatively Cauchy compact, we are done.
That is because of the fact that compactness and net compactness are always equivalent in all topological spaces.

Let $\tld x:\fA\to\tld X$ be a net in $\tld X$.
Take an approximating net $x:\fA\x\cU\to X$ in $X$ such that
\[(x_{(\alpha,E)},\tld x_\alpha)\in E\]
for all $\alpha\in\fA$ and all entourages $E\in\cU$.
Recall that $(\alpha,E)\succ(\alpha',E')$ if and only if $\alpha\succ\alpha'$ and $E\subset E'$.
By the assumption that $X$ is relatively Cauchy compact, there is a Cauchy subnet
\[xh:\fB\to{h}\fA\x\cU\to X\]
of $x$.
Then,
\[\tld x\alpha h:\fB\to{h}\fA\x\cU\to{\alpha}\fA\to\tld X\]
is a subnet of $\tld x$ since both $h$ and the projection $\alpha$ are monotone and cofinal so that so is their composition.
We claim that $\tld x\alpha h$ is Cauchy.

In order to show this, take an arbitrary entourage $E$.
We may assume $E$ is symmetric.
By the Cauchyness of $xh$, we can find $\beta_0\in\fB$ such that
\[\beta,\beta'\succ\beta_0\impl(x_{h(\beta)},x_{h(\beta')})\in E.\]
Moreover, we may assume $h(\beta_0)=(\alpha_0,E_0)$ satisfies $(\alpha_0,E_0)\succ(\alpha_0,E)$ so that
\[(x_{h(\beta_0)},\tld x_{\alpha h(\beta_0)})=(x_{(\alpha_0,E_0)},\tld x_{\alpha_0})\in E_0\subset E.\]
Then, for $\beta,\beta'\succ\beta_0$, the following three relations
\[(x_{h(\beta)},\tld x_{\alpha h(\beta)})\in E_0\subset E,\quad(x_{h(\beta)},x_{h(\beta')})\in E,\quad(x_{h(\beta')},\tld x_{\alpha h(\beta')})\in E_0\subset E\]
implies $(\tld x_{\alpha h(\beta)},\tld x_{\alpha h(\beta')})\in E^3$.
Therefore, $\tld x\alpha h:\fB\to\tld X$ is Cauchy.

(3)$\impl$(1).
Clearly, $\tld X$ is totally bounded.
A complete totally bounded space is compact.
\end{pf}

In the last of the proof above, we used the famous result of complete totally bounded spaces.
This can be easily proved with diagonal subsequence extracting argument under the metric space condition, but we need the subtle application of the axiom of choice when we require only uniformness of the space.

\begin{thm}
A complete totally bounded uniform space is compact.
\end{thm}
\begin{pf}
Omitted.
Refer to any advanced general topology text or my other expository essay: totally bounded uniform spaces.
\end{pf}


Empirically, compactness checking problems seem to be fallen into two cases: one is to show both completeness and relative compactness, and the other is to apply Tychonoff's theorem.
Followings are some examples.

\begin{ex}[The Heine-Borel theorem]
A subset of a Euclidean space is compact if and only if it is closed and bounded.
\end{ex}
\begin{ex}[The Blaschke selection theorem]
Let $H(X)$ be the metric space of nonempty compact subsets of a metric space $X$ with Hausdorff metric.
If $X$ is compact, then $H(X)$ is compact.
\end{ex}
\begin{ex}[The Banach-Alaoglu theorem]
Let $X$ be a locally convex space and $X^*$ the continuous dual of $X$ with weak$^*$ topology.
If $B\subset X^*$ satisfies $\sup_{f\in B}|f(x)|<\infty$ for each $x\in X$, then $B$ is compact.
\end{ex}
\begin{pf}
We can embed $X^*$ into $\F^X$.
\end{pf}















\chapter{Separation axioms}

\section{Separation axioms}
\section{Metrization theorems}









\chapter{Function spaces}




\section{Compact-open topology}

% 6-1-1
\subsection{Definition}

\begin{defn}
Let $X$ and $Y$ be topological spaces.
The \emph{continuous functions space} $C(X,Y)$ is the set of continuous functions from $X$ to $Y$.
If $Y=\mathbb{R}$ or $\mathbb{C}$, then the continuous function space is denoted by $C(X)$.
\end{defn}

% 6-1-2
\subsection{Compact convergence}
topology of compact convergence
metrizability and hemicompact
topology of uniform convergence
uniform structure of pointwise convergence


$C(X,Y)$ has the compact-open topology
When $Y$ is uniform, $C(X,Y)$ has the topology of compact convergence
When $X$ is compact and $Y$ is uniform, $C(X,Y)$ has the topology of uniform convergence

When $X$ is locally compact Hausdorff, and the exponential space is endowed with compact-open topology


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In considering the continuous function space, $Y$ will be assumed to be a metric space because of its usefulness in most applications.
Then, there are two useful topologies on $C(X,Y)$.
Since there is a difficulty to deal with open sets or basis directly in a function space, the convergence will be a reliable alternative to describe the topologies.
Before giving definition of the topologies, define pseudometrics $\rho_K$ on $C(X,Y)$ by
\[\rho_K(f,g)=\sup_{x\in K}d(f(x),g(x))\]
for $K\subset X$ compact.

\begin{defn}
Let $X$ and $Y$ be topological spaces.
The \emph{topology of pointwise convergence} on $C(X,Y)$ is a subspace topology inherited from the product topology on $Y^X$.
\end{defn}

\begin{prop}
Let $X$ be a topological space and $Y$ be a metric space.
The topology of pointwise convergence on $C(X,Y)$ is generated by pseudometrics $\rho_{\{x\}}$, namely all $\{g:d(f(x),g(x))<\e\}$ for $f\in C(X,Y)$, $\e>0$, and $x\in X$.
\end{prop}

\begin{defn}
Let $X$ be a topological space and $Y$ be a metric space.
The \emph{topology of compact convergence} on $C(X,Y)$ is a topology generated by pseudometrics $\rho_K$, namely all $\{g:\rho_K(f,g)<\e\}$ for $f\in C(X,Y)$, $\e>0$, and compact $K\subset X$.
\end{defn}

\begin{prop}
Let $C(X,Y)$ be a continuous function space for a topological space $X$ and a metric space $Y$.
A functional sequence in $C(X,Y)$ converges in the topology of compact convergence if and only if the functional sequence converges compactly.
\end{prop}

\begin{thm}
Let $X$ be a topological space and $Y$ be a metric space.
If $X$ is hemicompact, in other words, $X$ has a sequence of compact subsets $\{K_n\}_{n\in\N}$ such that every compact subset of $X$ is contained in $K_n$ for some $n\in\N$, then the topology of compact convergence on $C(X,Y)$ is metrizable.
\end{thm}

\begin{proof}
bounding and merging pseudometrics
\end{proof}



% 6-1-3
\subsection{Exponentiability}
locally compact Hausdorff spaces
exponential space






$\frac\e3$ argument





% SECTION 6-2
\section{Rings of continuous functions}



\subsection{$C(X), C_0(X), C_b(X)$}



\section{Important theorems on function space}


\subsection{The Arzela-Ascoli theorem}

The Arzela-Ascoli theorem is a main technique to verify compactness of a subspace of continuous function space.
The theorem requires the notion of equicontinuity, which lifts pointwise compactness up onto compactness in topology of compact convergence.

\begin{defn}
Let $X$ be a topological space and $Y$ be a metric space.
A subset $\mathcal{F}\subset C(X,Y)$ is called \emph{(pointwise or locally) equicontinuous} if for every $\e>0$ and each $x_0\in X$, there is an open neighborhood $U$ of $x_0$ such that $x\in U\impl d(f(x),f(x_0))<\e$ for all $f\in\cF$.
\end{defn}
Compare with the following definition:
\begin{defn}
Let $X$ be a metric space and $Y$ be a metric space.
A subset $\mathcal{F}\subset C(X,Y)$ is called \emph{uniformly equicontinuous} if for every $\e>0$ there exists $\delta>0$ such that $d(x,y)<\delta\impl d(f(x),f(y))<\e$ for all $f\in\cF$.
\end{defn}
The uniform equicontinuity is what the Rudin's book says it just equicontinuous.

\begin{thm}[Arzela-Ascoli, conventional version]
Let $X$ be a compact space.
For $\{f_n\}_{n\in\N}\subset C(X)$, if it is equicontinuous and pointwisely bounded, then there is a subsequence that uniformly converges.
\end{thm}

Let $\cT_p$ be the topology of pointwise convergence and $\cT_c$ be the topology of compact convergence.

\begin{thm}[Arzela-Ascoli, metrized version]
Let $X$ be a hemicompact space and $Y$ be a metric space.
If $\cF\subset C(X,Y)$ is equicontinuous and relatively compact in $\cT_p$, then it is relatively compact in $\cT_c$.
\end{thm}
\begin{pf}
Let $\{f_n\}_{n\in\N}$ be a sequence in $\cF$ and $K\subset X$ be a compact.

By equicontinuity, for each $k\in\N$ a finite open cover $\{U_s\}_{s\in S_k}$ with a finite set $S_k\subset K$ can be taken such that $x\in U_s\,\impl\,d(f(x),f(s))<\frac1k$ for all $f\in\cF$.
By the pointwise relative compactness, we can extract a subsequence $\{f_m\}_{m\in\N}$ of $\{f_n\}_n$ such that $\{f_m(s)\}_m$ is Cauchy for each $s\in\bigcup_{k\in\N}S_k$ by the diagonal argument.

For every $\e>0$, let $k=\ceil{\e^{-1}}$ so that $\frac1k\le\e$.
Let $m_{0,s}$ be an index such that $m,m'>m_{0,s}\impl d(f_m(s),f_{m'}(s))<\e$, and define $m_0=\max\{m_{0,s}:s\in S_k\}$.
Then, for arbitrary $x\in K$, we obtain $m,m'>m_0\impl$
\[d(f_m(x),f_{m'}(x))\le d(f_m(x),f_m(s))+d(f_m(s),f_{m'}(s))+d(f_{m'}(s),f_{m'}(x))<3\e\]
by taking $s\in S_k$ such that $x\in U_s$.
Thus, $\{f_m\}_m$ is a subsequence of $\{f_n\}_n$ that is uniformly Cauchy on $K$.
\end{pf}

If $C(X,Y)$ is not metrizable, or if $Y$ is uniform but not metrizable, the subsequence extracting procedure is no more available.

\begin{thm}[Arzela-Ascoli, generalized version]
Let $X$ be a topological space and $Y$ be a uniform space.
If $\cF\subset C(X,Y)$ is equicontinuous and relatively compact in $\cT_p$, then it is relatively compact in $\cT_c$.
\end{thm}
\begin{pf}[1]
Every net in $\cF$ has a subnet that is pointwisely Cauchy.
Then we are done if we prove every pointwisely Cauchy net in $\cF$ is in fact uniformly Cauchy on each compact set $K\subset X$.

Let $f:\fA\to\cF$ be a pointwisely Cauchy net.
Let $E$ be an arbitrary entourage in $Y$.
By equicontinuity, every point $s\in X$ has a neighborhood $U_s$ such that
\[x\in U_s\impl(f(x),f(s))\in E\]
for all $f\in\cF$.
We can find a finite set $S\subset K$ such that $\{U_s\}_{s\in S}$ is a cover of $X$.
(In here, we do not need to extract a subnet because the net is already pointwisely Cauchy.)
Let $\alpha_{0,s}$ be an index such that
\[\alpha,\alpha'\succ\alpha_{0,s}\impl(f_\alpha(s),f_{\alpha'}(s))\in E,\]
and define $\alpha_0=\max\{\alpha_{0,s}\}_{s\in S}$.
Then, for arbitrary $x\in K$ there is $s\in S$ such that $x\in U_s$, so we get
\[\alpha,\alpha'\succ\alpha_0\impl(f_\alpha(x),f_{\alpha'}(x))=(f_\alpha(x),f_\alpha(s))\o(f_\alpha(s),f_{\alpha'}(s))\o(f_{\alpha'}(s),f_{\alpha'}(x))\in E^3.\]
Thus, $f$ is uniformly Cauchy on $K$.
\end{pf}

\begin{proof}[Proof 2]

\end{proof}

\begin{proof}[Proof 3]
We are going to prove the two topologies coincide in $\cF$.
Note that subspace topologies $\cT_p\vert_\cF$ and $\cT_c\vert_\cF$ are also generated by pseudometrics $\rho_{\{x\}}(f,g)=d(f(x),g(x))$ and $\rho_K(f,g)=\sup\{d(f(x),g(x)):x\in K\}$ defined on $\cF$ respectively.
Since $\cT_p\vert_\cF\subset\cT_c\vert_\cF$ clearly, it is enough to show the converse.

Take a subbasis element $B_K(f_0,\e)\cap\cF$ of $\cT_c\vert_\cF$ with $f_0\in\cF$.
By equicontinuity of $\cF$, there is a finite cover $\{U_s\}_{s\in S}$ of a compact subset $K$ such that $x\in U_s\,\impl\,d(f(x),f(s))<\e$ for all $f\in\cF$.

If $f\in\cF$ satisfies $\rho_{\{s\}}(f,f_0)<\e$ for all $s\in S$, then we get
\[\rho_K(f,f_0)\le\sup_{x\in K}d(f(x),f(s))+d(f(s),f_0(s))+\sup_{x\in K}d(f_0(s),f_0(x))<\e\]
by taking $s\in S$ such that $x\in U_s$.
This means
\[\bigcap_{s\in S}B_{\{s\}}(f_0,\e)\subset B_K(f_0,3\e).\]
It implies that the subbasis element contains an open set in $\cT_p\vert_\cF$.
Therefore, $\cT_c\vert_\cF\subset\cT_p\vert_\cF$.
\end{proof}

converse of Arzela-Ascoli

\subsection{The Stone-Weierstrass theorem}








\end{document}












Limiting inequality
dependency diagram
double limit table










