\documentclass{../../small}
\usepackage{../../ikhanchoi}

\newcommand{\sech}{\operatorname{sech}}

\begin{document}
\title{Operator Algebra Seminar Note II}
\author{Ikhan Choi}
\maketitle
\tableofcontents


\section*{Acknowledgement}
This note has been written based on the first-year graduate seminar presented at the University of Tokyo in the 2023 Autumn semester.
Each seminar was delivered for 105 minutes.
I gratefully acknowledge advice of Prof. Yasuyuki Kawahigashi and support of my colleagues Futaba Sato, Yusuke Suzuki.

TODO
\begin{itemize}
\item lower semi-continuous weights, Thomsen's Combes theorem
\item normal stinespring dilation
\item cocycle, commutant, central, spatial derivatives
\item approximation techniques: $E_n,R_n$ for actions
\end{itemize}


\newpage
\section{October 18}

\subsection{Countably decomposable von Neumann algebras}

\begin{defn}[Countably decomposable von Neumann algebras]
Let $M$ be a von Neumann algebra.
A projection $p\in M$ is called \emph{countably decomposable} if mutually orthogonal non-zero projections majorized by $p$ are at most countable, and we say $M$ is \emph{countably decomposable} if the identity is.
\end{defn}
\begin{prop}
For a von Neumann algebra $M$, the followings are all equivalent.
\begin{parts}
\item $M$ is countably decomposable.
\item $M$ admits a faithful normal state.
\item $M$ admits a faithful normal non-degenerate representation with a cyclic and separating vector.
\item The unit ball of $M$ is metrizable in one of the following topologies: $\sigma$-strong$^*$, $\sigma$-strong, strong$^*$, strong.
\end{parts}
\end{prop}
\begin{pf}
(a)$\Leftrightarrow$(b)
Suppose $M$ is countably decomposable.
Let $\{\xi_i\}\subset H$ be a maximal family of unit vectors such that $\bar{M'\xi_i}$ are mutually orthogonal subspaces, taken by Zorn's lemma.
If we let $p_i$ be the projection on $\bar{M'\xi_1}$, then $p_izp_i=zp_i$ for $z\in M'$ implies $p_i\in M''=M$.
By the assumption, the family $\{\xi_i\}$ is countable.
Define a state $\omega$ of $M$ such that
\[\omega(x):=\sum_{i=1}^\infty\omega_{2^{-i}\xi_i}(x),\qquad x\in M.\]
It converges due to $\|\omega_{2^{-i}\xi_i}\|=2^{-i+1}$.
It is normal since the sequence $(2^{-i}\xi_i)$ belongs to $\ell(\N,H)$, and it is faithful because $\omega(x^*x)=0$ implies $x\xi_i=0$ for all $i$, which deduces that $x=\sum_ixp_i=0$.

Conversely, if $\omega$ is a faithful normal state, then for a mutually orthogonal family of non-zero projections $\{p_i\}\subset M$, we have
\[\{p_i\}=\bigcup_{n=1}^\infty\{p_i:\f(p_i)>n^{-1}\}\]
the countable union of finite sets.
Thus $M$ is countable decomposable.

(b)$\Leftrightarrow$(c)
Let $\omega$ be a faithful normal state of $M$.
Consider any faithful normal nondegenerate representation in which $\omega$ is a vector state so that the corresponding vector is a separating vector by the faithfullness of $\omega$.
Examples include the GNS representation of $\omega$, and the composition with the diagonal map $B(H)\to B(\ell^2(\N,H))$.
Then, $\bar{M\Omega}$ admits a cyclic and separating vector $\Omega$ of $M$.
The converse is immediate, i.e.~the vector state $\omega_\Omega$ is a faithful normal state of $M$.

(a)$\Leftrightarrow$(d)
Suppose $M$ is countably decomposable and take $\{\xi_i\}_{i=1}^\infty$ and $\{p_i\}_{i=1}^\infty$ as we did.
Define
\[d(x,y):=\sum_{i=1}^\infty2^{-i}\|(x-y)\xi_i\|.\]
Clearly it generates a topology coarser than strong topology.
It is also finer because if a bounded net $x_\alpha$ in $M$ converges to zero in the metric $d$ so that $x\xi_i\to0$ for all $i$, then $H=\bigoplus_iM'\xi_i$ implies that for every $\xi\in H$ and $\e>0$ we have $\|\xi-\sum_{k=1}^nz_k\xi_{i_k}\|<\e$ for some $z_k\in M'$ so that
\[\|x_\alpha\xi\|\le\|x_\alpha(\xi-\sum_{k=1}^nz_k\xi_{i_k})\|+\sum_{k=1}^n\|x_\alpha z_k\xi_{i_k}\|<\e+\sum_{k=1}^n\|z_k\|\|x_\alpha\xi_{i_k}\|\to\e.\]
Since on the bounded part the strong and $\sigma$-strong topologies coincide, the two topologies on the unit ball are metrizable.
We can do similar for the strong$^*$ and the $\sigma$-strong$^*$ topologies.

Conversely, for a mutually orthogonal family of non-zero projections $\{p_i\}_{i\in I}\subset M$, since the net of finite partial sums $p_F:=\sum_{i\in F}p_i$ is an non-decreasing net in the closed unit ball whose supremum is the identity of $M$, there is a convergent subsequence $p_{F_n}\uparrow1$ by the metrizability, which implies $I=\bigcup_{n=1}^\infty F_n$, the countable union of finite sets.
\end{pf}

\begin{prop}
For a von Neumann algebra $M$, the followings are all equivalent.
\begin{parts}
\item $M$ has the separable predual.
\item $M$ admits a faithful normal non-degenerate representation on a separable Hilbert space.
\item $M$ is countably decomposable and countably generated.
\item The unit ball of $M$ is metrizable in one of the following topologies: $\sigma$-weak, weak.
\end{parts}
\end{prop}


\subsection{Weights and semi-cyclic representations}


\begin{defn}[Weights]
Let $M$ be a von Neumann algebra.
A \emph{weight} is a function $\f:M^+\to[0,\infty]$ such that
\[\f(x+y)=\f(x)+\f(y),\qquad\f(\lambda x)=\lambda\f(x),\qquad x,y\in M^+,\ \lambda\ge0,\]
where we use the convention $0\cdot\infty=0$.
\end{defn}

\begin{defn}
Let $\f$ be a weight on a von Neumann algebra $M$.
Define
\[\fn:=\{x\in M:\f(x^*x)<\infty\},\qquad\fa:=\fn^*\cap\fn,\qquad\fm:=\fn^*\fn.\]
It easily follows that $\fn$ is a left ideal of $M$ with a sesquilinear form $\<,\>_\f:\fn\times\fn\to\C$ such that
\[\<x,y\>_\f:=\f(y^*x),\qquad x,y\in\fn,\]
$\fa$ is a $*$-subalgebra of $M$, and $\fm$ is a hereditary $*$-subalgebra of $M$ with a positive linear functional $\f:\fm\to\C$ such that
\[\f(y^*x):=\sum_{k=0}^3i^k\f((x+i^ky)^*(x+i^ky)),\qquad x,y\in\fn,\]
which extends the original $\f$.
\end{defn}


\begin{prop}
Let $\f$ be a weight on a von Neumann algebra $M$.
\begin{parts}
\item Every element of $\fm^+$ can be written to be $x^*x$ for some $x\in\fn$.
\item Every element of $\fm$ can be written to be $y^*x$ for some $x,y\in\fn$.
\end{parts}
\end{prop}
\begin{pf}
(a)
Let $a:=\sum_{i=1}^ny_i^*x_i\in\fm^+$ for some $x_i,y_i\in\fn$.
The polarization writes
\[a=\frac14\sum_{i=1}^n\sum_{k=0}^3i^k|x_i+i^ky_i|^2\]
and $a^*=a$ implies
\[a=\frac12\sum_{i=1}^n(|x_i+y_i|^2-|x_i-y_i|^2)\le\frac12\sum_{i=1}^n|x_i+y_i|^2\]
implies
\[\f(a)\le\frac12\sum_{i=1}^n\f(|x_i+y_i|^2)<\infty.\]
Therefore, if $x:=a^{\frac12}\in\fn$, then $a=x^*x$.

(b)
Let $a:=\sum_{i=1}^ny_i^*x_i\in\fm$ for some $x_i,y_i\in\fn$.
Let $x:=(\sum_{i=1}^nx_i^*x_i)^{\frac12}\in\fn$.
Since $x_i^*x_i\le x^2$, we have $s_i\in M$ such that $x_i=s_ix$.
If we let $y:=\sum_{i=1}^ns_i^*y_i\in\fn$, then
\[a=\sum_{i=1}^ny_i^*x_i=\sum_{i=1}^ny_i^*s_ix=(\sum_{i=1}^ns_i^*y_i)x=y^*x.\qedhere\]
\end{pf}


\begin{defn}[Semi-cyclic representations]
Let $A$ be a C$^*$-algebra.
A \emph{semi-cyclic representation} of $A$ is a pair $(\pi,\Lambda)$ of a representation $\pi:A\to B(H)$ and a linear map $\Lambda:\dom\Lambda\to H$ of dense image such that $\pi(a)\Lambda(b)=\Lambda(ab)$ for $x\in A$ and $b\in\dom\Lambda$, where $\dom\Lambda$ is a left ideal of $A$.
\end{defn}

\begin{prop}
Let $\f$ be a weight on a von Neumann algebra and $(\pi,\Lambda)$ be the associated semi-cyclic representation to $\f$.
For $h\in\pi(M)'$, the linear functional $\fm\to\C:y^*x\mapsto\<h\Lambda(x),\Lambda(y)\>$ is well-defined.
\end{prop}
\begin{pf}
We first check the well-definedness on $\fm^+$.
Let $x^*x=y^*y\in\fm^+$ for $x,y\in\fn$.
Then, there is $s\in M$ such that $y=sx$ and $s=sp$, where $p$ is the range projection of $x$, so $x^*(1-s^*s)x=x^*x-y^*y=0$ implies $0=p(1-s^*s)p=p-s^*s$ and $x=px=s^*sx=s^*y$.
The well-definedness follows from
\[\<z\Lambda(x),\Lambda(x)\>=\<\pi(s)z\pi(s^*)\Lambda(y),\Lambda(y)\>=\<z\Lambda(ss^*y),\Lambda(y)\>=\<z\Lambda(y),\Lambda(y)\>.\]

The homogeneity is clear, so now we prove the addivitiy.
Let $x^*x,y^*y\in\fm^+$ for some $x,y\in\fn$.
Let $a:=(x^*x+y^*y)^{\frac12}$ and take $s,t\in M$ such that $x=sa$, $y=ta$, $s=sa$, and $t=ta$, where $p$ is the range projection of $a$.
Then, $a(1-s^*s-t^*t)a=a^*a-x^*x-y^*y=0$ implies $p(1-s^*s-t^*t)p=p-s^*s-t^*t$.
It follows that
\begin{align*}
\<z\Lambda(a),\Lambda(a)\>
&=\<z\pi(p)\Lambda(a),\Lambda(a)\>\\
&=\<z\pi(s^*s)\Lambda(a),\Lambda(a)\>+\<z\pi(t^*t)\Lambda(a),\Lambda(a)\>\\
&=\<z\Lambda(x),\Lambda(x)\>+\<z\Lambda(y),\Lambda(y)\>.
\end{align*}
Now the $\Theta(\cdot,z)$ is linearly extendable to $\fm$.
\end{pf}

\begin{prop}[Radon-Nikodym affiliated with commutant]
Let $\f$ be a weight on a von Neumann algebra and $(\pi,\Lambda)$ be the associated semi-cyclic representation to $\f$.
Let $\psi$ be a ...
There is $h$ such that
\[\psi(y^*x)=\<h\Lambda(x),\Lambda(y)\>\]


In particular, if $l\in\fm^\#$ satisfies $|l|\le C\f$ for some $C>0$, then there is $h\in\pi(M)'$ such that $\|h\|\le C$ and $l(y^*x)=\<h\Lambda(x),\Lambda(y)\>$ for $x,y\in\fn$.
\end{prop}
\begin{pf}
(a)

(b)
The linear map $\theta^*$ is injective since $\Lambda$ has dense range.
Take $z\in\pi(M)'$ and consider $\theta^*(z)$, which maps $x^*x$ to $\<z\Lambda(x),\Lambda(x)\>$ for $x\in\fn$.
The image is majorized by $\f$ as
\[|\<z\Lambda(x),\Lambda(x)\>|\le\|z\|\|\Lambda(x)\|^2=\|z\|\f(x^*x).\]
Conversely, let $l\in\fm^\#$ is a linear functional majorized by $\f$, i.e.~there is a constant $C>0$ such that
\[|l(x^*x)|\le C\f(x^*x),\qquad x\in\fn.\]
Define a sesquilinear form $\sigma:\fn\times\fn\to\C$ such that $\sigma(x,y):=l(y^*x)$.
It is well-defined after separation of $\fn$ and is bounded by the Cauhy-Schwartz inequality
\[|\sigma(x,y)|^2=|l(y^*x)|^2\le\|l(x^*x)\|\|l(y^*y)\|\le\f(x^*x)\f(y^*y)=\|\Lambda(x)\|^2\|\Lambda(y)\|^2.\]
Therefore, $\sigma$ defines a bounded linear operator $z\in\pi(M)'$ such that
\[\sigma(x,y)=\<z\Lambda(x),\Lambda(y)\>,\]
exactly meaning $\theta^*(z)(y^*x)=l(y^*x)$ for $x,y\in\fn$.
\end{pf}

Note that we have a commutative diagram
\[\begin{tikzcd}
\fn \ar{r}{\Lambda}\ar[swap]{dd}{|\cdot|^2} & H \ar{d}{\omega} \\
& B(H)_* \ar{d}{\mathrm{res}}\\
\fm^+ \ar{r}{\theta} & \pi(M)'_*.
\end{tikzcd}\]
In particular, for $x\in\fn^+$ we have
\[\|\theta(x^2)\|=\|\omega_{\Lambda(x)}\|=\|\Lambda(x)\|^2=\f(x^2).\]





\subsection{Normal weights and normal semi-cyclic representations}




\begin{defn}[Normal semi-cyclic representations]
Let $M$ be a von Neumann algebra.
We say a weight $\f$ on $M$ is \emph{normal} if it is the supremum of normal positive linear functionals.
We say a semi-cyclic representation $(\pi,\Lambda)$ of $M$ is \emph{normal} if $\pi$ is normal and $\Lambda$ is closed with respect to $\sigma$-weak topology of $M$ and weak topology of $H$.
\end{defn}

\begin{prop}
Let $\f$ be a weight on $M$.
Let $H_\f$ be the Hilbert space defined by the separation and completion of a sesquilinear form $\fn_\f\times\fn_\f\to\C:(x,y)\mapsto\f_\f(y^*x)$, and let $\Lambda_\f:\fn_\f\to H_\f$ be the canonical map.

Let $(\pi,\Lambda)$ be a semi-cyclic representation of $M$.
Let
\[\cF_\Lambda:=\{\omega\in M_*^+:\omega(x^*x)\le\|\Lambda(x)\|^2,\ x\in\dom\Lambda\}\]
and $\f_\Lambda(x^*x):=\sup_{\omega\in\cF_\Lambda}\omega(x^*x)$ for $x\in M$.
Then, it is clear that $\f_\Lambda$ is a weight.
\begin{parts}
\item If $\f$ is normal, then $(\pi_\f,\Lambda_\f)$ is a normal semi-cyclic representation such that $\f=\f_{(\pi_\f,\Lambda_\f)}$.
\item If $(\pi,\Lambda)$ is normal, then $\f_\Lambda$ is a normal weight such that there is a unitary $u:H\to H_{\f_\Lambda}$ satisfying $\pi_{\f_\Lambda}=(\Ad u)\pi$ and $\Lambda_{\f_\Lambda}=u\Lambda$.
\item For a normal $\f$, $\f$ is faithful if and only if $\Lambda$ is injective.
\item For a normal $\f$, $\f$ is semi-finite if and only if $\Lambda$ is $\sigma$-weakly densely defined.
\end{parts}
\end{prop}
\begin{pf}
(a)
We show $\pi_\f$ is normal.
The proof is almost same as the normality of cyclic representation associated to normal states.
Consider $\pi_\f^*:B(H)_*\to M^*$, which is bounded.
Since
\[\pi_\f^*(\omega_{\Lambda_\f(y)})(x)=\<\pi_\f(x)\Lambda_\f(y),\Lambda_\f(y)\>=\f(y^*xy),\qquad x\in M, y\in\fn_\f,\]
and $\f$ is order continuous, we can see that $\pi_\f^*(\omega_{\Lambda_\f(y)})$ is also order continuous, so it is contained in $M_*$.
Because the image of $\Lambda_\f$ is dense, the linear span of states of the form $\omega_{\Lambda_\f(y)}$ for $y\in\fn_\f$ is norm-dense in $B(H)_*$ by the inequality
\[\|\omega_\xi-\omega_\eta\|\le\|\xi-\eta\|(\|\xi\|+\|\eta\|),\qquad\xi,\eta\in H.\]
Since $M_*$ is norm-closed $M^*$, so $\pi_\f^*(B(H)_*)\to M_*$ and $\pi_\f$ is normal.

For closedness of $\Lambda$,



(b)
First we show $\dom\Lambda=\fn_{\f_{(\pi,\Lambda)}}$.
One direction $\dom\Lambda\subset\fn_{\f_{(\pi,\Lambda)}}$ is clear because $x\in\dom\Lambda$ implies $\f_{(\pi,\Lambda)}(x^*x)\le\|\Lambda(x)\|^2$ by definition of $\cF_{(\pi,\Lambda)}$ and $\f_{(\pi,\Lambda)}$.
Conversely, we let $x\in\fn_{\f(\pi,\Lambda)}$ and claim $x\in\dom\Lambda$.
We may assume $x\ge0$ and $\f_{(\pi,\Lambda)}(x^2)=1$.
If we consider the $\sigma$-weak and weak topologies on $\dom\Lambda$ and $H$ respectively, then since the graph of $\Lambda$ is closed and the projection $\dom\Lambda\times H_1\to\dom\Lambda$ is a closed map due to the tube lemma, the set $\{y\in\dom\Lambda:\|\Lambda(y)\|\le1\}$ and its positive part is $\sigma$-weakly closed.
Since the square root is strongly continuous, if we temporarily consider a sufficiently large representation of $M$ in which every normal state is a vector state so that a strong and $\sigma$-strong topology coincide on $M$, we can conclude that $C:=\{y^2:\|\Lambda(y)\|^2\le1,\ y\in(\dom\Lambda)^+\}$ is $\sigma$-weakly closed with its convexity.
If $x^2\notin C$, then there is $\omega\in M_*^{sa}$ such that
\[\sup_{y^2\in C}\omega(y^2)\le1<\omega(x^2)\]
by the Hahn-Banach separation.
Since all functional arguments in the above inequality are all positive, we may assume $\omega$ is positive.
Then, for every $y\in\dom\Lambda$ we have
\[\omega(y^*y)=\|\Lambda(y)\|^2\omega(\frac{y^*y}{\|\Lambda(y)\|^2})\le\|\Lambda(y)\|^2\]
because $y^*y/\|\Lambda(y)\|^2\in C$, which means $\omega\in\cF_{(\pi,\Lambda)}$.
Thus, $\omega(x^2)\le\f_{(\pi,\Lambda)}(x^2)=1$ by definition of $\f_{(\pi,\Lambda)}$, which leads a contradiction, so $x^2\in C$ and $x\in\dom\Lambda$.


Next, fixing $x\in\dom\Lambda=\fn_{\f_{(\pi,\Lambda)}}$, we can check $\|\Lambda(x)\|^2=\f(x^*x)=\|\Lambda_{\f_{(\pi,\Lambda)}}(x)\|^2$.
The rest is routine.

(c)
Suppose $\f$ is faithful.
If $x\in\fn$ satisfies $\Lambda(x)=0$, then $\f(x^*x)=\|\Lambda(x)\|^2=0$ implies $x=0$, so $\Lambda$ is injective.

Suppose $\Lambda$ is injective.
Take a non-zero $x\in\fn$ so that $\|\Lambda(x)\|^2>0$.
We claim $\f(x^*x)\ne0$.

(d)
Also clear.
\end{pf}


\begin{thm}
Let $\f$ is a weight on a von Neumann algebra $M$.
Then, $\f$ is normal if and only if $\f$ is $\sigma$-weakly lower semi-continuous.
\end{thm}
\begin{pf}
($\Rightarrow$)
Endow a partial order on the set of all weights.
Then, every set of monotonically increasing subadditive homogeneous functions $\f:M^+\to[0,\infty]$ always have its supremum given by its pointwise supremum.
Since if $\f$ is the supremum of $\sigma$-weakly lower semi-continuous $\f_i$, then
\[\f^{-1}([0,1])=\bigcap_i\f_i^{-1}([0,1])\]
implies the $\sigma$-weak lower semi-continuity of $\f$.
Conversly, the following theorem holds.

($\Leftarrow$)
Let $F:=\f^{-1}([0,1])$.
It is a hereditary closed convex subset of the real locally convex space $(M^{sa},\sigma w)$.
Denote by the superscript circle the real polar set.
Since
\[\cF_\f=F^{\circ+}=\{\omega\in M_*^+:\omega\le\f\},\qquad
F^{\circ+\circ+}=\{x\in M^+:\sup_{\omega\in\cF_\f}\omega(x)\le1\},\]
it is enough to show $F^{\circ+\circ+}=F$.
The positive part of the real polar of $F$ is generally written as
\[F^{\circ+}=F^\circ\cap M_*^+=F^\circ\cap(-M^+)^\circ=(F\cup-M^+)^\circ=(F-M^+)^\circ.\]
Consider a sequence of inclusions
\[F\subset\bar F\subset\bar{(F-M^+)^+}\subset\bar{(F-M^+)}^+\subset(F-M^+)^{\circ\circ+}=F^{\circ+\circ+}.\]
The first, second, and forth inclusions are in fact full because $F$ is closed, hereditary, and convex.
The forth one uses the bipolar theorem.
So we claim that the reverse of the third inclusion $\bar{(F-M^+)}^+\subset\bar{(F-M^+)^+}$.

Let $x\in\bar{(F-M^+)}^+$.
For arbitrary $\e>0$, it is enough to show $f_\e(x)\in F-M^+$ because $x\ge0$ implies $f_\e(x)\ge0$ and $f_\e(x)\uparrow x$ as $\e\to0$.
Let $x_\alpha$ be a net in $F-M^+$ that converges to $x$ $\sigma$-strongly, which can be done by the convexity of $F-M^+$.
Let $y_\alpha$ be a net in $F$ such that $f_{\e/2}(x_\alpha)\le y_\alpha$.
Since $f_{\e/2}(y_\alpha)$ is a bounded net, we may assume it is $\sigma$-weakly convergent.
By the $\sigma$-strong continuity of $f_\e$, the net $f_\e(x_\alpha)$ converges to $f_\e(x)$ $\sigma$-strongly, hence $\sigma$-weakly.
Therefore, by the closedness of $F$,
\[f_\e(x)=\lim_\alpha f_\e(x_\alpha)\le\lim_\alpha f_{\e/2}(y_\alpha)\in F,\]
so we conclude $f_\e(x)\in F-M^+$.
\end{pf}



\begin{lem}
Let 
For $z\in\fm^{sa}$, we have
\[\inf\{\f(a):z\le a\in\fm^+\}\le\|\theta(z)\|.\]
In particular, for $x,y\in\fn^+$ and for any $\e>0$ there is $a\in\fm^+$ such that $x^2-y^2\le a$ and
\[\f(a)\le\|\theta(x^2-y^2)\|+\e=\|\omega_{\Lambda(x)}-\omega_{\Lambda(y)}\|+\e.\]
\end{lem}
\begin{pf}
Denote by $p(z)$ the left-hand side of the inequality.
Then, we can check $p:\fm^{sa}\to\R_{\ge0}$ is a semi-norm such that $p(z)=\f(z)$ for $z\ge0$.
(If we take $p(z):=\f(z^+)$, then it seems to be dangerous when checking the sublinearity. I could not find the counterexample for $(z_1+z_2)^+\le z_1^++z_2^+$.)

Fix any non-zero $z_0\in\fm^{sa}$.
By the Hahn-Banach extension, there is an algebraic real linear functional $l:\fm^{sa}\to\R$ such that
\[l(z_0)=p(z_0),\qquad |l(z)|\le p(z),\qquad z\in\fm^{sa}.\]
Extend linearly $l$ to be $l:\fm\to\C$.
Since $|l(z)|\le\f(z)$ for $z\in\fm^+$, by the bounded Radon-Nikodym theorem, we have a corresponding operator $a\in\pi(M)'_1$ such that $\theta^*(a)=l$, hence
\[p(z_0)=l(z_0)=\theta^*(a)(z_0)=\theta(z_0)(a)\le\|\theta(z_0)\|.\]
Since $z_0\in\fm^{sa}$ is aribtrary, we are done.
\end{pf}



\begin{thm}
Let $\f$ is a weight on a von Neumann algebra $M$.
Then, $\f$ is $\sigma$-weakly lower semi-continuous if and only if $\f$ is order continuous.
\end{thm}
\begin{pf}
($\Rightarrow$)
Easy

($\Leftarrow$)
Let $\f$ be an order continuous weight on $M$.
We first claim that the associated semi-cyclic representation $(\pi,\Lambda)$ to $\f$ is normal if $M$ is countably decomposable.

Suppose a sequence $x_n\in\fn_1$ satisfies $x_n\to x$ $\sigma$-strongly in $M_1$ and $\Lambda(x_n)\to\xi$ in $H_1$.
Since $\Lambda(x_n)$ is Cauchy and bounded, $\omega_{\Lambda(x_n)}$ is also Cauchy in the norm topology of $B(H)_*$, so we may assume $\|\omega_{\Lambda(x_{n+1})}-\omega_{\Lambda(x_n)}\|<\e2^{-n}$, for arbitrarily taken $\e>0$.
In order to dominate $x_n$ with an monotone sequence, we take $a_n\in\fm^+$ such that $|x_{n+1}|^2-|x_n|^2\le a_n$ and $\f(a_n)<\e2^{-n}$ using the previous lemma.
Since the limit of the increasing sequence $\sum_{k=1}^n a_k$ in $n\to\infty$ may not exist, we introduce the cutoff $f_\e(t):=t(1+\e t)^{-1}$.
By taking the limit $\e\to0$ on the inequality
\[\f(f_\e(|x|^2))=\f(\lim_{n\to\infty}f_\e(|x_n|^2))\le\f(\sup_nf_\e(|x_1|^2+\sum_{k=1}^na_k))=\sup_n\f(f_\e(|x_1|^2+\sum_{k=1}^na_k))<1+\e,\]
we have $x\in(\fn_\f)_1$ and $\Lambda(x)\in H_1$.
Next, since $\Lambda(x_n-x)$ is Cauchy, we may assume $\|\omega_{\Lambda(x_n-x)}-\omega_{\Lambda(x_{n+1}-x)}\|<2^{-n}$.
Take $b_n\in\fm^+$ such that $|x_n-x|^2-|x_{n+1}-x|^2\le b_n$ and $\f(b_n)<2^{-n}$.
As we did previously, by taking $\e\to0$ on the inequality
\[\f(f_\e(|x_m-x|^2))=\f(\lim_{n\to\infty}f_\e(|x_m-x|^2-|x_n-x|^2))\le\f(\sup_nf_\e(\sum_{k=m}^nb_k))=\sup_n\f(f_\e(\sum_{k=m}^nb_k))<2^{-(m-1)},\]
we have $\|\Lambda(x_n)-\Lambda(x)\|^2=\f(|x_n-x|^2)\to0$ and $\xi=\lim_{n\to\infty}\Lambda(x_n)=\Lambda(x)$.
Thus $(\pi,\Lambda)$ is normal.


In the spirit of the Krein-\v Smulian theorem, the $\sigma$-weak lower semi-continuity is equivalent to the $\sigma$-weak closedness of the bounded part of the inverse image of the closed interval
\begin{align*}
\f^{-1}([0,1])_1
&=\{x\in M^+:\f(x)\le1,\ \|x\|\le1\}\\
&=\{x^*x\in\fm^+:\|\Lambda(x)\|\le1,\ \|x\|\le1\}.
\end{align*}
Since the $\sigma$-weak and strong closedness of a bounded convex set are equivalent and that the square root operation is strongly continuous, we are enough to show the square root
\[\f^{-1}([0,1])_1^{\frac12}=\{x\in\fn^+:\|\Lambda(x)\|\le1,\ \|x\|\le1\}\]
is $\sigma$-weakly closed.
This set, if we denote the graph of $\Lambda:\fn\to H$ by $\Gamma_\Lambda$, is exactly the image of the positive part of the unit ball
\[(\Gamma_\Lambda)^+_1=\{(x,\Lambda(x))\in\fn^+\oplus_\infty H:\|\Lambda(x)\|\le1,\ \|x\|\le1\}\]
under the projection $M\oplus_\infty H\to M$.
Observe $(x_\alpha,\xi_\alpha)$ converges to $(x,\xi)$ weakly$^*$ in $M\oplus_\infty H\cong(M_*\oplus_1H)^*$ if and only if $x_\alpha\to x$ $\sigma$-weakly and $\xi_\alpha\to\xi$ weakly.
Since the graph of $\Lambda$ and the closed ball in $M\oplus_\infty H$ is a closed with respect to the $\sigma$-weak topology of $\fn$ and the weak topology of $H$, their intersection $(\Gamma_\Lambda)_1^+$ is weakly$^*$ closed.
Therefore, by its compactness, $\f$ is $\sigma$-wealy lower semi-continuous done provided $M$ is countably decomposable.


Now, let $M$ be an arbitrary von Neumann algebra, and let $\f$ be a order continuous weight on $M$.
Let $\Sigma$ be the set of all countably decomposable projections of $M$ and let $M_0:=\bigcup_{p\in\Sigma}pMp$.
The equivalent condition for $x\in M$ to belong to $M_0$ is that the left and right support projections of $x$ are countably decomposable.
Since then the left support projection $p$ and the right support projection $q$ of $x$ are Murray-von Neumann equivalent so that there is a $*$-isomorphism between $pMp$ and $qMq$, the countable decomposability is equivalent for $p$ and $q$.
It implies that $M_0$ is an algebraic ideal of $M$.
(Moreover, $M_0$ is $\sigma$-weakly sequentially closed in $M$ since if a sequence $x_n\in M_0$ converges to $x\in M$ $\sigma$-weakly, then for $p_n\in\Sigma$ such that $x_n=p_nx_np_n$, we have $p\in\Sigma$ with $p_n\le p$ so that $x_n=px_np$ converges to $x=pxp$ $\sigma$-weakly.
This fact is not needed in the proof.)

We first claim that $\f^{-1}([0,1])_1$ is relatively $\sigma$-weakly closed in $M_0$.
Let $y\in\bar{\f^{-1}([0,1])_1}^{\sigma w}\cap M_0$ so that there is a net $y_\alpha\in\f^{-1}([0,1])_1$ converges $\sigma$-weakly to $y$, and there is $p\in\Sigma$ such that $pyp=y$.
Note that the previous theorem states that $\f^{-1}([0,1])\cap pMp$ is $\sigma$-weakly closed.
Since $py_\alpha p$ is a net in $\f^{-1}([0,1])_1\cap pMp$ that also converges $\sigma$-weakly to $pyp=y$, we have $y\in\f^{-1}([0,1])$.
The claim proved.

We now claim that $\f^{-1}([0,1])_1$ is $\sigma$-weakly closed in $M$.
Suppose a net $x_\alpha\in\f^{-1}([0,1])_1$ converges to $x\in M$ $\sigma$-weakly.
Clearly $x\in M_1^+$.
Let $\{p_i\}_{i\in I}$ be a maximal mutually orthogonal projections in $\Sigma$, and let $p_J:=\sum_{i\in J}p_i$ for finite sets $J\subset I$ so that $\sup_Jp_J=1$.
It clearly follows that for each $\alpha$ we have
\[x_\alpha^{\frac12}p_Jx_\alpha^{\frac12}\in\f^{-1}([0,1])_1.\]
Then, we can show easily with boundedness of $x_\alpha$ that
\[x^{\frac12}p_Jx^{\frac12}\in\bar{\f^{-1}([0,1])_1}^{\sigma w}.\]
Because $p_J\in M_0$ and $M_0$ is an ideal, 
\[x^{\frac12}p_Jx^{\frac12}\in\bar{\f^{-1}([0,1])_1}^{\sigma w}\cap M_0.\]
By the above claim,
\[x^{\frac12}p_Jx^{\frac12}\in\f^{-1}([0,1])_1.\]
By the complete additivity of $\f$, we finally obtain
\[x\in\f^{-1}([0,1])_1.\]
Therefore, $\f^{-1}([0,1])_1$ is $\sigma$-weakly closed.
\end{pf}





\newpage
\section{November 10}
\subsection{Hilbert algebras}

\begin{defn}[Left Hilbert algebra]
A \emph{left Hilbert algebra} is a $*$-algebra $A$ together with an inner product such that the involution is closable on $H$ and the square $A^2$ is dense in $H$, where $H:=\bar A$.
A left Hilbert algebra $A$ has the following additional devices:
\begin{enumerate}[(i)]
\item a closable densely defined anti-linear operator $S:A\to H$, defined by the involution,
\item a faithful non-degenerate $*$-homomorphism $\lambda:A\to B(H)$, defined by the left multiplication.
\end{enumerate}
The \emph{associated von Neumann algebra} of a left Hilbert algebra $A$ is defined as $M:=\lambda(A)''$.
\end{defn}

\begin{defn}[Right Hilbert algebra]
Let $A$ be a left Hilbert algebra.
For $\eta\in H$, define:
\begin{enumerate}[(i)]
\item a linear functional $F\eta:A\to\C$ such that $F\eta(\xi):=\<\eta,S\xi\>$ for $\xi\in A$,
\item a linear operator $\rho(\eta):A\to H$ such that $\rho(\eta)\xi:=\lambda(\xi)\eta$ for $\xi\in A$.
\end{enumerate}
Define also:
\[D':=\{\eta\in H\mid F\eta\text{ is bounded}\},\qquad
B':=\{\eta\in H\mid \rho(\eta)\text{ is bounded}\},\qquad
A':=B'\cap D'.\]
Then, for $\eta\in D'$, we can identify $F\eta$ with a vector in $H$ by the Riesz representation theorem, and for $\eta\in B'$, we can identify $\rho(\eta)$ with an element of $B(H)$.
\end{defn}


\begin{prop}
Let $A$ be a left Hilbert algebra.
\begin{parts}
\item $A'$ is a $*$-algebra such that $\eta^*:=F\eta$ and $\eta\zeta:=\rho(\zeta)\eta$.
\item $\rho(A')A'$ is dense in $H$.
\item $A'$ is a right Hilbert algebra such that $\bar{A'}=H$.
\end{parts}
\end{prop}
\begin{pf}
(a)
Combining from (i) to (iv) in the below, the claim follows clearly:

(i)
For $\eta\in D'$, we have $FF\eta=\eta$ in $H$ by
\[FF\eta(\xi)=\<F\eta,S\xi\>=\<SS\xi,\eta\>=\<\xi,\eta\>,\qquad\xi\in A.\]
Therefore, if $\eta\in D'$, then $F\eta\in D'$.

(ii)
For $\eta\in D'$, we have $\rho(F\eta)=\rho(\eta)^*$ on $A$ by
\begin{align*}
\<\rho(F\eta)\xi,\xi\>
&=\<\lambda(\xi)F\eta,\xi\>
=\<F\eta,\lambda(\xi)^*\xi\>
=\<S\lambda(\xi)^*\xi,\eta\>\\
&=\<\lambda(\xi)^*\xi,\eta\>
=\<\xi,\lambda(\xi)\eta\>
=\<\xi,\rho(\eta)\xi\>
=\<\rho(\eta)^*\xi,\xi\>
,\qquad\xi\in A.
\end{align*}
Therefore, if $\eta\in A'$, then $F\eta\in B'$.

(iii)
For $\eta,\zeta\in B'$, we have $F(\rho(\eta)^*\zeta)=\rho(\zeta)^*\eta$ in $H$ by
\begin{align*}
\<F(\rho(\eta)^*\zeta),\xi\>
&=\<S\xi,\rho(\eta)^*\zeta\>
=\<\rho(\eta)S\xi,\zeta\>
=\<\lambda(\xi)^*\eta,\zeta\>\\
&=\<\eta,\lambda(\xi)\zeta\>
=\<\eta,\rho(\zeta)\xi\>
=\<\rho(\zeta)^*\eta,\xi\>
,\qquad\xi\in A.
\end{align*}
Therefore, if $\eta,\zeta\in B'$, then $\rho(\eta)^*\zeta\in D'$.

(iv)
For $\eta\in B'$ and $\zeta\in H$, we have $\rho(\rho(\eta)^*\zeta)=\rho(\eta)^*\rho(\zeta)$ on $A$ by
\begin{align*}
\<\rho(\rho(\eta)^*\zeta)\xi,\xi\>
&=\<\lambda(\xi)\rho(\eta)^*\zeta,\xi\>
=\<\zeta,\rho(\eta)\lambda(\xi)^*\xi\>
=\<\zeta,\lambda(\lambda(\xi)^*\xi)\eta\>\\
&=\<\zeta,\lambda((S\xi)\xi)\eta\>
=\<\zeta,\lambda(\xi)^*\lambda(\xi)\eta\>
=\<\lambda(\xi)\zeta,\lambda(\xi)\eta\>\\
&=\<\rho(\zeta)\xi,\rho(\eta)\xi\>
=\<\rho(\eta)^*\rho(\zeta)\xi,\xi\>
,\qquad\xi\in A.
\end{align*}
Therefore, if $\eta,\zeta\in B'$, then $\rho(\eta)\zeta\in B'$.


(b)
Since $D'$ is dense in $H$ by the closability of $S$, it suffices to verify the inclusion $D'\subset\bar{\rho(A')A'}$.
Let $\eta\in D'$.
Since $\rho(\eta)$ has densely defined adjoint $\rho(F\eta)$, we may assume $\rho(\eta)$ to be closed and densely defined by taking closure, so we can write down the polar decomposition
\[\rho(\eta)=vh=kv,\qquad h:=|\rho(\eta)|,\quad k:=|\rho(\eta)^*|.\]
To control the unboundedness of $\rho(\eta)$, we introduce $f\in C_c((0,\infty))^+$ to cutoff $\rho(\eta)$.
Let $\acute f(t):=tf(t)$ and $\grave f(t):=t^{-1}f(t)$.
Now we have $f(k)\in\rho(B')$ since $f(k)$ is bounded and
\[f(k)=f(vhv^*)=vf(h)v^*=v\grave f(h)\rho(\eta)^*=\rho\left(v\grave f(h)F\eta\right).\]
We also have $f(k)\eta\in B'$ since
\[\rho(f(k)\eta)=f(k)\rho(\eta)=\acute f(k)v\]
is bounded.
Applying the above arguments for $f^{\frac13}\in C_c((0,\infty))$, 
\[f(k)\eta=(f(k)^{\frac13})^3\eta\in\rho(B')^*\rho(B')\rho(B')^*B'.\]
Because $\rho(B')^*B'\subset A'$ and $\rho(B')^*\rho(B)\subset\rho(A')$ by (iii) and (iv) in the part (a), we have $f(k)\eta\in\rho(A')A'$.

If we construct a non-decreasing net $f_\alpha\in C_c((0,\infty))$ such that $\sup_\alpha f_\alpha=1_{(0,\infty)}$, then the strong limit implies
\[\lim_\alpha f_\alpha(k)\eta=1_{(0,\infty)}(k)\eta=s(k)\eta=s_l(\rho(\eta))\eta.\]
Here we use the non-degeneracy of $\lambda$ to verify $\eta$ belongs to the closure of the range of $\rho(\eta)$, i.e.~since $M$ contains the identity operator on $H$, we have a net $\xi_\alpha\in A$ such that $\lambda(\xi_\alpha)$ converges to the identity strongly so that $\lambda(\xi_\alpha)\eta\to\eta$.
It implies that $\eta\in\bar{\lambda(A)\eta}=\bar{\rho(\eta)A}$ and $s_l(\rho(\eta))\eta=\eta$.
Therefore, $\eta=s_l(\rho(\eta))\eta\in\bar{\rho(A')A'}$.

(c)
The involution $F:A'\to H$ is a closable densely defined anti-linear operator because $A'$ is dense in $H$ by (b) and the closability follows from the dense domain of its adjoint $S$.
The right multiplication $\rho:A'^\op\to B(H)$ is a faithful non-degenerate $*$-homomorphism because $\rho(A')H$ is dense in $H$ by (b) and the faithfulness follows from the non-degeneracy of $\lambda$.
Therefore, $A'$ is a right Hilbert algebra with $\bar A'=H$.
\end{pf}


\begin{cor}
$\rho(A')'=M$.
\end{cor}
\begin{pf}
One direction is clear, i.e.~$\rho(A')\subset M'$ implies $\rho(A')''\subset M'$.
Conversely, let $y\in M'^+$.
Since $\rho:A'^{\operatorname{op}}\to B(H)$ is non-degenerate, there is a net $\eta_\alpha\in A'$ such that $\rho(\eta_\alpha)$ converges to the identity $\sigma$-weakly.
Then,
\[\rho(\eta_\alpha)^*y\rho(\eta_\alpha)=\rho(y^{\frac12}\eta_\alpha)^*\rho(y^{\frac12}\eta_\alpha)\in\rho(B')^*\rho(B')\subset\rho(A')\]
converges to $y$ $\sigma$-weakly, hence $y\in\rho(A')''$.
\end{pf}

\begin{defn}[Full Hilbert algebra]
Let $A$ be a left Hilbert algebra.
Symmetrically as above, starting from the right Hilbert algebra $A'$, we can construct a left Hilbert algebra $A''$.
We say $A$ is \emph{full} if $A=A''$.
\end{defn}


\begin{defn}[Modular operator and conjugation]
Let $A$ be a left Hilbert algebra.
Denote the polar decomposition of $S$ by $S=J\Delta^{\frac12}$.
The unbounded operators $\Delta$ and $J$ are called the \emph{modular operator} and the \emph{modular conjugation}.
\end{defn}

\begin{cor}
From the polar decomposition theorem for unbounded (anti-)linear operators, we have
\begin{parts}
\item $S$ is injective with $S=S^{-1}$ and $D=\dom S=\dom\Delta^{\frac12}$.
\item $F$ is injective with $F=F^{-1}$ and $D'=\dom F=\dom\Delta^{-\frac12}$.
\item $\Delta$ is an injective positive self-adjoint operator.
\item $J$ is a conjugation, i.e.~an anti-linear isometric involution.
\item $S=J\Delta^{\frac12}=\Delta^{-\frac12}J$, $F=J\Delta^{-\frac12}=\Delta^{\frac12}J$, and $J\Delta J=\Delta^{-1}$.
\end{parts}
\end{cor}





\subsection{Faithful semi-finite normal weights}

\begin{defn}
Let $\f$ be a weight on a von Neumann algebra $M$.
We say $\f$ is \emph{faithful} if $\f(x^*x)=0$ implies $x=0$ for $x\in\fn$.
We say $\f$ is \emph{semi-finite} if $\fm$ is $\sigma$-weakly dense in $M$.
Recall that a weight $\f$ on a von Neumann algebra $M$ is normal if and only if it is obtained by the pointwise supremum of a set of normal positive linear functionals.
\end{defn}

In the proofs of theorems of this section, the following diagram might be helpful: 
\[\begin{tikzcd}
\fm:=\fn^*\fn \rar[phantom,"\subset"] & \fa:=\fn\cap\fn^* \rar[phantom,"\subset"]\dar[shift left]{\Lambda} & \fn \rar[phantom,"\subset"]\dar[shift left]{\Lambda} & \pi(M) \rar[phantom,"\subset"] & B(H)\\
& A \rar[phantom,"\subset"]\uar[shift left]{\lambda} & B \rar[phantom,"\subset"]\uar[shift left]{\lambda} & H.
\end{tikzcd}\]
Recall that for a weight $\f$ on a von Neumann algebra $M$ and its semi-cyclic representation $(\pi,\Lambda)$ of $M$ we have $\f(x^*x)=\|\Lambda(x)\|^2$ for $x\in\fn$.


\begin{thm}
Let $M$ be a von Neumann algebra.
If $A$ is a full left Hilbert algebra together with a faithful normal non-degenerate representation $\pi:M\to B(H)$ such that $\lambda(A)''=\pi(M)$, then
\[\f(x^*x):=\begin{cases}\|\xi\|^2&\text{ if }\pi(x)=\lambda(\xi)\in\lambda(B),\\\infty&\text{ otherwise},\end{cases}\]
is a faithful semi-finite normal weight on $M$.
\end{thm}
\begin{pf}
We use the notation $x=\pi(x)$.
We first check that the weight $\f$ is well-defined.
Let $x_1=\lambda(\xi_1),x_2=\lambda(\xi_2)\in\lambda(B)$ such that $x_1^*x_1=x_2^*x_2$.
Since $x_1,x_2\in M$, we have a partial isometry $v\in M$ such that $x_2=vx_1$ and $v^*v=s_l(x_1)$, and it is not diffcult to see $\xi_2=v\xi_1$.
As we know $s_l(x)\xi_1=\xi_1$,
\[\|\xi_2\|^2=\<\xi_2,\xi_2\>=\<v\xi_1,v\xi_1\>=\<v^*v\xi_1,\xi_1\>=\<\xi_1,\xi_1\>=\|\xi_1\|^2,\]
which proves the well-definedness.

With this weight $\f$, we can see
\[\fn=\lambda(B),\qquad\fa=\lambda(A),\qquad\fm=\lambda(B)^*\lambda(B).\]
The first one is by definition of $\f$, and the third one is by definition of $\fm$.
Since $A$ is full so that $A=B\cap D$, $\lambda$ is injective, $\lambda(A)^*=\lambda(A)$, and $\lambda(D)^*=\lambda(D)$, we have $\lambda(A)=\lambda(B)\cap\lambda(D)=\lambda(B)^*\cap\lambda(D)$, which implies $\lambda(A)=\lambda(B)\cap\lambda(B)^*\cap\lambda(D)$.
If $\xi_1,\xi_2\in B$ satisfy $\lambda(\xi_1)=\lambda(\xi_2)^*$, then
\begin{align*}
S\xi_1(\rho(\eta)^*\zeta)
&=\<F\rho(\eta)^*\zeta,\xi_1\>
=\<\rho(\zeta)^*\eta,\xi_1\>
=\<\eta,\rho(\zeta)\xi_1\>
=\<\eta,\lambda(\xi_1)\zeta\>\\
&=\<\lambda(\xi_2)\eta,\zeta\>
=\<\rho(\eta)\xi_2,\zeta\>
=\<\xi_2,\rho(\eta)^*\zeta\>,
\qquad\eta,\zeta\in A'.
\end{align*}
We have $\xi_1\in D$ by the density of $A'^2$ in $H$, so $\lambda(B)\cap\lambda(B)^*\subset\lambda(D)$, hence the second equality follows.

From now in the rest of proof, we will always denote $y=\rho(\eta)$ and $z=\rho(\zeta)$ for $y,z\in\fn'$.
The weight $\f$ is clearly faithful, and semi-finiteness follows from the assumption $\fa''=\lambda(A)''=M$ that a net $e_\alpha$ in $\fa$ convergent $\sigma$-strongly/weakly to the identity has a $\sigma$-weak limit $x=\lim_\alpha e_\alpha xe_\alpha\in\fm''$ for $x\in M$.
To verify the normality of $\f$, we will show
\[\f(x^*x)=\sup_{y\in\fn'_1}\omega_{\eta}(x^*x),\qquad x\in\fn,\]
where $\fn':=\rho(B')$.

($\ge$)
We may assume $x=\lambda(\xi)\in\fn=\lambda(B)$ so that $\f(x^*x)<\infty$.
Since the unit ball $\fn'_1$ has a net $y_\alpha$ that converges to $\id_H$ strongly by the Kaplansky density theorem, we have an inequality
\[\omega_{\eta_\alpha}(x^*x)=\|x\eta_\alpha\|^2=\|\lambda(\xi)\eta_\alpha\|^2=\|\rho(\eta_\alpha)\xi\|^2=\|y_\alpha\xi\|^2\le\|\xi\|^2=\f(x^*x),\]
in which the equality condition is attained at its limit.

($\le$)
Suppose $x\in M$ is taken such that the right-hand side $\sup_{y\in\fn'_1}\omega_{\eta}(x^*x)$ is finite.
If we show $x\in\fn$, then we are done from $\f(x^*x)<\infty$ by the previous argument.
To motivate the strategy, consider the opposite weight
\[\f'(y^*y):=\begin{cases}\|\eta\|^2&\text{ if }y\in\rho(B'),\\\infty&\text{ otherwise},\end{cases}\]
and the associated linear map
\[\theta'^*:M\to\fm'^\#:x^*x\mapsto(z^*y\mapsto\<x^*x\eta,\zeta\>),\qquad y,z\in\fn',\]
where we can check $\fm'=\rho(B')^*\rho(B')$.
The idea is to show a well-designed linear functional $l\in\fm'^\#$ such that $l=\theta'^*(x^*x)$ is contained in the image $\theta'^*(\fm)$ using the assumption that the right-hand side is finite to verify $x\in\fn$.

Define a linear functional
\[l:\fm'\to\C:z^*y\mapsto\<x^*x\eta,\zeta\>.\]
Then, by the assumption we have
\[\|l\|=\sup_{y\in\fn'_1}\<x^*x\eta,\eta\>=\sup_{y\in\fn'_1}\omega_\eta(x^*x)<\infty,\]
and
\[|l(y)|\le\|l\|l(y^*y)^{\frac12}=\|l\|\|x\eta\|,\qquad y\in\fn'\]
implies the well-definedness as well as boundedness of the linear functional $\bar{xH}\to\C:x\eta\mapsto l(y)$ for any $\eta\in H$, and it follows the existence of $\xi\in\bar{xH}$ such that
\[l(y)=\<x\eta,\xi\>,\qquad y\in\fn'\]
by the Riesz representation theorem on $\bar{xH}$.
We have $\lambda(\xi)\zeta\in\bar{xH}$ and
\begin{align*}
\<x\eta,x\zeta\>&=l(z^*y)=\<x\rho^{-1}(z^*y),\xi\>=\<xz^*\eta,\xi\>\\
&=\<z^*x\eta,\xi\>=\<x\eta,z\xi\>=\<x\eta,\rho(\zeta)\xi\>=\<x\eta,\lambda(\xi)\zeta\>,\qquad y,z\in\fn',
\end{align*}
hence $x=\lambda(\xi)$.
The vector $\xi$ is left bounded by definition and $x=\lambda(\xi)\in\lambda(B)=\fn$.
\end{pf}

\begin{thm}
Let $M$ be a von Neumann algebra.
If $\f$ is a faithful semi-finite normal weight on $M$ and $(\pi,\Lambda,H)$ is the associated semi-cyclic representation of $M$, then $A:=\Lambda(\fa)$ is a full left Hilbert algebra with
\[\Lambda(x_1)\Lambda(x_2):=\Lambda(x_1x_2),\qquad\Lambda(x)^*:=\Lambda(x^*),\]
such that $\lambda(A)''=\pi(M)$.
\end{thm}
\begin{pf}
We use the notation $x=\pi(x)$.
It does not make any confusion because the semi-cyclic representation $\pi:M\to B(H)$ is always unital and is faithful due to the assumption that $\f$ is faithful.
We clearly see that $A$ is a $*$-algebra and the left multiplication provides a $*$-homomorphism $\lambda:A\to B(H)$.
By the construction of the semi-cyclic representation associated to $\f$, $A$ is dense in $H$.
We need to show the non-degeneracy of $\lambda$, the closability of the involution, and the fullness of $A$.

(non-degeneracy)
Since $\f$ is semi-finite, there is a net $x_\alpha$ in $\fa_1$ converges strongly to the identity of $M$ by the Kaplansky density theorem.
Then, it follows that $\lambda$ is non-degenerate from
\[\lambda(\Lambda(x_\alpha))\Lambda(x)=\Lambda(x_\alpha x)=x_\alpha\Lambda(x)\to\Lambda(x),\qquad x\in\fa.\]

(closability)
We need to prove the domain of the adjoint
\[D':=\{\eta\in H\mid A\to\C:\Lambda(x)\mapsto\<\eta,\Lambda(x^*)\>\text{ is bounded}\}\]
is dense in $H$.
Let
\[\cG:=\{\omega\in M_*^+:(1+\e)\omega\le\f\text{ for some }\e>0\}.\]
Note that the normality of $\f$ says that $\f(x^*x)=\sup_{\omega\in\cG}\omega(x^*x)$ for any $x\in M$.
For each $\omega\in\cG$, by the bounded Radon-Nikodym theorem, there is $h_\omega\in M'^+$ such that $\|h_\omega\|<1$ and
\[\omega(x^*x)=\<h_\omega\Lambda(x),\Lambda(x)\>,\qquad x\in\fn.\]
Also, if we take a net $x_\alpha\in\fn_1$ that converges $\sigma$-strongly to the identity of $M$ using the strong density of $\fn$ in $M$, the Kaplansky density, and the coincidence of strong and the $\sigma$-strong topologies on the bounded part, then we have a $\sigma$-weak limit $\lim_{\alpha,\beta}|x_\alpha-x_\beta|^2=0$ so that by the normality of $\omega$ we obtain
\[\lim_{\alpha,\beta}\|h_\omega^{\frac12}\Lambda(x_\alpha)-h_\omega^{\frac12}\Lambda(x_\beta)\|^2=\lim_{\alpha,\beta}\omega(|x_\alpha-x_\beta|^2)=0.\]
Thus, the vector $\Lambda_\omega:=\lim_\alpha h_\omega^{\frac12}\Lambda(x_\alpha)$ can be defined, and in particular, we have $h_\omega^{\frac12}\Lambda(x)=x\Lambda_\omega$ for $x\in\fn$ and $\omega=\omega_{\Lambda_\omega}$.

If $\eta:=h_{\omega_2}^{\frac12}y\Lambda_{\omega_1}$ for some $y\in M'$ and $\omega_1,\omega_2\in\cG$, then
\begin{align*}
|\<\eta,\Lambda(x^*)\>|
&=|\<h_{\omega_2}^{\frac12}y\Lambda_{\omega_1},\Lambda(x^*)\>|=|\<y\Lambda_{\omega_1},h_{\omega_2}^{\frac12}\Lambda(x^*)\>|=|\<y\Lambda_{\omega_1},x^*\Lambda_{\omega_2}\>|\\
&=|\<yx\Lambda_\omega,\Lambda_{\omega_2}\>|=|\<yh_{\omega_1}^{\frac12}\Lambda(x),\Lambda_{\omega_2}\>|=|\<\Lambda(x),h_{\omega_1}^{\frac12}y^*\Lambda_{\omega_2}\>|\\
&\le\|\Lambda(x)\|\|h_{\omega_1}^{\frac12}y^*\Lambda_{\omega_2}\|,\qquad x\in\fa,
\end{align*}
which deduces that $\eta\in D'$.
Therefore, it suffices to show the following space is dense in $H$:
\[\{h_{\omega_2}^{\frac12}y\Lambda_{\omega_1}:\omega_1,\omega_2\in\cG,\ y\in M'\}.\]
Thanks to the normality of $\f$, we can write
\begin{align*}
\<\Lambda(x),\Lambda(x)\>&=\|\Lambda(x)\|^2=\f(x^*x)=\sup_{\omega\in\cG}\omega(x^*x)\\
&=\sup_{\omega\in\cG}\|x\Lambda_\omega\|^2=\sup_{\omega\in\cG}\|h_\omega^{\frac12}\Lambda(x)\|^2=\sup_{\omega\in\cG}\<h_\omega\Lambda(x),\Lambda(x)\>,\qquad x\in\fa.
\end{align*}
Because $A$ in $H$, for any $\xi\in H$ and $\e>0$ there is $x\in\fn\cap\fn^*$ such that $\|\xi-\Lambda(x)\|<\e$, so the inequality
\[\<(1-h_\omega)\xi,\xi\>\le\e(\|\xi\|+\|\Lambda(x)\|)+\<(1-h_\omega)\Lambda(x),\Lambda(x)\>\]
deduces $\inf_{\omega\in\Phi}\<(1-h_\omega)\xi,\xi\>=0$ by limiting $\e\to0$ and taking infinimum on $\omega\in\cG$.
In other words, for each $\xi\in H$ and $\e>0$, we can find $\omega\in\cG$ such that $\<(1-h_\omega)\xi,\xi\><\e$.
At this point, we claim the set $\{h_\omega:\omega\in\cG\}$ is upward directed.
If the claim is true, then we can construct an increasing net $\omega_\alpha$ in $\cG$ such that $h_{\omega_\alpha}$ converges weakly to the identity of $M$, and also strongly by the nature of increasing nets.
To prove the claim, take $h_1=h_{\omega_1}$ and $h_2=h_{\omega_2}$ with $\omega_1,\omega_2\in\cG$.
Introduce a operator monotone function $f(t):=t/(1+t)$ and its inverse $f^{-1}(t)=t/(1-t)$ to define 
\[h_0:=f(f^{-1}(h_1)+f^{-1}(h_2)).\]
Then, we have $h_0\ge h_1$, $h_0\ge h_2$, and $\|h_0\|<1$.
Consider a linear functional
\[\omega_0:\fn\to\C:x\mapsto\<h_0\Lambda(x),\Lambda(x)\>.\]
Write
\begin{align*}
\omega_0(x^*x)
&\le\<f^{-1}(h_1)\Lambda(x),\Lambda(x)\>+\<f^{-1}(h_2)\Lambda(x),\Lambda(x)\>\\
&\le(1-\|h_1\|)^{-1}\<h_1\Lambda(x),\Lambda(x)\>+(1-\|h_2\|)^{-1}\<h_2\Lambda(x),\Lambda(x)\>\\
&=(1-\|h_1\|)^{-1}\omega_1(x^*x)+(1-\|h_2\|)^{-1}\omega_2(x^*x),\qquad x\in\fn.
\end{align*}
Then, since $\omega_1$ and $\omega_2$ are normal, we can define $\Lambda_0:=\lim_\alpha h_0^{\frac12}\Lambda(x_\alpha)\in H$ for a $\sigma$-strongly convergent net $x_\alpha\in\fn_1$ to the identity of $M$ as we have taken above, and we have the vector functional $\omega_0=\omega_{\Lambda_0}$.
Henceforth, $\omega_0$ is extended to a normal positive linear functional on the whole $M$, and finally the norm condition $\|h_0\|<1$ tells us that $\omega_0\in\cG$, so the claim is true.

Now the problem is reduced to the density of $\{y\Lambda_{\omega}:\omega\in\cG,\ y\in M'\}$ in $H$.
Let $p\in B(H)$ be the projection to the closure of this space.
Then, $p\Lambda_\omega=\Lambda_\omega$ for every $\omega\in\cG$.
Since the space is left invariant under the action of the self-adjoint set $M'$, we have $p\in M$.
Then,
\[\f(1-p)=\sup_{\omega\in\cG}\omega(1-p)=\sup_{\omega\in\cG}\<(1-p)\Lambda_\omega,\Lambda_\omega\>=0\]
implies $p=1$, hence the density.

(fullness)
We have $\lambda(\Lambda(x))=x$ for $x\in\fa$ since $\Lambda(\fa)=A$ is dense in $H$ and
\[x_1\Lambda(x_2)=\Lambda(x_1x_2)=\Lambda(x_1)\Lambda(x_2)=\lambda(\Lambda(x_1))\Lambda(x_2),\qquad x_1,x_2\in\fn\cap\fn^*.\]
Also we have for $\xi=\Lambda(x)\in A$ that
\[\Lambda(\lambda(\xi))=\Lambda(\lambda(\Lambda(\xi)))=\Lambda(x)=\xi.\]
For $\xi\in B$ so that $\lambda(\xi)\in M$, since
\[\f(\lambda(\xi)^*\lambda(\xi))=\|\Lambda(\lambda(\xi))\|^2=\|\xi\|^2<\infty,\]
we get $\lambda(B)\subset\fn$.
Therefore, $A$ is full by
\[\lambda(A'')=\lambda(B)\cap\lambda(B)^*\subset\fa=\lambda(A).\qedhere\]
\end{pf}

\begin{cor}
The operations giving a faithful semi-finite normal weight and a full left Hilbert algebra in the above two theorems are mutually inverses of each other.
\end{cor}

\begin{prop}
Every von Neumann algebra admits a faithful semi-finite normal weight.
\end{prop}
\begin{pf}
Let $M$ be a von Neumann algebra and let $\{\omega_i\}_{i\in I}$ be a maximal family of normal states on $M$ with orthogonal support projections $p_i:=s(\omega_i)$.
Here, the support projection $s(\omega)$ of a normal state $\omega$ is the minimal projection $p$ such that $\omega(px)=\omega(x)=\omega(xp)$ for all $x\in M$.
Since every countably decomposable projection $p$ is a support of a normal state, a faithful normal state on $pMp$, we have $\sum_ip_i=1$.
Define a weight $\f$ by
\[\f(x):=\sum_{i\in I}\omega_i(x)=\sup_{J\Subset I}\sum_{i\in J}\omega_i(x).\]
It is faithful because $\f(x)=0$ with $x\ge0$ means $\omega_i(x)=0$ and $p_ixsp_i=0$ for all $i$, and it implies
\[x^{\frac12}=x^{\frac12}\sum_ip_i=\sum_ix^{\frac12}p_i=0.\]
It is normal because it is the supremum of normal positive linear functionals $\omega_J=\sum_{i\in J}\omega_i$.
It is semi-finite because $p_J\uparrow1$ with $\f(p_J)<\infty$ as $J\to I$, where $p_J:=\sum_{i\in J}p_i$ and $J$ runs through finite subsets of $I$.
\end{pf}



\subsection{Examples}




\begin{ex}[Locally compact groups]
For a locally compact group $G$, the set $A:=C_c(G)$ together with a left Haar measure on $G$ has the following left Hilbert algebra structure
\[\<\xi_1,\xi_2\>:=\int\bar{\xi_2(s)}\xi_1(s)\,ds,\qquad(\xi_1\xi_2)(s):=\int_G\xi_1(t)\xi_2(t^{-1}s)\,dt,\qquad\xi^*(s):=\Delta(s^{-1})\bar{\xi(s^{-1})}.\]
We have $S$, $F$, $\Delta$, and $J$ given by
\[S\xi(s):=\Delta(s^{-1})\bar{\xi(s^{-1})},\qquad F\xi(s)=\bar{\xi(s^{-1})},\]
\[\Delta\xi(s)=\Delta(s)\xi(s),\qquad J\xi(s)=\Delta(s)^{-\frac12}\bar{\xi(s^{-1})},\]
and they have the following norm formulas
\[\|S\xi\|_2=\|\Delta^{\frac12}\xi\|_2,\quad\|F\xi\|_2=\|\Delta^{-\frac12}\xi\|_2,\quad\|S\xi\|_1=\|\xi\|_1,\quad\|F\xi\|_1=\|\Delta^{-1}\xi\|_1.\]
The left von Neumann algebra $\lambda(A)''$ is called the \emph{group von Neumann algebra}.
\iffalse
The left involution $S$ is an isometric anti-linear automorphism of $L^1(G)=L^1(G,ds)$, but the right involution $F$ defines an isometric anti-linear isomorphism between $L^1(G,ds)$ and $L^1(G,ds^{-1})$.
To sum up,
\[\begin{array}{lrl}
\xi\in H &\Leftrightarrow& \|\xi\|_2<\infty,\\
\xi\in D &\Leftrightarrow& \|S\xi\|_2+\|\xi\|_2<\infty,\\
\xi\in A &\Rightarrow& \|\lambda(\xi)\|+\|S\xi\|_2+\|\xi\|_2<\infty,\\
\xi\in B' &\Leftrightarrow& \|\rho(\xi)\|+\|\xi\|_2<\infty,\\
\xi\in D' &\Leftrightarrow& \|F\xi\|_2+\|\xi\|_2<\infty,\\
\xi\in A' &\Leftrightarrow& \|\rho(\xi)\|+\|F\xi\|_2+\|\xi\|_2<\infty,\\
\xi\in B &\Leftrightarrow& \|\lambda(\xi)\|+\|\xi\|_2<\infty,\\
\xi\in A'' &\Leftrightarrow& \|\lambda(\xi)\|+\|S\xi\|_2+\|\xi\|_2<\infty.
\end{array}\]
\fi

For a locally compact abelian group $G$, the corresponding f.n.s.~weight is a suitably normalized Haar measure on the Pontryagin dual group $\hat G$, called the Plancherel measure, not the Haar measure on the original group $G$.
For a locally compact non-abelian group $G$, there is no characterization of the corresponding f.n.s.~weight as a measure because the left Hilbert algebra $(C_c(G),*)$ is not commutative.
\end{ex}

\begin{ex}[Locally compact abelian groups]
If $G$ is a locally compact abelian group, then $A=\cF^{-1}(L^2(\hat G)\cap L^\infty(\hat G))$ is a full Hilbert algebra, where $\cF:L^2(G)\to L^2(\hat G)$ is the Fourier transform, such that $B=A$, $D=H=L^2(G)$.
\end{ex}

\begin{ex}[Measure spaces]
If $(X,\mu)$ is a $\sigma$-finite measure space, then $L^2(X)\cap L^\infty(X)$ is a full Hilbert algebra.
\end{ex}


\begin{ex}[Cyclic separating vector]
Let $M$ be a countably decomposable von Neumann algebra and $\omega$ be a faithful normal state.
If we consider the associated cyclic representation of $\omega$, then we have an action of $M$ on $H$ together with a cyclic separating vector $\Omega\in H$.
Then, $A:=M\Omega$ has the following left Hilbert algebra structure:
\[\<x\Omega,y\Omega\>\text{ is defined as it is},\qquad (x\Omega)(y\Omega):=xy\Omega,\qquad (x\Omega)^*:=x^*\Omega.\]
There is no specific description of $\Delta$ and $J$ in general, but it is known that $\fn=\fa=\fm=M$ so that $A=B=M\Omega$ is full, and
\[D=\{c\Omega:c\in C(H)\text{ affiliated with $M$ such that }\Omega\in\dom c\cap\dom c^*\}.\]
\end{ex}










\newpage
\section{December 20}

\subsection{Pettis integral}

\begin{defn}[Properties of dual pairs]
Let $(X,F)$ be a dual pair.
For example, if $X$ is a topological vector space and $F$ is a linear subspace of $X^*$, then $(X,F)$ is a dual pair if and only if $F$ is weakly$^*$ dense in $X^*$.
Conversely, every dual pair $(X,F)$ can be understood as $(X,X^*)$ by endowing with the weak topology $\sigma(X,F)$ on $X$.
Then, we say $(X,F)$ has the \emph{Krein property} if the closed balanced convex hull of a compact subset of $X$ is compact in the topology $\sigma(X,F)$, and say $(X,F)$ has the \emph{Goldstine property} if $X$ is $\beta(X,F_\beta)$-closed in the strong bidual $(F_\beta)^*_\beta$.
\end{defn}
\begin{rmk*}
Let $X$ a Banach space.
The weak dual pair $(X,X^*)$ satisfies the Krein property by the Krein-\v Smulian theorem, and the Goldstine property by the closedness of $X$ in $X^{**}$.
Suppose there is a predual $X_*$ of $X$, i.e.~a norm closed subspace $X_*$ of $X^*$ such that the restriction of $(X^*)^*\to(X_*)^*$ on $X$ gives rise to a isometric isomorphism.
Then, the weak$^*$ dual pair $(X,X_*)$ satisfies the Krein property by the fact that the closed convex hull of a bounded set is bounded, and the Golstine property because the norm topology and $\beta(X,(X_*)_\beta)$ coincide by the Goldstine theorem.
In particular, a dual pair $(X,F)$ with $F\subset X^*$ has the Goldstine property if and only if the closed unit ball $F_1=F\cap X^*_1$ is weakly$^*$ dense in the closed ball $X^*_1$.
\end{rmk*}

\begin{prop}[Well-definedness of Pettis integral]
Let $x:\Omega\to X$ be a $\sigma(X,F)$-bounded $\sigma(X,F)$-measurable function, where $(\Omega,\mu)$ is a $\sigma$-finite measure space and $(X,F)$ is a dual pair.
Then, it determines a linear operator $F\to L^\infty(\mu)$ by definition.
By the adjoint and restriction, we have a linear operator $\phi_x:L^1(\mu)\to F^\#$, which satisfies
\[\<\phi_x(f),x^*\>:=\int_\Omega f(s)\<x(s),x^*\>\,d\mu(s),\qquad f\in L^1(\mu),\ x^*\in F.\]
We usually write as
\[\phi_x(f)=\int_\Omega f(s)x(s)\,d\mu(s).\]
\begin{parts}
\item $\phi_x(L^1(\mu))\subset(F_\beta)^*$ and $\phi_x$ is always weak-$\sigma((F_\beta)^*,F)$-continuous.
\item Suppose $(X,F)$ has the Krein property.
If $x$ is $\sigma(X,F)$-compactly valued, then $\phi_x(L^1(\mu))\subset X$.
\item Suppose $(X,F)$ has the Krein and Goldstine property.
Suppose $\Omega$ is a locally compact Hausdorff space with a Radon measure $\mu$.
If $x$ is $\sigma(X,F)$-continuous, then $\phi_x(L^1(\mu))\subset X$.
\item Suppose we have $\phi_x(L^1(\mu))\subset X$. Let $Y$ be another topological vector space and $G$ is a weakly$^*$ dense subspace of $Y^*$. If $T:X\to Y$ is a $\sigma(X,F)$-$\sigma(Y,G)$-continuous linear operator, then $T\phi_x=\phi_{T\circ x}$. In other words,
\[T\int_\Omega f(s)x(s)\,d\mu(s)=\int_\Omega f(s)Tx(s)\,d\mu(s),\qquad f\in L^1(\mu).\]
\item Suppose we have $\phi_x(L^1(\mu))\subset X$, $(X,F)$ has the Goldstine property, and $X$ is a Banach space. Then,
\[\|\int f(s)x(s)\,d\mu(s)\|\le\int\|f(s)x(s)\|\,d\mu(s),\qquad f\in L^1(\mu).\]
\end{parts}
\end{prop}
\begin{pf}
(a)
Let $B^*\subset F$ be a $\beta(F,X_\sigma)$-bounded set.
For $x^*\in F$ we have an inequality
\[|\<\phi_x(f),x^*\>|\le\int_\Omega |f(s)\<x(s),x^*\>|\,d\mu(s)\le\|f\|_{L^1}\sup_{y\in x(\Omega)}|\<y,x^*\>|,\]
and a bound
\[\sup_{x_*\in B^*}\sup_{y\in x(\Omega)}|\<y,x^*\>|<\infty\]
due to the $\sigma(X,F)$-boundedness of $x(\Omega)$, so $\phi_x(f)\in(F_\beta)^*$.
If $f_\alpha\in L^1(\mu)$ converges weakly to zero, then
\[\<\phi_x(f_\alpha),x^*\>=\int_\Omega f(s)\<x(s),x^*\>\,d\mu(s)\to0,\qquad x^*\in F\]
because $x$ is $\sigma(X,F)$-integrable so that $(s\mapsto\<x(s),x^*\>)\in L^\infty(\mu)$, so the continuity of $\phi_x$.

(b)
Fix $p\in L^\infty(\mu)$ and let $C$ be the $\sigma(X,F)$-closed balanced convex hull of $x(\Omega)\subset X$.
Then $C$ is $\sigma(X,F)$-compact by the Krein property.
Since for every $x^*\in F$ we have
\[|\<\phi_x(f),x^*\>|\le\int_\Omega|f(s)\<x(s),x^*\>|\,d\mu(s)\le\|f\|_{L^1}\sup_{y\in x(\Omega)}|\<y,x^*\>|\le\|f\|_{L^1}\sup_{y\in C}|\<y,x^*\>|,\]
the linear functional $\phi_x(f)$ on $F$ is continuous with respect to the Mackey topology $\tau(F,X)$, which is a dual topology so that $\phi_x(f)$ can be naturally identified with a vector in $(F_\tau)^*=X$.

(c)
Fix $f\in L^1(\mu)$.
By the tightness of $\mu$, there is a sequence of compact sets $K_n\subset\Omega$ such that $\int_{\Omega\setminus K_n}|f(s)|\,d\mu(s)<n^{-1}$.
Since for each $x^*\in F$ we have
\[|\<\phi_x(f)-\phi_{x|_{K_n}}(f),x^*\>|\le\int_{\Omega\setminus K_n}|f(s)|\,d\mu(s)\cdot\sup_{s\in\Omega}|\<x(s),x^*\>|<n^{-1}\sup_{y\in x(\Omega)}|\<y,x^*\>|\]
so that
\[\sup_{x^*\in B^*}|\<\phi_x(f)-\phi_{x|_{K_n}}(f),x^*\>|\le n^{-1}\sup_{x_*\in B^*}\sup_{y\in x(\Omega)}|\<y,x^*\>|\to0,\qquad n\to\infty,\]
which means that $\phi_{x|_{K_n}}(f)$ converges to $\phi_x(f)$ in $\beta((F_\beta)^*,F_\beta)$.
Since $\phi_{x|_{K_n}}(f)\in X$ by the part (b) and $X$ is closed in $\beta((F_\beta)^*,F_\beta)$ by the Goldstine property, we have $\phi_x(f)\in X$.

(d)
By the continuity of $T$, the adjoint $T^*:G\to F$ is well-defined.
The measurability of $T$ and the existence of the adjoint $T^*$ imply that the composition $T\circ x:\Omega\to Y$ is $\sigma(Y,G)$-bounded and $\sigma(Y,G)$-measurable, so the operator $\phi_{T\circ x}:L^1(\mu)\to G^\#$ is well-defined.
Then,
\begin{align*}
\<T\phi_x(f),y^*\>&=\<\phi_x(f),T^*y^*\>=\int_\Omega f(s)\<x(x),T^*y^*\>\,d\mu(s)\\
&=\int_\Omega f(s)\<Tx(s),y^*\>\,d\mu(s)=\<\phi_{T\circ x}(f),y^*\>,\qquad f\in L^1(\mu),\ y^*\in G.
\end{align*}
In particular, $\phi_{T\circ x}:L^1(\mu)\to Y$.

(e)
By the Goldstine property,
\begin{align*}
\|\int f(s)x(s)\,d\mu(s)\|
&=\sup_{x^*\in F_1}|\int f(s)x(s)\,d\mu(s)|
\le\sup_{x^*\in F_1}\int|f(s)x(s)|\,d\mu(s)\\
&\le\int\sup_{x^*\in F_1}|f(s)x(s)|\,d\mu(s)
\le\int\|f(s)x(s)\|\,d\mu(s).\qedhere\\
\end{align*}
\end{pf}



\begin{prop}
Let $X$ be a Banach space together with a weakly$^*$ dense subspace $F$ of $X^*$ such that $(X,F)$ satisfies the Krein and Goldstine property.
A $\sigma(X,F)$-holomorphic function $x:\Omega\subset\C\to X$ is holomorphic.
\end{prop}
\begin{pf}
It may be false.
\end{pf}


\subsection{Isometric actions}

From now on, we always let $G$ be a locally compact group, and let $X$ be a Banach space together with a weakly$^*$ dense subspace $F$ of $X^*$ such that $(X,F)$ satisfies the Krein and Goldstine property.



\begin{defn}[Isometric group actions]
By an \emph{isometric action} of $G$ on $(X,F)$, we mean a $\sigma(X,F)$-continuous group homomorphism $\alpha:G\to\Isom(X)\subset B(X)$ of $\sigma(X,F)$-continuous linear isometries.
Let $A$ be a C$^*$-algebra.
Then, we always consider an \emph{action} of $G$ on $A$ as an isometric action $\alpha:G\to\Aut(A)$ in the above sense, where $(X,F)=(A,A^*)$.
Let $M$ be a von Neumann algebra.
Then, we always consider an \emph{action} of $G$ on $M$ as an isometric action $\alpha:G\to\Aut(M)$ in the above sense, where $(X,F)=(M,M_*)$.
\end{defn}

\begin{rmk*}
Suppose, for an isometric action $\alpha:G\to\Isom(X)$ on $(X,F)$, we want to justify the following integral:
\[\int_G\alpha_s(x)\,d\mu(s),\qquad x\in X,\ \mu\in M(G).\]
For actions on C$^*$-algebras, the point-weak continuity is in fact equivalent to the point-norm continuity because a weakly continuous semi-group on a Banach space is strongly continuous. (Not that easy.)
It means that the function $G\to X:s\mapsto\alpha_s(a)$ is norm continuous for each $a\in A$ so that it is strongly measurable, which allows to use the Bochner integral to justify the above integral.
However, for von Neumann algebras, the $\sigma$-weak continuity cannot imply the strong measurability in general, so we need to develop the Pettis integral.
\end{rmk*}


\begin{prop}[Representation of groups and measure algebras]
Let $\alpha:G\to\Isom(X)$ be an isometric action of $G$ on $(X,F)$.
There is a (faithful non-degenerate?) homomorphism $\pi_\alpha:M(G)\to B(X)$ defined by
\[\pi_\alpha(\mu)x:=\int_G\alpha_s(x)\,d\mu(s),\]
which is justified by the Pettis integral.
\end{prop}
\begin{pf}
For each $x\in X$, since $G\to X:s\mapsto\alpha_s(x)$ is bounded and continuous with respect to $\sigma(X,F)$, by (c) of the previous proposition, we can define the Pettis integral
\[\pi_\alpha(\mu)x:=\phi_{s\mapsto\alpha_s(x)}(1)=\int_G\alpha_s(x)\,d\mu(s),\qquad x\in X,\ \mu\in M(G).\]
For $\mu,\nu\in M(G)$,
\begin{align*}
\pi_\alpha(\mu*\nu)x
&=\iint\alpha_{st}(x)\,d\mu(s)\,d\nu(t)=\iint\alpha_s(\alpha_t(x))\,d\nu(t)\,d\mu(s)\\
&=\int\alpha_s\Bigl(\int\alpha_t(x)\,d\nu(t)\Bigr)\,d\mu(s)=\pi_\alpha(\mu)\pi_\alpha(\nu)x,\qquad x\in M.\qedhere
\end{align*}
\end{pf}

\begin{prop}[Dual actions]
Let $\alpha:G\to\Isom(X)$ be an isometric action of $G$ on $(X,F)$.
For $\mu\in M(G)$, the linear map
\[X\to X:x\mapsto\int\alpha_s(x)\,d\mu(s)\]
is $\sigma(X,F)$-$\sigma(X,F)$-continuous.
\end{prop}
\begin{pf}
Consider the dual one-parameter group $\alpha^*:G\to\Isom(F)$, which is $\sigma(F,X)$-continuous group of $\sigma(F,X)$-$\sigma(F,X)$-continuous linear isometries.
Since it satisfies the conditions in (c) of the proposition at the first with the dual pair $(F,X)$, the Pettis integral
\[\int\alpha_s^*(x^*)\,d\mu(s)\]
is well-defined in $F$.
Therefore, if a net $x_i$ converges to zero in $\sigma(X,F)$, then for $x^*\in F$
\[\<\int\alpha_s(x_i)\,d\mu(s),x^*\>
=\int\<\alpha_s(x_i),x^*\>\,d\mu(s)
=\int\<x_i,\alpha_s^*(x^*)\>\,d\mu(s)
=\<x_i,\int\alpha_s^*(x^*)\,d\mu(s)\>\to0.\qedhere\]
\end{pf}





\subsection{One-parameter group of isometries}

If $G=\R$, then an isometric action is somtimes called a \emph{flow}.

\begin{prop}[Smoothing operators]
Let $\alpha:\R\to\Isom(X)$ be a flow on $(X,F)$.
For each $n>0$, define a linear operator $R_n:X\to X$ such that
\[R_n(x):=\sqrt{\frac n\pi}\int e^{-ns^2}\alpha_s(x)\,ds,\qquad x\in X.\]
\begin{parts}
\item $R_n$ is contractive.
\item $R_n(x)\to x$ in $\sigma(X,F)$.
\item $R_n(x)\to x$ in norm if $F=X^*$.
\item $R_n(x)\to x$ $\sigma$-strongly$^*$ if $(X,F)=(M,M_*)$ for a von Neumann algebra $M$.
\end{parts}
\end{prop}
\begin{pf}
Relatively obvious.
\end{pf}


\begin{thm}[Analytic continuations]
Let $\alpha:\R\to\Isom(X)$ be a flow on $(X,F)$.
We have a family of densely defined closed operators $\{\alpha_z:z\in\C\}$ on $X$ which extends the original $\alpha$, such that
\begin{enumerate}[(i)]
\item $\alpha_z\alpha_t=\alpha_{z+s}=\alpha_s\alpha_z$ and $\alpha_z\alpha_w\subset\alpha_{z+w}$ for $s\in\R$ and $z,w\in\C$,
\item $\alpha_z^{-1}=\alpha_{-z}$,
\item $\dom\alpha_z\subset\dom\alpha_w$ if $\Im z\ge\Im w\ge0$,
\item $\bigcap_{z\in\C}\dom\alpha_z$ is dense in $X$.
\end{enumerate}
\end{thm}
\begin{pf}
Consider the set of regularized vectors
\[\{R_n(x):n\in\N,\ x\in X\}.\]
Now we define $\alpha_z:X_0\to X$ for $z\in\C$ such that
\[\alpha_z\Bigl(\int_\R f(s)\alpha_s(x)\,ds\Bigr):=\int_\R f(s-z)\alpha_s(x)\,ds.\]
It satisfies some properties:
\begin{parts}
\item It extends the original $\{\alpha_s:s\in\R\}$.
\item For fixed $x\in X_0$, $z\mapsto\alpha_z(x)$ is $\sigma(X,F)$-entire.
\item $X_0$ is $\sigma(X,F)$-dense in $E$, so $\alpha_z$ is densely defined for each $z\in\C$.
\item $\alpha_z$ is closable for each $z\in\C$.
\end{parts}
(a) is clear by coordinate change, and (b) follows from the Fubini and the Morera after taking arbitrary elements of $E^*$.
(c) is by an approximate identity $e_n$ of $L^1(\R)$ has $x=\lim_{n\to\infty}\int_\R e_n(s)\alpha_s(x)\,ds$.
For (d), we have the adjoint $(\alpha_z)_0^*\supset(\alpha_{-\bar z})_0$, which is densely defined.
Now we have a family of closed densely defined operators $\{\alpha_z:z\in\C\}$ on $E$ such that $\alpha_z\alpha_w\subset\alpha_{z+w}$ for all $z,w\in\C$.
\end{pf}

\begin{prop}
\begin{parts}
\item $R_n(x)\to x$
\end{parts}
\end{prop}

\begin{defn}[Entire elements]
The set of entire elements is $\bigcup_{z\in\C}\dom\alpha_z=\bigcup_{n\in\Z}\dom\alpha_{ni}$, which is dense.
If $X$ is a von Neumann algebra, then it is a $*$-subalgebra of $M$.

\end{defn}





\subsection{Tomita-Takesaki commutation theorem}

In this section, we let $A$ be a left Hilbert algebra.
We will use the following notations freely:
\[H,M,S,\lambda,F,\rho,B,D,A',B',D',\Delta,J.\]
Also note that
\[\begin{tikzcd}
\fm:=\fn^*\fn \rar[phantom,"\subset"] & \fa:=\fn^*\cap\fn \rar[phantom,"\subset"]\dar[shift left]{\Lambda} & \fn \rar[phantom,"\subset"]\dar[shift left]{\Lambda} & M\\
& A \rar[phantom,"\subset"]\uar[shift left]{\lambda} & B \rar[phantom,"\subset"]\uar[shift left]{\lambda} & H.
\end{tikzcd}\]

The goal of this section is to prove that there exists the following commutative ``cube'' diagram:
\[\begin{tikzcd}[column sep={3.5em,between origins},row sep={2.5em,between origins}]
&A\ar{rr}{\Delta^{it}}&&A\ar{dd}{\lambda}\\
A'\ar[<->]{ur}{J}\ar[swap]{rr}{\Delta^{it}}\ar[swap]{dd}{\rho}&&A'\ar[<->,swap]{ur}{J}\ar{dd}{\rho}&\\
&&&\lambda(A)\\
\rho(A')\ar[swap]{rr}{\Ad\Delta^{it}}&&\rho(A')\ar[<->,swap]{ur}{\Ad J}&.
\end{tikzcd}\]


\begin{lem*}
For every $t\in\R$, the unitary operator $\Delta^{it}$ commutes with $J$, $S$, and $F$.
\end{lem*}
\begin{pf}
It is enough to show $\Delta^{it}J=J\Delta^{it}$.
By the relation $J\Delta J=\Delta^{-1}$, the anti-linearity of $J$, and the uniqueness of the bounded Borel functional calculus, we have the commutation.
More precisely, if we let $f(s):=e^{it\log s}$ on $(0,\infty)$, then
\[\Delta^{-it}=f(\Delta^{-1})=f(J\Delta J)=J\bar{f(\Delta)}J=J(\Delta^{it})^*J=J\Delta^{-it}J.\]
(Here we omit the detailed proof of $f(J\Delta J)=J\bar{f(\Delta^{-1})}J$.)
\end{pf}


\begin{lem*}
$J:D'\to D$ and $\Delta^{it}:D\to D$.
\end{lem*}
\begin{pf}
We have $J:D'\to D$ since $\eta\in D'$ implies that $SJ\eta=JF\eta$ is well-defined in $H$.
We have $\Delta^{it}:D\to D$ for real $t$ since $\xi\in D$ implies that $S\Delta^{it}\xi=\Delta^{it}S\xi$ is well-defined in $H$ because $S\xi\in D$.
\end{pf}



We need two critical lemmas.

\begin{lem}[Fourier inversion of sech]
Let $\alpha$ be a flow.
Let $H$ be a Hilbert space.
\begin{parts}
\item We have a Pettis integral
\[\int_\R(e^{-\frac s2}\alpha_{-\frac i2}+e^{\frac s2}\alpha_{\frac i2})\frac{e^{-ist}}{e^{\pi t}+e^{-\pi t}}\alpha_t(x)\,dt
=x,\qquad x\in\dom\alpha_{-\frac i2}\cap\dom\alpha_{\frac i2}.\]
\item If $\alpha=\sigma:\R\to\Aut(B(H))$ such that $\sigma_t=\Ad_{\Delta^{it}}$ for a injective positive self-adjoint operator $\Delta$ on $H$, then we have a $\sigma$-weak Pettis integral
\[\int_\R\frac{e^{-ist}}{e^{\pi t}+e^{-\pi t}}\sigma_t(x)\,dt
=(e^{-\frac s2}\sigma_{-\frac i2}+e^{\frac s2}\sigma_{\frac i2})^{-1}x,\qquad x\in B(H).\]
\item If $\alpha=u^*:\R\to U(H)$ such that $u_t=\Delta^{it}$ for a injective positive self-adjoint operator $\Delta$ on $H$, then we have a Pettis integral
\[\int_\R\frac{e^{-ist}}{e^{\pi t}+e^{-\pi t}}u_t^*(\xi)\,dt
=(e^{-\frac s2}u_{\frac i2}+e^{\frac s2}u_{-\frac i2})^{-1}\xi,\qquad \xi\in H.\]
The adjoint $u_t^*$ is called the propagator.
\end{parts}
\end{lem}
\begin{rmk*}
If we let $f(t):=(e^{\frac t2}+e^{-\frac t2})^{-1}$ and write $\alpha_t=e^{t\delta}$, then the equation in the lemma can be rewritten formally as the Fourier inversion
\[\frac1{\sqrt{2\pi}}\int_\R e^{it(-i\delta-s)}\hat f(t)\,dt=f(-i\delta-s),\qquad s\in\R.\]
However, this Fourier calculus in general setting using an unbounded holomorphic functional calculus for unbounded operators acting on Banach spaces is impossible, because even for a fairly normal example (e.g.~$\sigma_t=\Ad u_t$, $u_t$ is given by the translation on $L^2(\R)$) we have a counterexample having the entire spectrum of the analytic generator $\sigma(\sigma_{-i})=\C$.
\end{rmk*}
\begin{pf}
(a)
We use the special fact that the function $\hat f(t):=\sqrt{2\pi}(e^{\pi t}+e^{-\pi t})^{-1}$ has imaginary period $i$.
Fix $s\in\R$ and $x\in\dom\alpha_{-\frac i2}\cap\dom\alpha_{\frac i2}$.
Define a weakly$^*$ meromorphic vector function $g:\C\setminus i\Z\to X$ such that
\[g(z):=-i\sqrt{2\pi}\frac{e^{-isz}}{e^{\pi z}-e^{-\pi z}}\alpha_z(x).\]
It satisfies relations
\[g(t-\frac i2)=e^{-\frac s2}\alpha_{-\frac i2}(e^{-ist}\hat f(t)\alpha_t(x)),\qquad
g(t+\frac i2)=-e^{\frac s2}\alpha_{\frac i2}(e^{-ist}\hat f(t)\alpha_t(x))\]
and enjoys an estimate
\[\sup_{|r|\le\frac12}\|g(t+ir)\|\le\sup_{|r|\le\frac12}\sqrt{2\pi}\frac{e^{sr}}{|e^{\pi(t+ir)}-e^{-\pi(t+ir)}|}\|x\|=O(e^{-\pi|t|}),\qquad|t|\to\infty.\]
Then, by the residue theorem
\begin{align*}
\sqrt{2\pi}x=2\pi\lim_{z\to0}zg(z)
&=\int_{-\infty}^\infty g(t-\frac i2)\,dt-\int_{-\infty}^\infty g(t+\frac i2)\,dt\\
&=\int_{-\infty}^\infty(e^{-\frac s2}\alpha_{-\frac i2}+e^{\frac s2}\alpha_{\frac i2})e^{-ist}\hat f(t)\alpha_t(x)\,dt.
\end{align*}
Extend for $x\in X$ using the boundedness.

(b)
Let $A=(e^{-\frac s2}\sigma_{-\frac i2}+e^{\frac s2}\sigma_{\frac i2})$ be a densely defined operator on $B(H)$, and let $R$ be a bounded linear operator on $B(H)$ such that
\[R(x):=\int\frac{e^{-ist}}{e^{\pi t}+e^{-\pi t}}\sigma_t(x)\,dt,\qquad x\in B(H).\]
Fix $x\in B(H)$.
If we let $e_n:=1_{[n^{-1},n]}(\Delta)$ for some $n>1$, then $\sigma_{\pm\frac i2}$ acts on the compression $e_nB(H)e_n$ as bounded invertible operators $e_nB(H)e_n\to e_nB(H)e_n$, which is continuous between $\sigma$-weak topologies.
Thus, the part (a) and the commutation with integral imply
\begin{align*}
e_nxe_n=RA(e_nxe_n)=AR(e_nxe_n)=e^{-\frac s2}\Delta^{\frac12}R(e_nxe_n)\Delta^{-\frac12}+e^{\frac s2}\Delta^{-\frac12}R(e_nxe_n)\Delta^{\frac12}.
\end{align*}
Since $R$ is continuous in $\sigma$-weak topologies, we obtain by letting $n\to\infty$ an equation $x=AR(x)$ as sesquilinear forms on a dense subspace $\dom\Delta^{\frac12}\cap\dom\Delta^{-\frac12}$ of $H$, and hence as bounded operators because linear functionals given by vectors in a dense subspace of $H$ separate points of $B(H)$.
In particular, $A$ is surjective.
Since the injectivity of $A$ follows from the part (a), we have $A^{-1}=R$.

(c)
Similar to (b), but cut $\xi$ off into $e_n\xi$.
\end{pf}





\begin{lem}
Let $A$ be a left Hilbert algebra.
For $s\in\R$, we have $(e^{-s}+\Delta)^{-1}:A'\to A\cap D'$.
In particular, $A\cap D'$ is dense in $H$.
\end{lem}
\begin{pf}
Let $\eta\in A'$ and $\xi:=(e^{-s}+\Delta)^{-1}\eta$.
Then, $\Delta\xi=\eta-e^{-s}\xi\in H$ implies $\xi\in\dom\Delta\subset\dom\Delta^{\frac12}=D$, and $F\xi=e^s(F\eta-S\xi)\in H$ implies $\xi\in D'$.
The only non-trivial fact is $\xi\in B$.
Since $\xi\in D$, by the polar decomposition, we have
\[\lambda(\xi)=vh=kv,\qquad h:=|\lambda(\xi)|,\quad k:=|\lambda(\xi)^*|.\]
Let $f\in C_c((0,\infty))^+$.
Since
\begin{align*}
\<f(h)S\xi,\zeta\>
&=\<S\xi,f(h)\zeta\>
=\<Ff(h)\zeta,\xi\>
=\<Fv^*\grave f(k)\lambda(\xi)\zeta,\xi\>
=\<F\lambda(v^*\grave f(k)\xi)\zeta,\xi\>\\
&=\<F\rho(\zeta)v^*\grave f(k)\xi,\xi\>
=\<\rho(v^*\grave f(k)\xi)^*F\zeta,\xi\>
=\<F\zeta,\rho(v^*\grave f(k)\xi)\xi\>\\
&=\<F\zeta,\lambda(\xi)v^*\grave f(k)\xi\>
=\<F\zeta,f(k)\xi\>
=\<Sf(k)\xi,\zeta\>,\qquad\xi\in D,\ \zeta\in D',
\end{align*}
we have
\begin{align*}
\|f(k)\eta\|^2
&=\|f(k)(e^{-s}+\Delta)\xi\|^2\\
&=e^{-2s}\|f(k)\xi\|^2+\|f(k)\Delta\xi\|^2+2e^{-s}\Re\<f(k)\xi,f(k)\Delta\xi\>\\
&\ge2e^{-s}\|f(k)\xi\|\|f(k)\Delta\xi\|+2e^{-s}\Re\<f(k)\xi,f(k)\Delta\xi\>\\
&\ge4e^{-s}\Re\<f(k)\xi,f(k)\Delta\xi\>\\
&=4e^{-s}\Re\<f(k)^2\xi,FS\xi\>\\
&=4e^{-s}\Re\<Sf(k)^2\xi,S\xi\>\\
&=4e^{-s}\Re\<f(h)^2S\xi,S\xi\>\\
&=4e^{-s}\|f(h)S\xi\|^2,
\end{align*}
and
\begin{align*}
\|f(k)\eta\|^2
&=\|\grave f(k)k\eta\|^2
=\|\grave f(k)v\lambda(\xi)^*\eta\|^2
=\|v\grave f(h)\rho(\eta)S\xi\|^2\\
&=\|\rho(\eta)v\grave f(h)S\xi\|^2
\le\|\rho(\eta)\|^2\|\grave f(h)S\xi\|^2,\qquad\eta\in A',\ f\in C_c((0,\infty))^+,
\end{align*}
which imply that $c:=\frac12e^{\frac s2}\|\rho(\eta)\|$ satisfies
\[\|f(h)S\xi\|\le c\|\grave f(h)S\xi\|.\]

For arbitrary $\e>0$, by considering a net $f_\alpha\uparrow1_{(c+\e,\infty)}$ and defining $p_\e:=1_{[0,c+\e]}(h)$, we have $\grave f\le(c+\e)^{-1}f$ and that
\[\|(1-p_\e)S\xi\|\le\frac c{c+\e}\|(1-p_\e)S\xi\|,\]
which implies $p_\e S\xi=S\xi$ for all $\e>0$, so $p_0S\xi=S\xi$.
Then,
\[\|\lambda(\xi)^*\zeta\|=\|p_0\lambda(\xi)^*\zeta\|=\|1_{[0,c]}(h)hv^*\zeta\|\le c\|v^*\zeta\|\le c\|\zeta\|,\qquad\zeta\in A'.\]
Therefore, $S\xi\in B$, which implies $S\xi\in A$ and $\xi\in A$.

For the density of $A\cap D'$, we approximate $\zeta\in\dom\Delta$.
Define a sequence $\eta_n\in A'$ such that $\eta_n\to(1+\Delta)\zeta$.
Then, since $(1+\Delta)^{-1}$ is bounded, we have $(1+\Delta)^{-1}\eta_n\to\zeta\in\bar{A\cap D'}$.
Since $\dom\Delta$ is dense in $H$, we are done.
\end{pf}


\begin{thm}[Tomita-Takesaki commutation theorem]
Let $A$ be a left Hilbert algebra.
Then, for every $t\in\R$, the following diagram commutes:
\[\begin{tikzcd}[column sep={3.5em,between origins},row sep={2.5em,between origins}]
&D\ar{rr}{u_t=\Delta^{it}}&&D\ar{dd}{\lambda}\\
A'\ar{ur}{J}\ar[swap]{dd}{\rho}&&&\\
&&&C(H).\\
\rho(A')\ar[swap]{rr}{\sigma_t=\Ad\Delta^{it}}&&B(H)\ar[swap]{ur}{\Ad J}&
\end{tikzcd}\]
\end{thm}
\begin{pf}
Fix $\eta\in A'$ and define
\begin{align*}
\xi:&=(e^{-\frac s2}u_{\frac i2}+e^{\frac s2}u_{-\frac i2})^{-1}J\eta
=(e^{-\frac s2}\Delta^{-\frac12}+e^{\frac s2}\Delta^{\frac12})^{-1}J\eta\\
&=(e^{-\frac s2}\Delta^{-\frac12}+e^{\frac s2}\Delta^{\frac12})^{-1}\Delta^{-\frac12}F\eta
=e^{-\frac s2}(e^{-s}+\Delta)^{-1}F\eta
\in A\cap D'.
\end{align*}
By the computations
\begin{align*}
\<\rho(F\xi)\zeta_1,\zeta_2\>
&=\<\lambda(\zeta_1)F\xi,\zeta_2\>
=\<F\xi,\lambda(\zeta_1)^*\zeta_2\>
=\<S\lambda(\zeta_1)^*\zeta_2,\xi\>\\
&=\<\lambda(\zeta_2)^*\zeta_1,\xi\>
=\<\rho(\zeta_1)S\zeta_2,\xi\>
=\<S\zeta_2,\rho(\zeta_1)^*\xi\>\\
&=\<S\zeta_2,\lambda(\xi)F\zeta_1\>
=\<F\lambda(\xi)F\zeta_1,\zeta_2\>,\qquad\qquad\zeta_1\in A\cap D',\ \zeta_2\in A,\\
\<\rho(S\xi)\zeta_1,\zeta_2\>
&=\<\lambda(\zeta_1)S\xi,\zeta_2\>
=\<S\xi,\lambda(\zeta_1)^*\zeta_2\>
=\<S\xi,\rho(\zeta_2)S\zeta_1\>\\
&=\<\rho(\zeta_2)^*S\xi,S\zeta_1\>
=\<\lambda(\xi)^*F\zeta_2,S\zeta_1\>
=\<F\zeta_2,\lambda(\xi)S\zeta_1\>\\
&=\<S\lambda(\xi)S\zeta_1,\zeta_2\>,\qquad\qquad\qquad\qquad\qquad\qquad\zeta_1\in A\cap D',\ \zeta_2\in D',
\end{align*}
the domains of $\rho(F\xi)$ and $\rho(S\xi)$ contain $A\cap D'$ and we have
\begin{align*}
\rho(\eta)
&=\rho(J(e^{-\frac s2}\Delta^{-\frac12}+e^{\frac s2}\Delta^{\frac12})\xi)\\
&=e^{-\frac s2}\rho(F\xi)+e^{\frac s2}\rho(S\xi)\\
&=e^{-\frac s2}F\lambda(\xi)F+e^{\frac s2}S\lambda(\xi)S\\
&=e^{-\frac s2}\Delta^{\frac12}J\lambda(\xi)J\Delta^{-\frac12}+e^{\frac s2}\Delta^{-\frac12}J\lambda(\xi)J\Delta^{\frac12}\\
&=(e^{-\frac s2}\sigma_{-\frac i2}+e^{\frac s2}\sigma_{\frac i2})(\Ad J)\lambda(\xi)
\end{align*}
as sesquilinear forms on $A\cap D'$.
The conditions for $\xi$ and $\zeta_1$ to belong to $A\cap D'$ are necessary in the above computation.
By the density of $A\cap D'$ in $H$, we have the bounded operators
\[(\Ad J)(e^{-\frac s2}\sigma_{-\frac i2}+e^{\frac s2}\sigma_{\frac i2})^{-1}\rho(\eta)=\lambda((e^{-\frac s2}u_{\frac i2}+e^{\frac s2}u_{-\frac i2})^{-1}J\eta).\]


Then, we get the equation of bounded linear operators
\[(\Ad J)\Bigl(\int\frac{e^{-ist}}{e^{\pi t}+e^{-\pi t}}\sigma_t(\rho(\eta))\,dt\Bigr)
=\lambda\Bigl(\int\frac{e^{ist}}{e^{\pi t}+e^{-\pi t}}u_t(J\eta)\,dt\Bigr),\qquad s\in\R,\ \eta\in A',\]
changing the variable using that the hyperbolic secant functions is even.
For every $\zeta\in B'$, since $\Ad J:B(H)\to B(H)$, $\cdot\zeta:B(H)\to H$, and $\rho(\zeta):H\to H$ are all continuous between weak$^*$ topologies, we have
\begin{align*}
\int\frac{e^{ist}}{e^{\pi t}+e^{-\pi t}}(\Ad J)\sigma_t(\rho(\eta))\zeta\,dt
&=(\Ad J)\Bigl(\int\frac{e^{-ist}}{e^{\pi t}+e^{-\pi t}}\sigma_t(\rho(\eta))\,dt\Bigr)\zeta,
\end{align*}
which is equal to
\begin{align*}
\lambda\Bigl(\int\frac{e^{ist}}{e^{\pi t}+e^{-\pi t}}u_t(J\eta)\,dt\Bigr)\zeta
&=\rho(\zeta)\int\frac{e^{ist}}{e^{\pi t}+e^{-\pi t}}u_t(J\eta)\,dt\\
&=\int\frac{e^{ist}}{e^{\pi t}+e^{-\pi t}}\rho(\zeta)u_t(J\eta)\,dt\\
&=\int\frac{e^{ist}}{e^{\pi t}+e^{-\pi t}}\lambda(u_t(J\eta))\zeta\,dt.
\end{align*}
Then, by taking arbitrary bounded linear functionals of $H$ on the above integral, and by the injectivity of the Fourier transform, we finally obtain $\Ad_J\circ\,\sigma_t\circ\rho=\lambda\circ u_t\circ J$ on $A'$.
\end{pf}

\begin{cor}
Let $A$ be a full left Hilbert algebra.
Then, for $t\in\R$, the following diagram is well-defined and commutes:
\[\begin{tikzcd}[column sep={3.5em,between origins},row sep={2.5em,between origins}]
&A\ar{rr}{\Delta^{it}}&&A\ar{dd}{\lambda}\\
A'\ar[<->]{ur}{J}\ar[swap]{rr}{\Delta^{it}}\ar[swap]{dd}{\rho}&&A'\ar[<->,swap]{ur}{J}\ar{dd}{\rho}&\\
&&&\lambda(A)\\
\rho(A')\ar[swap]{rr}{\Ad_{\Delta^{it}}}&&\rho(A')\ar[<->,swap]{ur}{\Ad_J}&.
\end{tikzcd}\]
In particular, we have
\[JA=A',\qquad\Delta^{it}A=A,\qquad JMJ=M',\qquad\Delta^{it}M\Delta^{-it}=M,\]
and $J$ is an anti-homomorphism, $\Delta^{it}$ is a $*$-homomorphism
\end{cor}
\begin{pf}

\end{pf}



\begin{cor}[Flow on a Hilbert space]

\[R_n(\xi):=\sqrt{\frac n\pi}\int e^{-ns^2}\Delta^{is}\xi\,ds.\]
$R_n(\xi)-\xi\to0$ in norm, $\Delta^{\frac12}(R_n(\xi)-\xi)\to0$ in norm if $\xi\in D$, $\|\lambda(R_n(\xi))\|\le\|\lambda(\xi)\|$ if $\xi\in B$, $\lambda(R_n(\xi))\to\lambda(\xi)$ $\sigma$-strongly$^*$.
Stone's theorem,
Spectral truncation technique
\end{cor}


\begin{ex}[Flow on a von Neumann algebra]

\[R_n(x):=\sqrt{\frac n\pi}\int e^{-ns^2}\sigma_s(x)\,ds.\]

A \emph{Tomita algebra} is a left Hilbert algebra $A_0$ such that every element of $A_0$ is entire with respect to the associated modular automorphism group.

Spectral truncation technique
\end{ex}








\newpage
\section{January 17}



\subsection{Cocycle conjugacy}

\begin{defn*}[Actions and flows]
Let $M$ be a von Neumann algebra and $G$ be a locally compact group.
An \emph{action} of $G$ on $M$ is a $\sigma$-weakly continuous group homomorphism $\alpha:G\to\Aut(M)$.
The triple $(M,G,\alpha)$ is called a \emph{W$^*$-dynamical system}.
If $G=\R$, then an action is also called a \emph{flow}.
A \emph{covariant representation} of a W$^*$-dynamical system $(M,G,\alpha)$ is a pair $(\pi,u,H)$ of a normal representation $\pi:M\to B(H)$ and a strongly continuous unitary representation $u:G\to U(H)$ such that $\alpha_s(x)=u_sxu_s^*$.
\end{defn*}



\begin{defn}[Cocycle conjugacy]
Let $(M,G,\alpha)$ be a W$^*$-dynamical system.
A \emph{$\alpha$-(one)-cocycle} of a strongly continuous map $u:G\to U(M)$ such that $u_{st}=u_s\alpha_s(u_t)$, and we denote by $Z_\alpha^1(G,U(M))$ the set of all $\alpha$-cocycles.
\end{defn}


\begin{thm}[Connes cocycle derivative]
Let $\f$ and $\psi$ be faithful semi-finite normal weights on a von Neumann algebra $M$.
\begin{parts}
\item The representations $\pi_\f$ and $\psi_\psi$ are unitarily equivalent.
In particular, every normal state is a vector state in a semi-cyclic reprsentation of a faithful semi-finite normal weight.
\item The modular automorphism groups $\sigma_t^\f$ and $\sigma_t^\psi$ are conjugate up to cocycles.
In other words, there is a canonical continuous group homomorphism $\R\to\operatorname{Out}(M)$ for $M$.
\item 
\end{parts}
\end{thm}
\begin{pf}
\AtBeginEnvironment{bmatrix}{\setlength{\arraycolsep}{2pt}}
Consider the \emph{balanced weight} $\f\oplus\psi$ on $M\otimes M_2(\C)=M_2(M)$.
Then, it is also faithful, semi-finite, and normal.***

We investigate the semi-cyclic representation and the left Hilbert algebra structure corresponding to $\f\oplus\psi$.
First, we have
\[\fn_{\f\oplus\psi}=\mat{\fn_\f&\fn_\psi\\\fn_\f&\fn_\psi},\qquad
\fa_{\f\oplus\psi}=\mat{\fa_\f&\fn_\f^*\cap\fn_\psi\\\fn_\psi^*\cap\fn_\f&\fa_\psi},\qquad
\fm_{\f\oplus\psi}=\mat{\fm_\f&\fn_\f^*\fn_\psi\\\fn_\psi^*\fn_\f&\fm_\psi}.
\]
The semi-cyclic representation of $\f\oplus\psi$ can be realized on the identification with the direct sum
\[H_{\f\oplus\psi}=H_\f\oplus H_\f\oplus H_\psi\oplus H_\psi\]
such that $\Lambda_{\f\oplus\psi}:\fn_{\f\oplus\psi}\to H_{\f\oplus\psi}$ and $\pi_{\f\oplus\psi}:M_2(M)\to B(H_{\f\oplus\psi})$ given by
\[\Lambda_{\f\oplus\psi}\mat{x_{11}&x_{12}\\x_{21}&x_{22}}=\mat[b]{\Lambda_\f(x_{11})\\\Lambda_\f(x_{21})\\\Lambda_\psi(x_{12})\\\Lambda_\psi(x_{22})},\quad
\pi_{\f\oplus\psi}\mat{x_{11}&x_{12}\\x_{21}&x_{22}}=\mat[b]{
\pi_\f(x_{11})&\pi_\f(x_{12})&0&0\\
\pi_\f(x_{21})&\pi_\f(x_{22})&0&0\\
0&0&\pi_\psi(x_{11})&\pi_\psi(x_{12})\\
0&0&\pi_\psi(x_{21})&\pi_\psi(x_{22})}.\]
The Hilbert algebra structure $S_{\f\oplus\psi},\ \Delta_{\f\oplus\psi},\ J_{\f\oplus\psi}:A_{\f\oplus\psi}\to H_{\f\oplus\psi}$ on $A_{\f\oplus\psi}=\Lambda_{\f\oplus\psi}(\fa_{\f\oplus\psi})$ are computed as
\[S_{\f\oplus\psi}=\mat[b]{
S_\f&0&0&0\\
0&0&S_{\f,\psi}&0\\
0&S_{\psi,\f}&0&0\\
0&0&0&S_\psi},\quad
J_{\f\oplus\psi}=\mat[b]{
J_\f&0&0&0\\
0&0&J_{\f,\psi}&0\\
0&J_{\psi,\f}&0&0\\
0&0&0&J_\psi},\quad
\Delta_{\f\oplus\psi}=\mat[b]{
\Delta_\f&0&0&0\\
0&\Delta_{\f,\f}&0&0\\
0&0&\Delta_{\psi,\psi}&0\\
0&0&0&\Delta_\psi}.\]




(a)
Since
\[\pi_{\f\oplus\psi}\mat{x&0\\0&x}=\mat[b]{
\pi_\f(x)&0&0&0\\
0&\pi_\f(x)&0&0\\
0&0&\pi_\psi(x)&0\\
0&0&0&\pi_\psi(x)},\quad
J\pi_{\f\oplus\psi}\mat{0&0\\1&0}J=\mat[b]{
0&0&\ \ 0\ \ &\ \ 0\ \ \\
0&0&0&0\\
J_{\psi,\f}J_\f&0&0&0\\
0&J_\psi J_{\psi,\f}&0&0}\]
are commuting by the Tomita-Takesaki commutation theorem, we obtain
\[\mat[b]{\pi_\psi(x)J_{\psi,\f}J_\f&0\\0&\pi_\psi(x)J_\psi J_{\psi,\f}}=\mat[b]{J_{\psi,\f}J_\f\pi_\f(x)&0\\0&J_\psi J_{\psi,\f}\pi_\f(x)},\]
so if we define $u_{\psi,\f}:=J_{\psi,\f}J_\f=J_\psi J_{\psi,\f}:H_\f\to H_\psi$, then it is unitary such that $\pi_\psi(x)=u_{\psi,\f}\pi_\f(x)u_{\psi,\f}^*$ for all $x\in M$.
Be cautious that $\Lambda_\psi(x)\ne u\Lambda_\f(x)$ unless $\f=\psi$ in general, so the two semi-cyclic representations are not unitarily equivalent in the full sense.

(b)
Define $\sigma_t^{\f,\psi}$ and $\sigma_t^{\psi,\f}$ such that
\[\sigma_t^{\f\oplus\psi}\mat{x_{11}&x_{12}\\x_{21}&x_{22}}=:\mat{\sigma_t^\f(x_{11})&\sigma_t^{\f,\psi}(x_{12})\\\sigma_t^{\psi,\f}(x_{21})&\sigma_t^\psi(x_{22})}.\]

\end{pf}



\subsection{Commuting weights}


\begin{defn}[Kubo-Martin-Schwinger weights]
Let $M$ be a von Neumann algebra.
Let $\alpha$ be a flow on $M$, and $\f$ be a faithful semi-finite normal weight on $M$.
For $x,y\in M$, their \emph{two-point function} at inverse temperature $\beta\in\R$ is a bounded continuous function $f:\Im^{-1}([\beta,0]\cup[0,\beta])\to\C$ which is holomorphic on its interior such that
\[f(t)=\f(y\sigma_t(x)),\qquad f(t+i\beta)=\f(\sigma_t(x)y),\qquad t\in\R.\]
If $\f$ is invariant under $\sigma$ and every pair $x,y\in\fa$ admits a two-point function at $\beta$, then we say $\f$ is a \emph{Kubo-Martin-Schwinger weight} or \emph{KMS weight} for $\alpha$ at $\beta$.
From now on, we always assume $\beta=-1$.
\end{defn}

\begin{rmk*}
If $\f$ is a state, then for $\f$ to be a KMS state the invariance condition is superfluous: since $\fm=\fa=M$, we can put $y=1$ to show the invariance using the Liouville theorem and the Schwarz reflection principle.
\end{rmk*}


\begin{lem}[Action of entire elements]
Let $\f$ be a faithful semi-finite normal weight on a von Neumann algebra $M$.
If $x$ is entire with respect to $\sigma$, then $x\fm\cup\fm x\subset\fm$.
\end{lem}
\begin{pf}
We first show $x\fa\cup\fa x\subset\fa$.
Let $y\in\fa$.
By symmetry, it suffices to show $xy\in\fa$.
Since $\fn$ is a left ideal of $M$, $xy\in\fn$, which implies $\Lambda(xy)\in B$.
Consider
\[\xi(t):=\Delta^{it}\Lambda(xy)=\Delta^{it}x\Lambda(y)=\sigma_t(x)\Delta^{it}\Lambda(y).\]
Since $\Lambda(y)\in D=\dom\Delta^{\frac12}$, the function $f$ is holomorphically extended to the strip $\Im^{-1}([-\frac12,0])$.
It means that $\xi(0)=\Lambda(xy)\in\dom\Delta^{\frac12}$, so $\Lambda(xy)\in D$.
Thus we have $\Lambda(xy)\in A$ and $xy\in\fa$.

For the original claim, if $y\in\fm^+$, since $y^{\frac12}\in\fa$ and $xy^{\frac12}\in\fa$ as above, we have $xy=(xy^{\frac12})y^{\frac12}\in\fa^2=\fm$.
The linear span and symmetry show $x\fm\cup\fm x\subset\fm$.
\end{pf}


\begin{lem}[Existence of two-point functions]
Let $M$ be a von Neumann algebra.
For $\sigma$ the associated modular automorphism group for a faithful semi-finite normal weight $\f$ on $M$, the followings hold.
\begin{parts}
\item If $x,y\in\fa$, then they admit a two-point function.
\item If $x\in M$ is entire for $\sigma$ and $y\in\fm$, then they admit an entire two-point function.
\item If $x\in M$ satisfies $x\fm\cup\fm x\subset\fm$ and $y\in\fa_0^*\fa_0$, then they admit an entire two-point function.
\end{parts}
\end{lem}
\begin{pf}
We may assume $x,y\ge0$.
In this case, $\Delta^{\frac12}\Lambda(y)=JS\Lambda(y)=J\Lambda(y)$ for $y\in\fn^+$.

(a)
Define
\[f(z):=\<\Delta^{i\frac z2}\Lambda(x),\Delta^{-i\frac{\bar z}2}\Lambda(y)\>.\]
Since $\Lambda(x),\Lambda(y)\in A\subset\dom\Delta^{\frac12}$, the function $f$ is bounded and continuous on $\Im^{-1}([-1,0])$, and holomorphic on its interior.
Also, for $t\in\R$
\begin{align*}
\f(y\sigma_t(x))
&=\<\Delta^{it}\Lambda(x),\Lambda(y)\>
=\<\Delta^{i\frac t2}\Lambda(x),\Delta^{-i\frac t2}\Lambda(y)\>
=f(t),\\
\f(\sigma_t(x)y)
&=\<\Lambda(y),\Delta^{it}\Lambda(x)\>
=\<\Lambda(y),J\Delta^{it}J\Lambda(x)\>
=\<\Delta^{it}J\Lambda(x),J\Lambda(y)\>\\
&=\<\Delta^{it}\Delta^{\frac12}\Lambda(x),\Delta^{\frac12}\Lambda(y)\>
=\<\Delta^{i\frac{t-i}2}\Lambda(x),\Delta^{-i\frac{t+i}2}\Lambda(y)\>
=f(t-i).
\end{align*}

(b)
Since $\sigma_t$ sends entire elements to entire elements, we have $y\sigma_t(x),\sigma_t(x)y\in\fm$ by the previous lemma.
Define
\[f(z):=\<\sigma_{z+\frac i2}(x)\Delta^{\frac12}\Lambda(y^{\frac12}),\Delta^{\frac12}\Lambda(y^{\frac12})\>.\]
Since $x$ is entire, the function $f$ is entire and bounded on the strip $\Im^{-1}([-1,0])$.
Then, for $t\in\R$,
\begin{align*}
\f(y\sigma_t(x))
&=\<\Delta^{\frac12}\Lambda(y^{\frac12}),\Delta^{\frac12}\sigma_t(x)\Lambda(y^\frac12)\>
=\<\Delta^{\frac12}\Lambda(y^{\frac12}),\sigma_{t-\frac i2}(x)\Delta^{\frac12}\Lambda(y^\frac12)\>\\
&=\<\sigma_{t+\frac i2}(x)\Delta^{\frac12}\Lambda(y^{\frac12}),\Delta^{\frac12}\Lambda(y^\frac12)\>=f(t),\\
\f(\sigma_t(x)y)
&=\<\Delta^{\frac12}\sigma_t(x)\Lambda(y^{\frac12}),\Delta^{\frac12}\Lambda(y^\frac12)\>
=\<\sigma_{t-\frac i2}\Delta^{\frac12}\Lambda(y^{\frac12}),\Delta^{\frac12}\Lambda(y^\frac12)\>=f(t-i).
\end{align*}

(c)
We may assume $y^{\frac12}\in\f_0$.
Define
\[f(z):=\<x\Delta^{-i(z+i)}\Lambda(y^{\frac12}),\Delta^{-i\bar z}\Lambda(y^{\frac12})\>.\]
Since $\Lambda(y^{\frac12})\in A_0\subset\dom\Delta$, the function $f$ is bounded and continuous on $\Im^{-1}([-1,0])$, and holomorphic on its interior, and in fact it is entire.
Then, for $t\in\R$,
\begin{align*}
\f(y\sigma_t(x))
&=\<\Lambda(y^{\frac12}\sigma_t(x)),\Lambda(y^{\frac12})\>
=\<J\Lambda(y^{\frac12}),J\Lambda(y^{\frac12}\sigma_t(x))\>\\
&=\<\Delta^{\frac12}\Lambda(y^{\frac12}),\Delta^{\frac12}\Lambda(\sigma_t(x)y^{\frac12})\>
=\<\Delta\Lambda(y^{\frac12}),\sigma_t(x)\Lambda(y^{\frac12})\>\\
&=\<\Delta\Lambda(y^{\frac12}),\Delta^{it}x\Delta^{-it}\Lambda(y^{\frac12})\>
=\<x\Delta^{-it+1}\Lambda(y^{\frac12}),\Delta^{-it}\Lambda(y^{\frac12})\>
=f(t),\\
\f(\sigma_t(y))
&=\<\Lambda(y^{\frac12}),\Lambda(y^{\frac12}\sigma_t(x))\>
=\<J\Lambda(y^{\frac12}\sigma_t(x)),J\Lambda(y^{\frac12})\>\\
&=\<\Delta^{\frac12}\Lambda(\sigma_t(x)y^{\frac12}),\Delta^{\frac12}\Lambda(y^{\frac12})\>
=\<\sigma_t(x)\Lambda(y^{\frac12}),\Delta\Lambda(y^{\frac12})\>\\
&=\<\Delta^{it}x\Delta^{-it}\Lambda(y^{\frac12}),\Delta\Lambda(y^{\frac12})\>
=\<x\Delta^{-it}\Lambda(y^{\frac12}),\Delta^{it+1}\Lambda(y^{\frac12})\>
=f(t-i).\qedhere
\end{align*}
\end{pf}



\begin{prop}[Centralizers]
Let $\f$ be a faithful semi-finite normal weight on a von Neumann algebra $M$.
For $x\in M$, the followings are all equivalent:
\begin{parts}
\item $\sigma_t(x)=x$ for all $t\in\R$,
\item $x\fm\cup\fm x\subset\fm$ and $\f(xy)=\f(yx)$ for all $y\in\fm$.
\end{parts}
The set of all $x$ satisfying one of the above conditions is called the \emph{centralizer} or the \emph{fixed point algebra} of $\f$, and denoted by $M^\f$.
\end{prop}
\begin{pf}
(a)$\Rightarrow$(b)
Let $\sigma_t(x)=x$ and $y\in\fm$, then since the constant function is entire, we have $x\in M_0$.
By (b) of the previous lemma, observing the two-point function $f$ is constant on the real line so that it is entirely constant by the identity principle, we can check that the KMS condition gives
\[\f(yx)=\f(y\sigma_t(x))=f(t)=f(t-i)=\f(\sigma_t(x)y)=\f(xy).\]

(b)$\Rightarrow$(a)
Let $x\fm\cup\fm x\subset\fm$ and $y\in(\fa_0^*\fa_0)^+$.
Then, $\sigma_t(y)\in\fa_0^*\fa_0$.
By (c) of the previous lemma, we have a two-point function such that
\[f(t)=\f(y\sigma_t(x))=\f(\sigma_{-t}(y)x)=\f(x\sigma_{-t}(y))=\f(\sigma_t(x)y)=f(t-i).\]
By the Liouville theorem $f$ is constant, so we have
\[0=\f(y\sigma_t(x))-\f(yx)=\<(\sigma_t(x)-x)\Lambda(y^{\frac12}),\Lambda(y^{\frac12})\>.\]
Since $\Lambda(\fa_0^*\fa_0)=A_0^2$ is dense in $H$, we have $\sigma_t(x)=x$.
\end{pf}





\begin{prop}[Centrally perturbed weights]
Let $\f$ be a faithful semi-finite normal weight on a von Neumann algebra $M$.
Let $h$ be a non-negative self-adjoint operator affiliated with the centralizer $M^\f$.
Then,
\[\f_h(x):=\lim_{\e\to0}\f(h_\e^{\frac12}xh_\e^{\frac12}),\qquad x\in M^+\]
is a semi-finite normal weight, where $h_\e=h(1+\e h)^{-1}$.
The weight $\f$ is faithful if and only if $h$ is non-singular.
\end{prop}
\begin{pf}
2.7, 2.8
First assume $h,k\in M_*^+$.


\end{pf}

\iffalse

\begin{prop}[Uniqueness of modular automorphism group]
Let $\f$ be a faithful semi-finite normal weight on a von Neumann algebra $M$.
For flow $\alpha$ on $M$, $\alpha$ is the modular automorphism group of $\f$ if and only if $\f$ is a KMS weight for $\alpha$.
\end{prop}
\begin{pf}
($\Rightarrow$)
Let $\alpha=\sigma$, where $\sigma=\Ad_{\Delta^{it}}$ is the modular automorphism group.
By the Tomita-Takesaki commutation theorem, we have $\sigma_t(\fa)=\fa$ and $\Lambda(\sigma_t(x))=\Delta^{it}\Lambda(x)$ for all $t\in\R$.
Then, the invariance follows as
\begin{align*}
\f(\sigma_t(y^*x))&=\f(\sigma_t(y)^*\sigma_t(x))=\<\Lambda(\sigma_t(x)),\Lambda(\sigma_t(y))\>\\
&=\<\Delta^{it}\Lambda(x),\Delta^{it}\Lambda(y)\>=\<\Lambda(x),\Lambda(y)\>=\f(y^*x),\qquad x,y\in\fn.
\end{align*}
The part (a) in the previous lemma proves that the existence of the two-point function, so $\f$ is a KMS weight.

($\Leftarrow$)
The proof is much easier if we assume $\f$ is a state.
Common core of the infinitesimal generator?
\end{pf}
\fi

\begin{thm}[Commuting weights]
Let $\f,\psi$ be a faithful semi-finite normal weights on a von Neumann algebra $M$.
TFAE
\begin{parts}
\item $\psi=\f_h$.
\item $\psi=\psi\circ\sigma_t^\f$.
\end{parts}
\end{thm}
\begin{pf}
(a)$\Rightarrow$(b)
First we claim that:
Let $h$ be a positive non-singular self-adjoint operator affiliated with $M^\f$.
Then, the modular automorphism group of $\psi:=\f_h$ is given by
\[\sigma_t^{\psi}(x)=h^{it}\sigma_t^\f(x)h^{-it}.\]
Since $h^{it}\in M^\f$, we can show the invariance.

First suppose $h\in M^{\f+}$ invertible.
Since $h$ is entire, $\fm_\f=\fm_\psi$.
By the uniqueness theorem, it is enough to show that $t\mapsto h^{it}\sigma_t^\f(x)h^{-it}$ satisfies the KMS condition.
We will construct $f$.
Take a sequence 

For the general unbounded case, we skip.

(b)$\Rightarrow$(a)
\[\sigma_s^\f((D\psi:D\f)_t)=(D\psi\circ\sigma_{-s}^\f:D\f\circ\sigma_{-s}^\f)_t=(D\psi:D\f)_t.\]
Stone's theorem, construct $h$.

\end{pf}

\begin{thm}[Semi-finiteness]
Existence of trace vs inner modular automorphism
\end{thm}
\begin{pf}

\end{pf}



\iffalse

\[*\quad*\quad*\]
\begin{thm*}[KMS characterization of modular automorphism group]
Let $\f$ be a faithful semi-finite normal weight on a von Neumann algebra $M$.
Suppose $x:\R\to\fa$ is a $\sigma$-wealy continuous map that satisfies that
\begin{enumerate}[(i)]
\item $\sup_{t\in\R}\f(x_t^*x_t+x_tx_t^*)<\infty$,
\item for each $y\in\fa$ there is a bounded continuous function $f:\Im^{-1}([-1,0])\to\C$ holomorphic on its interior such that
\[f_{x,y}(t)=\f(yx_t),\qquad f_{x,y}(t-i)=\f(x_ty).\]
Then, $x_t=\sigma_t(x_0)$.
\end{enumerate}
\end{thm*}
\begin{pf}
For each $y\in\fa$, if we let $\eta:=\Lambda(y)$ and $\xi_t:=\Lambda(x_t)$, then there is $F_\eta\in\cA(\Im^{-1}([-1,0]))$ such that
\[F_\eta(t)=\f(yx_t)=\<\Delta^{\frac12}\eta,J\xi_t\>,\qquad F_\eta(t-i)=\f(x_ty)=\<\eta,J\Delta^{\frac12}\xi_t\>.\]


The Phragmen-Lindel\"of theorem, 

$D$ is a Hilbert space since $\Delta^{\frac12}$ is closed.
By the Riesz representation theorem, there is $\zeta_z\in D$ such that
\[F_\eta(z)=\<\eta,\zeta_z\>_D=\<\eta,\zeta_z\>+\<\Delta^{\frac12}\eta,\Delta^{\frac12}\zeta_z\>,\qquad\eta\in D.\]
Then $\zeta_z$ is anti-holomorphic(?)
Let $t\in\R$.
Then,
\begin{align*}
\<\eta,\zeta_t\>_D&=F_\eta(t)=\<\Delta^{\frac12}\eta,J\xi_t\>=\<\eta,(\Delta^{-\frac12}+\Delta^{\frac12})^{-1}J\xi_t\>_D,\\
\<\eta,\zeta_{t-i}\>_D&=F_\eta(t-i)=\<\eta,J\Delta^{\frac12}\xi_t\>=\<\eta,(1+\Delta)^{-1}J\Delta^{\frac12}\xi_t\>_D,
\end{align*}
so we get by the density of $A$ in $D$ that
\[\zeta_t=(\Delta^{-\frac12}+\Delta^{\frac12})^{-1}J\xi_t,\qquad\zeta_{t-i}=(1+\Delta)^{-1}J\Delta^{\frac12}\xi_t,\]
and in particular we have $\Delta\zeta_{t-i}=\zeta_t$.
Define
\[G_\eta(z):=\<\Delta^{i\frac z2}\eta,\Delta^{-i\frac{\bar z}2}\zeta_z\>,\]
which is holomorphic in the open strip $\Im^{-1}((-1,0))$
\[G_\eta(t-i)=\<\Delta^{it}\eta,\Delta\zeta_{t-i}\>=\<\Delta^{it}\eta,\zeta_t\>=G_\eta(t),\qquad t\in\R.\]
Using the Morera and Fubini, $G_\eta$ can be extended to a bounded entire function, and the Liouville theorem is applied to deduce $G_\eta(z)$ is a constant function.


\end{pf}
\fi


\subsection{Standard form}

If $(H,P,J)$ is a standard form of $M$, then there is a unique covariant representation of $(M,G,\alpha)$, called the \emph{standard covariant representation}.


By the Friedrichs extension (a non-negative densely defined symmetric operator admits a canonical non-negative self-adjoint extension)



\subsection{Noncommutative integration}


\newpage
\section{March 8}


\subsection{Takesaki duality}
abelian group


$T(M)$, $S(M)$


Type III
begin

\newpage
\section*{Appendix}

\begin{prop}
For positive elements
\[x(1+\e x)^{-1}\]

At first, they are operator monotone.
Next, they are $\sigma$-strongly continuous on a closed subset of its domain due to the boundedness of $f_\e$, as we can see in the proof of the Kaplansky density theorem.
Finally, for each $x\in M_+$, the increasing limit $f_\e(x)\uparrow x$ in norm as $\e\to0$ implies that $\sup_\e f_\e(x)=x$.
\end{prop}
Consider for a while, a family of functions
\[f_\e(t):=t(1+\e t)^{-1},\qquad t\in(-\e^{-1},\infty),\]
parametrized by $\e>0$.
They have several properties.
At first, they are operator monotone.
Next, they are $\sigma$-strongly continuous on a closed subset of its domain due to the boundedness of $f_\e$, as we can see in the proof of the Kaplansky density theorem.
Finally, for each $x\in M_+$, the increasing limit $f_\e(x)\uparrow x$ in norm as $\e\to0$ implies that $\sup_\e f_\e(x)=x$.



\begin{prop}
\[E_n(x):=1_{[n^{-1},n]}(\Delta)x1_{[n^{-1},n]}(\Delta),\qquad E_\e(\xi):=1_{[n^{-1},n]}(\Delta)\xi\]
\end{prop}

\begin{prop}
\[R_n(x):=\sqrt{\frac n\pi}\int e^{-ns^2}\alpha_s(x)\,ds,\qquad R_n(\xi):=\sqrt{\frac n\pi}\int e^{-ns^2}\Delta^{is}(x)\,ds\]
\end{prop}



\end{document}