\documentclass{../note}
\usepackage{../../ikany}


\begin{document}
\title{Lebesgue Theory}
\author{Ikhan Choi}
\maketitle
\tableofcontents

\part{Measure theory}





\chapter{Measures and $\sigma$-algebras}


\section{Measures}

\begin{prb}[Definition of measures]
Let $(\Omega,\cM)$ be a measurable space.
A \emph{measure} on $\cM$ is a set function $\mu:\cM\to[0,\infty]:\varnothing\mapsto0$ that is \emph{countably additive}: we have
\[\mu\Bigl(\bigsqcup_{i=1}^\infty E_i\Bigr)=\sum_{i=1}^\infty\mu(E_i)\]
for $(E_i)_{i=1}^\infty\subset\cM$.
Here the squared cup notation reads the disjoint union.
\end{prb}

\begin{prb}[Continuity of measures]

\end{prb}

\section{Carath\'eodory extension}


\begin{prb}[Outer measures]
Let $\Omega$ be a set.
An \emph{outer measure} on $\Omega$ is a set function $\mu^*:\cP(\Omega)\to[0,\infty]:\varnothing\mapsto0$ such that
\begin{enumerate}[(i)]
\item $\mu^*$ is \emph{monotone}: we have
\[S_1\subset S_2\Rightarrow\mu^*(S_1)\le\mu^*(S_2)\]
for $S_1,S_2\in\cP(\Omega)$,
\item $\mu^*$ is \emph{countably subadditive}: we have
\[\mu^*\Bigl(\bigcup_{i=1}^\infty S_i\Bigr)\le\sum_{i=1}^\infty\mu^*(S_i)\]
for $(S_i)_{i=1}^\infty\subset\cP(\Omega)$.
\end{enumerate}
Compairing the definition of measures, we can see the outer measures extend the domain to the power set, but loosen the countable additivity to monotone countable subadditivity.
\begin{parts}
\item A set function $\mu^*:\cP(\Omega)\to[0,\infty]:\varnothing\mapsto0$ is an outer measure if and only if $\mu^*$ is \emph{monotonically countably subadditive}:
\[S\subset\bigcup_{i=1}^\infty S_i\Rightarrow\mu^*(S)\le\sum_{i=1}^\infty\mu^*(S_i)\]
for $S\in\cP(\Omega)$ and $(S_i)_{i=1}^\infty\subset\cP(\Omega)$.
\item
For $\varnothing\in\cA\subset\cP(\Omega)$, let $\rho:\cA\to[0,\infty]:\varnothing\mapsto0$ be a set function.
We can associate an outer measure $\mu^*:\cP(\Omega)\to[0,\infty]$ by defining as
\[\mu^*(S):=\inf\left\{\,\sum_{i=1}^\infty\rho(A_i):S\subset\bigcup_{i=1}^\infty A_i,\ A_i\in\cA\,\right\},\]
where we use the convention $\inf\varnothing=\infty$.
\end{parts}
\end{prb}
\begin{pf}

\end{pf}

\begin{prb}[Carath\'eodory measurable sets]
Let $\mu^*$ be an outer measure on a set $\Omega$.
We want to construct a measure by restriction of $\mu^*$ on a properly defined $\sigma$-algebra.
A subset $E\subset\Omega$ is called \emph{Carath\'eodory measurable} relative to $\mu^*$ if
\[\mu^*(S)=\mu^*(S\cap E)+\mu^*(S\setminus E)\]
for every $S\in\cP(\Omega)$.
Let $\cM$ be the collection of all Carath\'eodory measurable subsets relative to $\mu^*$.
\begin{parts}
\item $\cM$ is an algebra and $\mu^*$ is finitely additive on $\cM$.
\item $\cM$ is a $\sigma$-algebra and $\mu^*$ is countably additive on $\cM$.
\item The measure $\mu:=\mu^*|_\cM:\cM\to[0,\infty]$ is complete.
\end{parts}
\end{prb}
\begin{pf}

\end{pf}


\begin{prb}[Carath\'eodory extension theorem]
For $\varnothing\in\cA\subset\cP(\Omega)$, let $\rho:\cA\to[0,\infty]:\varnothing\mapsto0$ be a set function.
Consider the following two conditions:
\begin{enumerate}[(i)]
\item We have the monotone countable subadditivity:
\[A\subset\bigcup_{i=1}^\infty A_i\Rightarrow\rho(A)\le\sum_{i=1}^\infty\rho(A_i)\]
for $A\in\cA$ and $(A_i)_{i=1}^\infty\subset\cA$.
\item For every $B,A\in\cA$, and for any $\e>0$, there are $\{B'_j\}_{j=1}^\infty$ and $\{B''_j\}_{j=1}^\infty\subset\cA$ such that
\[B\cap A\subset\bigcup_{j=1}^\infty B'_j\quad\text{ and }\quad B\setminus A\subset\bigcup_{j=1}^\infty B''_j,\]
and
\[\rho(B)+\e>\sum_{j=1}^\infty\rho(B'_j)+\sum_{j=1}^\infty\rho(B''_j).\]
\end{enumerate}
Let $\mu^*:\cP(\Omega)\to[0,\infty]$ be the associated outer measure of $\rho$, and $\mu:\cM\to[0,\infty]$ the measure defined by the restriction of $\mu^*$ on Carath\'eodory measurable subsets.
The above two conditions give a sufficient condition for $\mu$ to be a measure on a $\sigma$-algebra containing $\cA$.
\begin{parts}
\item $\mu^*|_\cA=\rho$ if (i) is satisfied.
\item $\cA\subset\cM$ if (ii) is satisfied.
\end{parts}
\end{prb}
\begin{pf}
(a)
Clearly $\mu^*(A)\le\rho(A)$ for $A\in\cA$.
We may assume $\mu^*(A)<\infty$.
For arbitrary $\e>0$ there is $\{A_i\}_{i=1}^\infty$ such that $A\subset\bigcup_{i=1}^\infty A_i$ and
\[\mu^*(A)+\e>\sum_{i=1}^\infty\rho(A_i)\ge\rho(A).\]
Limiting $\e\to0$, we get $\mu^*(A)\ge\rho(A)$.

(b)
Let $S\in\cP(\Omega)$ and $A\in\cA$.
It is enough to check the inequality $\mu^*(S)\ge\mu^*(S\cap A)+\mu^*(S\setminus A)$ for $S$ with $\mu^*(S)<\infty$, so we may assume there is a countable family $\{B_i\}_{i=1}^\infty\subset\cA$ such that $S\subset\bigcup_{i=1}^\infty B_i$.
Then, we have $B_i\cap A\subset\bigcup_{j=1}^\infty B'_{i,j}$ and $B_i\setminus A\subset\bigcup_{j=1}^\infty B''_{i,j}$ satisfying
\[\mu^*(S)+\e>\sum_{i=1}^\infty(\rho(B_i)+\frac\e{2^{i+1}})
>\sum_{i,j=1}^\infty\rho(B'_{i,j})+\sum_{i,j=1}^\infty\rho(B''_{i,j})\ge\mu^*(S\cap A)+\mu^*(S\setminus A).\]
Therefore, $A$ is Carath\'eodory measurable relative to $\mu^*$.
\end{pf}






\begin{prb}[Uniqueness of Carath\'eodory extensions]
The Carath\'eodory extension theorem provides with a uniqueness theorem for measures.
\end{prb}
\begin{pf}
\end{pf}


\section*{Exercises}

\begin{prb}[Semi-rings and semi-algebras]
We will prove a simplified Carath\'eodory extension with respect to \emph{semi-rings} and \emph{semi-algebras}.
Let $\cA$ be a collection of subsets of a set $\Omega$ such that $\varnothing\in\cA$.
We say $\cA$ is a semi-ring if it is closed under finite intersection, and the complement is a finite union of elements of $\cA$.
We say $\cA$ is a semi-algebra

Let $\cA$ be a semi-ring of sets over $\Omega$.
Suppose a set function $\rho:\cA\to[0,\infty]:\varnothing\mapsto0$ satisfies
\begin{enumerate}[(i)]
\item $\rho$ is \emph{disjointly countably subadditive}: we have
\[\rho\Bigl(\bigsqcup_{i=1}^\infty A_i\Bigr)\le\sum_{i=1}^\infty\rho(A_i)\]
for $(A_i)_{i=1}^\infty\subset\cA$,
\item $\rho$ is \emph{finitely additive}: we have
\[\rho(A_1\sqcup A_2)=\rho(A_1)+\rho(A_2)\]
for $A_1,A_2\in\cA$.
\end{enumerate}
A set function satisfying the above conditions are occasionally called a \emph{pre-measure}.
\begin{parts}
\item
\item 
\end{parts}
\end{prb}

\begin{prb}[Monotone class lemma]
alternative direct proof method without using Carath\'eodory extension.
\end{prb}





\chapter{Measures on the real line}

\begin{prb}[Distribution functions]
\end{prb}

\begin{prb}[Helly selection theorem]
\end{prb}

\begin{prb}[Non-Lebesgue measurable set]
\end{prb}


\section*{Exercises}

\begin{prb}[Steinhaus theorem]
Let $\E\subset\R$ be Lebesgue measurable with $\lambda(E)>0$.
\begin{parts}
\item For any $\alpha<1$, there is an interval $I=[a,b]$ such that $\lambda(E\cap I)/\lambda(I)>\alpha$.
\item $E-E$ contains an open interval containing zero.
\end{parts}
\begin{pf}
(a)
\end{pf}
% convolution으로 푸는 방법: continuous approximation　이 레벨에선 무리인듯
\end{prb}




\section*{Problems}
\begin{enumerate}
\item* Every Lebesgue measurable set in $\R$ of positive measure contains an arbitrarily long arithmetic progression.
\end{enumerate}

















\chapter{Measurable functions}

\section{Extended real numbers}


\section{Simple functions}
\begin{prb}[Measurability of pointwise limits]
\end{prb}
\begin{pf}
Let $f(x)=\lim_{n\to\infty}s_n(x)$.

\end{pf}

Every measurable extended real-valued function is a pointwise limit of simple functions.




\begin{prb}[Egorov theorem]
Let $f_n:\Omega\to\R$ be a sequence of measurable functions on a finite measure space $(\Omega,\mu)$ that converges almost everywhere.
\begin{parts}
\item For every $\e>0$,
\[\bigcap_{n\ge n_0}\{\,x:|f_n(x)|<\e\,\}\uparrow\text{ a full set }\quad\text{ as }\quad n_0\to\infty.\]
\item For $\e>0$, there is a measurable $E_\e\subset\Omega$ such that $\mu(\Omega\setminus E_\e)<\e$ and $f_n$ is uniformly convergent on $E_\e$.
\end{parts}
\end{prb}
\begin{pf}
(a)
We may assume $f_n\to0$.
The set of convergence is given by
\[\bigcap_{k>0}\ \bigcup_{n_0>0}\ \bigcap_{n\ge n_0}\{\,x:|f_n(x)|<\e\,\},\]
which is a full set.
We want to get rid of the dependence on the point $x$ of $n_0$ in the union $\bigcup_{n_0>0}$.
Since
\[\bigcap_{n\ge n_0}\{\,x:|f_n(x)|<\e\,\}\]
is increasing as $n_0\to\infty$ to a full set.

(b)
We can find $n_0=n_0(k,\e)$ such that
\[\mu(\bigcap_{n\ge n_0}\{\,x:|f_n(x)|<\tfrac1k\,\})>\mu(\Omega)-\frac\e{2^k}.\]
Then,
\[\mu(\bigcap_{k>0}\ \bigcap_{n\ge n_0}\{\,x:|f_n(x)|<\tfrac1k\,\})>\mu(\Omega)-\e.\]
If we define
\[E_\e:=\bigcap_{k>0}\ \bigcap_{n\ge n_0}\{\,x:|f_n(x)|<\tfrac1k\,\},\]
then for any $k>0$ and $x\in E_\e$, and with the $n_0(k,\e)$ we have chosen,
we have
\[n\ge n_0\quad\Rightarrow\quad |f_n(x)|<\frac1k.\qedhere\]
\end{pf}



\section*{Exercises}
\begin{prb}[Cauchy's functional equation]
Let $f:\R\to\R$ be a function.
Cauchy's functional equation refers to the equation $f(x+y)=f(x)+f(y)$, satisfied for all $x,y\in\R$.
Suppose $f$ satisfies the Cauchy functional equation.
We ask if $f$ is linear, that is $f(x)=ax$ for all $x\in\R$, where $a:=f(1)$.
\begin{parts}
\item $f(x)=ax$ for all $x\in\Q$, but there is a nonlinear solution of Cauchy's functional equation.
\item If $f$ is conitnuous at a point, then $f$ is linear.
\item If $f$ is Lebesgue measurable, then $f$ is linear.
\end{parts}
\end{prb}









\part{Lebesgue integral}


\chapter{Convergence theorems}
\section{Definition of Lebesgue integral}
\section{Convergence theorems}

% Stein: Egorov $\to$ BCT $\to$ Fatou $\to$ MCT $\to$ L1<M\\
% Stein: BCT + L1<M $\to$ DCT\\
% Folland: MCT $\to$ Fatou $\to$ DCT $\to$ BCT
\begin{prb}[Monotone convergence theorem]
\end{prb}




\section{Radon-Nikodym theorem}


\section{Modes of convergence}

\begin{prb}[Borel-Cantelli lemma]
\end{prb}

\begin{prb}[Convergence in measure]
Let $(X,\mu)$ be a measure space.
Let $f_n$ and $f$ be measurable.
We say $f_n$ converges to $f$ \emph{in measure} if for each $\e>0$ we have
\[\lim_{n\to\infty}\mu(\{\,x:|f_n(x)-f(x)|>\e\,\})=0.\]
\begin{parts}
\item If $f_n\to f$ in $L^1$, then $f_n\to f$ in measure.
\item If $f_n\to f$ in measure, then there is a subsequence $f_{n_k}$ such that $f_{n_k}\to f$ almost everywhere.
\end{parts}
\end{prb}
\begin{pf}
(b)
We can extract a subsequence $f_{n_k}$ such that
\[\mu(\{\,x:|f_{n_k}-f|>\tfrac1k\,\})>\tfrac1{2^k}.\]
Since
\[\sum_{k=1}^\infty\mu(\{\,x:|f_{n_k}-f|>\tfrac1k\,\})<\infty,\]
by the Borel-Cantelli lemma, we get
\[\mu(\limsup_k\{\,x:|f_{n_k}-f|>\tfrac1k\,\})=0.\]
Therefore, $f_{n_k}$ converges $\mu$-a.e.
\end{pf}


\chapter{Product measures}
\section{Fubini-Tonelli theorem}
\section{Lebesgue measure on Euclidean spaces}


\chapter{Measures on metric spaces}
\section{Borel measures}

\section{Riesz-Markov-Kakutani representation theorem}

locally compact

\section{Hausdorff measures}









\part{Linear operators}



\chapter{Lebesgue spaces}
\section{$L^p$ spaces}
\section{$L^1$ spaces}
\section{$L^2$ spaces}
\section{$L^\infty$ spaces}








\chapter{Bounded linear operators}
\section{Continuity}
Schur test

\section{Density arguments}
extension of operators

\section{Interpolation}
weak Lp, marcinkiewicz




\chapter{Convergence of linear operators}
\section{Translation and multiplication operators}

\section{Convolution type operators}
approximation of identity

\section{Computation of integral transforms}











\part{Fundamental theorem of calculus}

\chapter{Weak derivatives}

The space of weakly differentiable functions with respect to all variables $=W_\loc^{1,1}$.

\begin{prb}[Product rule for weakly differentiable functions]
We want to show that if $u$, $v$, and $uv$ are weakly differentiable with respect to $x_i$, then $\pd_{x_i}(uv)=\pd_{x_i}uv+u\pd_{x_i}v$.
\begin{parts}
\item If $u$ is weakly differentiable with respect to $x_i$ and $v\in C^1$, then $\pd_{x_i}(uv)=\pd_{x_i}uv+u\pd_{x_i}v$.
\end{parts}
\end{prb}


\begin{prb}[Interchange of differentiation and integration]
Let $f:\Omega_x\times\Omega_y\to\R$ be such that $\pd_{x_i}f$ is well-defined. Suppose $f$ and $\pd_{x_i}f$ are locally integrable in $x$ and integrable $y$.

Then,
\[\pd_{x_i}\int f(x,y)\,dy=\int\pd_{x_i}f(x,y)\,dy.\]
\end{prb}





\chapter{Absolutely continuity}

\begin{parts}
\item $f$ is $\Lip_\loc$ iff $f'$ is $L_\loc^\infty$
\item $f$ is $\textrm{AC}_\loc$ iff $f'$ is $L_\loc^1$
\end{parts}
\begin{parts}
\item $f$ is $\Lip$ iff $f'$ is $L^\infty$
\item $f$ is $\textrm{AC}$ iff $f'$ is $L^1$
\item $f$ is $\textrm{BV}$ iff $f'$ is a finite regular Borel measure
\end{parts}



\chapter{Lebesgue differentiation theorem}

\end{document}




\pd{f}{x}{y}가 원점에서 연속이 아니면 못바꾼다?
라고 생각하지 말고 계산된 편미분계수가 편도함수를 잘 표현하지 못할 수 있다고 이해하자.
즉, 편미분계수는 C2임을 보일 때 말고는 C2가 아닌 경우에 쓸모가 없다
