\documentclass{../../large}
\usepackage{../../ikhanchoi}


\begin{document}
\title{Homotopy theory}
\author{Ikhan Choi}
\maketitle
\tableofcontents
\part{Fiber bundles}
\chapter{Principal bundles}

\section{Category of bundles}
\begin{prb}[Pullback and restricted bundles]
\end{prb}

\begin{prb}[Product of bundles]
the \emph{Fiber product} or the \emph{Whitney sum}
\end{prb}



\section{Classifying spaces}

\section{\v Cech cohomology}

\begin{prb}
Let $\{U_\alpha\}_\alpha$ be an open cover of a topological space $X$.
We say a presheaf $\cF$ on $X$ is sheaf if the sequence
\begin{cd}
\cF(U)\rar&\displaystyle\prod_\alpha\cF(U_\alpha)\rar[shift left]{\alpha}\rar[shift right,swap]{\beta}&\displaystyle\prod_{\alpha,\beta}\cF(U_\alpha\cap U_\beta)
\end{cd}
is an equalizer.
\end{prb}

\begin{prb}
Let $\cF$ be a preseah of groups and let $\cU=\{U_\alpha\}_\alpha$ be an ordered open cover of a toplogical space $X$.

\begin{cd}
\displaystyle\prod_\alpha\cF(U_\alpha) \rar[shift left]{\res_\alpha}\rar[shift right,swap]{\res_\beta}
&\displaystyle\prod_{\alpha<\beta}\cF(U_\alpha\cap U_\beta) \rar["\res_\beta"description]\rar[shift left=2]{\res_\alpha}\rar[shift right=2,swap]{\res_\gamma}
&\displaystyle\prod_{\alpha<\beta<\gamma}\cF(U_\alpha\cap U_\beta\cap U_\gamma)
\end{cd}
\begin{es}
C^0(\cU,\cF) \>{\delta} C^1(\cU,\cF) \>{\delta} C^2(\cU,\cF) \>{\delta} \cdots
\end{es}

\[f=\{f_\alpha:U_\alpha\to\GL(k,\R)\}_\alpha\in\prod_\alpha\cF(U_\alpha)=C^0(\cU,\cF)\]

\end{prb}

\begin{prb}
Let $G$ be a sheaf of groups.
Then, we have a natural one-to-one correspondence
\[\left\{\begin{tabular}{c}isomorphism classes of\\principal $G$-bundles\end{tabular}\right\}\xrightarrow{\sim}H^1(B,G).\]
\end{prb}
\begin{pf}
(Injectivity)
We show the correspondence is left invertible.
Let $p:E\to B$ be a principal $G$-bundle.
Define $p':E'\to B$ by
\[E':=\left(\bigsqcup_\alpha\{\alpha\}\times U_\alpha\times\R^k\right)/\sim,\]
where the equivalence relation $\sim$ denotes $(\alpha,b,g_{\alpha\beta}(v))\sim(\beta,b,v)$ with $b\in U_\alpha\cap U_\beta$ for some $\alpha,\beta$, and define $p':E'\to B$, which is well-defined bundle.

We first check that $p'$ is a principal $G$-bundle.

(Surjectivity)
\end{pf}






\chapter{Vector bundles}
\section{}
\begin{prb}[Vector space structure on total spaces]

\end{prb}

\begin{prb}[Vector bundle maps]
Let $p_1:E_1\to B$ and $p_2:E_2\to B$ be vector bundles.
\begin{parts}
\item A vector bundle map $u$ over $B$ is vector bundle isomorphism if and only if it is a fiberwise linear isomorphism.
\end{parts}
\end{prb}

\begin{prb}[Tautological bundles]
\end{prb}

\begin{prb}[Homotopy properteis]
Let $p:E\to B$ be a vector bundle

If $p_1:E_1\to B\times[0,\frac12]$ and $p_2:E_2\to B\times[\frac12,1]$ are trivial, then 
\begin{parts}
\item 
\end{parts}
\end{prb}

\begin{prb}[Principal bundle over the general linear group]
\end{prb}



\chapter{Characteristic classes}



\part{K-theory}

\part{}

\part{}

\end{document}