\documentclass{../../large}
\usepackage{../../ikhanchoi}


\begin{document}
\title{Representation Theory}
\author{Ikhan Choi}
\maketitle
\tableofcontents

\part{Finite groups}
\chapter{Character theory}

\section{Irreducible representations}
\begin{prb}[Definition of group representations]
\end{prb}

\begin{prb}[Intertwining maps]
\end{prb}

\begin{prb}[Subrepresentations]
We say \emph{invariant} or \emph{stable}
\end{prb}

\begin{prb}[Irreducible representations]
indecomposable and irreducible
\end{prb}

\begin{prb}[Maschke's theorem]
Let $G$ be a finite group and $k$ be a field.
Suppose the characteristic of $k$ does not divide $|G|$.
Let $V$ be a finite-dimensional representation of $G$ over $k$.
\begin{parts}
\item Every invariant subspace $W$ of $V$ has a complement $W'$ in $V$ that is also invariant.
\item $V$ is isomorphic to the direct sum of irreducible representations of $G$ over $k$.
\item If $k=\R$ or $\C$, then $V$ admits an inner product such that $W\perp W'$ and $\rho_V(g)$ is unitary for all $g\in G$.
\end{parts}
\end{prb}

\begin{prb}[Schur's lemma]
Let $G$ be a group and $k$ be a field.
Let $V$ and $W$ be irreducible representations of $G$ over $k$.
Let $\psi:V\to W$ be an intertwining map.
\begin{parts}
\item If $V\not\cong W$, then $\psi=0$.
\item If $V\cong W$, then $\psi$ is an isomorphism.
\item If $k$ is algebraically closed and $\dim V<\infty$, then every intertwining map $\psi:V\to V$ is a homothety.
\end{parts}
\end{prb}




\section{Group algebra}


\begin{prb}[Modules and representations]
ring <-> group
module <-> representation
finitely generated <-> finite dimensional
\end{prb}

\begin{prb}[Wedderburn's theorem]
central idempotents
dimension computation
\end{prb}

\begin{prb}[Group algebra]
regular representation
$k[G]$-module and $G$-representation correspondence
\begin{parts}
\item $\C[G]$ is the direct sum of all irreducible representations.
\item $|G|=\sum_{[V]\in\hat G}(\dim V)^2$.
\end{parts}
\end{prb}

\begin{prb}
The number of irreducible representations and the number of conjugacy classes
double counting on $Z(\C[G])$.
\end{prb}



\section{Characters}




\begin{prb}[Space of class functions]
Ring and inner product structure on the space of class functions.
\begin{parts}
\item $\dim\hom_G(V,W)=\<\chi_V,\chi_W\>$.
\item Irreducible characters form an orthonormal basis of the space of class functions.
\end{parts}
\end{prb}

\begin{prb}[Characters classify representations]
Let $G$ be a finite group and let $\mathbf{Rep}(G)$ be the category of finite-dimensional representations of $G$ over $\C$.
\[\Tr:\mathbf{Rep}(G)\to\{\text{finite sum of irreducible characters}\}\]
surjectivity: trivial
injectivity:
	Suppose two characters are equal.
	Maschke -> all characters are sum of irreducible characters
	Schur -> orthogonality, so the coefficients are all equal
	irreducible-factor-wisely construct an isomoprhism.
\end{prb}



\begin{prb}[Character table]
computation of matrix elements by character table
abelian group, 1dim rep lifting
\begin{center}
$\begin{array}{c|ccc}
S^3&e&(12)&(123)\\\hline
1&1&1&1\\
\e&1&-1&1\\
\rho&2&0&-1
\end{array}$
\end{center}
\end{prb}






the dual inner product: conjugacy check
relation to normal subgroups
center of rep




algebraic integer
dim of irrep divides group order
burnside pq theorem





\chapter{Classification of representations}
\section{Symmetric groups}
young tableux

\section{Linear groups over finite fields}
GL2 and SL2 over finite fields

\section{Induced representations}
induction and restriction of reps (from and to subgroup)
frobenius reciprocity, mackey theory





tensoring, complex, real
symmetric, exterior


\chapter{Brauer theory}












\part{Lie algebras}
\chapter{Semisimple Lie algebras}
\section{}

group acts on an algebra $A$(e.g. $\End(V)$).
then its group algebra acts on $A$.
Lie algebra acts on $A$, and this Lie algebra information is enough to recover the group action.
Geometric meaning of Lie algebra action?

Lie algebra can only considered as a quantization of Poisson bracket.
How can the Poisson bracket embodies the group action?






Following Humphrey's book, let $L$ be always finite dimensional Lie algebra unless stated.

\begin{prb}
Every associative algebra is a Lie algebra, where the Lie bracket is given by the commutator.
For a Lie algebra, we are 

Intuitions of subalgebras, ideals, derivations.
Intuitions of solvable, nilpotent, and semisimple Lie algebras.
Constructing representations, trace forms,

The \emph{general linear Lie algebra} $\fgl(V)$ is just $\End(V)$ with a Lie bracket $[x,y]:=xy-yx$.
\end{prb}

\begin{prb}[Derivations]
Let $L$ be a Lie algebra.
A \emph{derivation} of $L$ is a linear map $\delta:L\to L$ such that \[\delta([x,y])=[\delta(x),y)]+[x,\delta(y)]\]
for all $x,y\in L$.
The set of derivations $\Der(L)$ of $L$ is a subalgebra of $\fgl(L)$, and we have the \emph{adjoint representation} $L\to\Der(L)\le\fgl(L)$ of $L$.
If $I$ is an ideal, then we have a faithful representation $\ad:L\to\ad L\le\Der(I)\le\fgl(I)$.
\end{prb}

\begin{prb}[Inner derivations and automorphisms]
Let $L$ be a Lie algebra.

The linear map $\ad x=[x,-]:L\to L$ for $x\in L$ is derivation, and derivation of this form is called \emph{inner}, and they form an ideal of $\Der(L)$.

Automorphisms of the form $\exp(\ad x)$ with nilpotent $\ad x$ generates a normal subgroup of $\Aut(L)$, and each generator is called \emph{inner automorphisms}.
\end{prb}





\begin{prb}[Solvable and nilpotent Lie algebras]
Let $L$ be a Lie algebra.
If the \emph{derived series} $L^{(0)}=L$, $L^{(n)}=[L^{(n-1)},L^{(n-1)}]$ eventually vanishes, then we call $L$ \emph{solvable}.

If $L$ is solvable, then its subalgebras and quotient algebras are all solvable.
If $I$ is a solvable ideal of $L$ such that $L/I$ is solvable, then $L$ is solvable.
The sum of two solvable ideals is also solvable.


Let $L$ be a Lie algebra.
If the \emph{lower central series} $L^0=L$, $L^n=[L,L^{n-1}]$ eventually vanishes, then we call $L$ \emph{nilpotent}.
It is a stronger notion than solvability.

If $L$ is nilpotent, then its subalgebras and quotient algebras are all nilpotent.
If $L/Z(L)\cong\ad(L)\subset\fgl(L)$ is nilpotent, then $L$ is nilpotent.
If $L$ is non-zero and nipotent, then $Z(L)$ is non-trivial.
\end{prb}

\begin{prb}[Engel's theorem]
.
\begin{parts}
\item A linear Lie algebra $L\subset\fgl(V)$ consists of nilpotent endomorphisms if and only if $L\subset\fn(V)$ for a certain basis of $V$.
\item An abstract Lie algebra $L$ is nilpotent if and only if $\ad(L)$ consists of nilpotent endomorphisms.
\item If $L\subset\fgl(V)$ is nilpotent in $\End(V)$, then there is a \emph{common eigenvector} $v\in V$ such that $[L,v]=0$, i.e. there is a flag $V_i$ such that $xV_i\subset V_{i-1}$...?
\end{parts}
\end{prb}
\begin{pf}



Let $L$ be an ad-nilpotent Lie algebra.
Then, every element of $\ad L\subset\fgl(L)$ is a nilpotent endomorphism, so there is $x\in L$ such that $[L,x]=0$, which implies $Z(L)\ne0$.
Since $L/Z(L)$ is also ad-nilpotent, and by induction on dimension, $L/Z(L)$ is nilpotent.
Therefore, $L$ is nilpotent.
\end{pf}


\begin{prb}[Lie's theorem]
Let $\F$ have characteristic zero and be algebraically closed.
\begin{parts}
\item A linear Lie algebra $L\subset\fgl(V)$ is solvable if and only if $L\subset\ft(V)$ for a certain basis of $V$.
\item If $L$ is solvable, then there is a flag $V_i$ such that $xV_i\subset V_i$.
\item Let $L$ be an abstract Lie algebra. $L$ is solvable if and only if $[L,L]$ is nilpotent.
\item Every finite-dimensional irreduciable representation of a solvable Lie algebra is one-dimensional.
\end{parts}
\end{prb}
\begin{pf}
Use induction on dimension.
Since $L/[L,L]$ is a non-trivial commutative Lie algebra, in which every subspace is an ideal, we can show the existence of an ideal $K$ of $L$ with codimension one by pullback.

By the induction assumption, we have a common eigenvector in $V$ for $K$ so that we have the ``eigenvalue'' linear functional $\kappa:K\to\F$ such that the ``eigenspace'' of $\kappa$ as
\[V_\kappa:=\{v\in V:xv=\kappa(x)v\text{ for }x\in K\}\]
is non-trivial.

Let $L=K+\F z$ with $z\in\fgl(V)$.
If $V_\kappa$ is invariant by $L$, then $V_\kappa$ contains an eigenvector of $z$ by the fact that $\F$ is algebraically closed, so we can extend $\kappa$ to obtain $\lambda:L\to\F$ such that $(V_\kappa)_\lambda$ is non-trivial.

We now show that $V_\kappa$ is invariant by $L$.
Let $v\in V_\kappa$ and $x\in L$.
Since
\[yxv-\lambda(y)xv=yxv-xyv=[y,x]v=\lambda([y,x])v\]
for $y\in K$, we have to show $\lambda([y,x])=0$.
Take $n$ to be largest such that $v,\cdots,x^{n-1}v$ are linearly independent.
Since $[x,y]$ is upper triangular matrix relative to the basis $v,\cdots,x^{n-1}v$ and the diagonal entries are $\lambda([x,y])$.
Since the trace of $[x,y]$ must be zero, we have $\lambda([x,y])=0$ because $\F$ has characteristic zero.

\end{pf}

There is a linear functional $\lambda:L\to\F$ such that $\lambda|_{[L,L]}=0$ and $V_\lambda$ is non-trivial.
$V_\kappa$


For a representation $\pi:\fg\to\fgl(V)$, then a weight of $V$ is a linear functional $\lambda:\pi(\fh)\to\F$ such that the weight space $V_\lambda$ is non-trivial.



\begin{prb}[Jordan-Chevalley decomposition]
Let $V$ be a finite-dimensional vector space over a field $K$.
Let $x\in\End(V)$.
Even if $\F$ is not algebraically closed, we have a generalization of Jordan decomposition as follows:

$x=x_s+x_n$ iff $x$ is the product of separable polynomials.
\begin{parts}
\item There exist unique $x_s,x_n\in\End(V)$ such that $x=x_s+x_n$ and $x_s$ semisimple, $x_n$ nilpotent.
\item $x_s$ and $x_n$ are polynomials in $x$.
\item If $x$ maps $B$ to $A$, then $x_s$ and $x_n$ also map $B$ to $A$ for subspaces $A\le B\le V$.
\end{parts}
\end{prb}
\begin{pf}

\end{pf}

\begin{prb}[Cartan criterion]
We will show a powerful criterion for solvability.
Let $\fg$ be a finite-dimensional Lie algebra over a field $\F$, and consider a finite-dimensional faithful representation $\fg\subset\fgl(V)$.
\begin{parts}
\item If $\tr(xy)=0$ for all $x\in[\fg,\fg]$ and $y\in \fg$, then $\fg$ is solvable.
\end{parts}
\end{prb}
\begin{pf}
Since the nilpotency of $[\fg,\fg]$ implies the solvability of $\fg$, it suffices to show the derived Lie algebra $[\fg,\fg]$ is nilpotent.



\item Let $A\subset B$ be two linear subspaces of $\fgl(V)$. Let
\[M:=\{x\in\fgl(V):[x,B]\subset A\}.\]
If $x\in M$ satisfies $\tr(xy)=0$ for all $y\in M$, then $x$ is nilpotent.
\end{pf}




\begin{prb}[Levi decomposition]

Therefore, $\fg$ admits a unique maximal solvable ideal, called \emph{radical}.
Since the center is a solvable ideal, the center of a semisimple Lie algebra is trivial.

A canonical example of a solvable Lie algebra is the Lie algbera of upper triangular matrices.
The radical of $\fgl(n,K)$ is $\fsl(n,K)$.($K$ cahracteristic zero?) Upper triangular matrices do not form an ideal of $\fgl(n,K)$.

We have $[\ft,\ft]=\fn$, $\ft=\fd\otimes\fn$. $\ft$ is a solvable subalgebra of $\fgl$, but not a solvable ideal.

$\fsl(n,\F)$ is simple if $\char K=0$.
\begin{parts}
\item $\fg$ is semi-simple if and only if the radical is trivial.
\end{parts}
\end{prb}


\begin{prb}[Killing form]
Let $\fg$ be a finite-dimensional Lie algebra over a field $\F$.
Since an endomorphism algebra of a finite-dimensional vector space over a field has a canonical symmetric bilinear form defined called the trace form, the adjoint representation $\ad:\fg\to\fgl(\fg)$ induces a symmetric bilinear form $\kappa:\fg\times\fg\to\F$ called the \emph{Killing form} such that $\kappa(x,y):=\tr(\ad x\ad y)$ for $x,y\in\fg$.
\begin{parts}
\item The kernel of $\kappa$ is contained in the radical of $L$, and triviality is equivalent; $L$ is semisimple if and only if $L$ is non-degenerate. (Here we use Cartan's criterion)
\item If $L$ is semisimple, then it is the direct sum of simple ideals.
\item If $L$ is semisimple, then every derivation is inner.
\item If $L$ is semisimple, then $L=[L,L]$ and every subalgebras and quotients are semisimple.
\end{parts}
\end{prb}
\begin{pf}

Suppose $\rad\fg=0$.
The restriction of the Killing form of $\fg$ to an ideal $\fraki\subset\fg$ is the Killing form of $\fraki$.

\end{pf}


\begin{prb}[Weyl's theorem on complete reducibility]
Finite dimensional representation of a semisimple Lie algebra is completely reducible.
Preservation of Jordan decomposition.
\end{prb}

\begin{prb}[Toral subalgebras]
Cartan subalgebra uniqueness (conjugacy theorem)
\end{prb}




\chapter{Root systems}
root space decomposition
Killing form on Cartan subalgebra
integrality and rationality
Weyl group


Classification:
Coxeter graph
Dynkin diagram
Real forms





\chapter{Representations of Lie algebras}
\section{Representations of $\fsl(2,\C)$}
\begin{prb}[Pauli matrices]
Pauli matrices are
\[\sigma_1=\mat{0&1\\1&0},\quad\sigma_2=\mat{0&-i\\i&0},\quad\sigma_3=\mat{1&0\\0&-1}.\]
\begin{parts}
\item $\{\sigma_1,\sigma_2,\sigma_3\}$ is a basis of complex Lie algebra $\fsl(2,\C)$, and $\{i\sigma_1,i\sigma_2,i\sigma_3\}$ is a basis of real Lie algebra $\fso(3)$.
\item For a unit vector $n=(n_1,n_2,n_3)\in\R^3$, $n_1\sigma_1+n_2\sigma_2+n_3\sigma_3$ has eigenvalues $\pm1$.
\end{parts}
\end{prb}
\section{Highest weight theory}

Isomorphism and conjugacy theorem?

Existence:
Universal enveloping algebra and the PBW theorem
Verma module definition and quotient finiteness proof

\section{Character theory}

\section{Multiplicity formulas}

\section*{Exercises}
\begin{prb}[Triplets and quadraplets]
Let $(\pi_2,V_2)$ be the irreducible representation of $\fsl(2,\C)$ of degree two.
Consider $V_2\otimes V_2$.
Cartan element $S_z$.
$V_2^{\otimes3}$.
\end{prb}
\begin{prb}[Casimir element]
Casimir element decomposes a representation into irreducible representations.
For a faithful representation $\f:L\to\fgl(V)$, we can associate a non-degenerate trace form since $L$ is semisimple.
Then, the \emph{Casimir element} of the representation $\f$ is $C_\f:=\sum_i\f(x_i)\f(y_i)\in\End(V)$ where $i$ runs over dual bases relative to the trace form.
\end{prb}







\part{Algebraic groups}
\chapter{Group schemes}

Usually we define a variety as an integral separated scheme of finite type over a field.
However, here we define a \emph{variety} as a reduced separated scheme of finite type over a field to allow its reducibility.
If a group scheme is a variety over a field, then we call it an \emph{algebraic group}.


\[\text{Reductive group schemes}
\subset\text{Affine group schemes}
\supset\text{Linear group schemes}\]

\[\text{Reductive group varieties}
\subset\text{Affine algebraic groups}
=\text{Linear algebraic groups}\]
\[\text{Projective algebraic groups}=\text{Abelian varieties}\]





\chapter{Linear algebraic groups}

\section{Affine group schemes}

\section{Reductive groups}





\chapter{Abelian varieties}

\section{Projective}


\part{Hopf algebras}
\chapter{}
\section{}

The category of affine group schemes is the opposite of the category of commutative Hopf algebras.

\begin{prb}[Hopf algebras]
Over the complex field, recall that the category of vector spaces is a symmetric monoidal category with the swap map $\sigma_A:A\otimes A\to A\otimes A$ for each vector space $A$.
A unital algebra can be internally defined as a vector space $A$ together with linear maps $\mu:A\otimes A\to A$ and $\eta:\C\to A$ such that we have the following commutative diagrams:
\[\begin{tikzcd}
A\otimes A\otimes A \rar{\mu\otimes\id}\dar[swap]{\id\otimes\mu} & A\otimes A \dar{\mu} \\
A\otimes A\rar{\mu} & A
\end{tikzcd}
\qquad
\begin{tikzcd}
A \rar{\eta\otimes\id}\dar[swap]{\id\otimes\eta}\ar{dr}{\id} & A\otimes A \dar{\mu} \\
A\otimes A \rar[swap]{\mu} & A
\end{tikzcd}\]
A \emph{counital coalgebra} is a vector space $A$ together with linear maps $\delta:A\to A\otimes A$ and $\e:A\to\C$ such that we have following commutative diagrams:
\[\begin{tikzcd}
A \rar{\delta}\dar[swap]{\delta} & A\otimes A \dar{\delta\otimes\id} \\
A\otimes A\rar{\id\otimes\delta} & A\otimes A\otimes A
\end{tikzcd}
\qquad
\begin{tikzcd}
A \rar{\delta}\dar[swap]{\delta}\ar{dr}{\id} & A\otimes A \dar{\e\otimes\id} \\
A\otimes A \rar[swap]{\id\otimes\e} & A
\end{tikzcd}\]
The linear maps $\mu$, $\eta$, $\delta$, and $\e$ are called the multiplication, unit, comultiplication, and counit.

A \emph{biunital bialgebra}, or just simply a \emph{bialgebra}, is a vector space $A$ which is simultaneously a unital algebra and a counital algebra, satisfying the compatibility condition as the following four commutative diagrams:
\[\begin{tikzcd}[sep=small]
A\otimes A \rar{\mu}\dar[swap]{\delta\otimes\delta} & A \rar{\delta} & A\otimes A\\
A\otimes A\otimes A\otimes A\ar{rr}{1\otimes\sigma_A\otimes1}&&A\otimes A\otimes A\otimes A\uar[swap]{\mu\otimes\mu}
\end{tikzcd}
\quad
\begin{tikzcd}[row sep=small,column sep=tiny]
A\otimes A \ar{rr}{\e\otimes\e}\ar[swap]{dr}{\mu} && \C\\
&A\ar[swap]{ur}{\e}&
\end{tikzcd}
\quad
\begin{tikzcd}[row sep=small,column sep=tiny]
\C \ar{rr}{\eta\otimes\eta}\ar[swap]{dr}{\delta} && A\otimes A\\
&A\ar[swap]{ur}{\eta}&
\end{tikzcd}
\quad
\begin{tikzcd}[row sep=small,column sep=tiny]
\C \ar{rr}{\id}\ar[swap]{dr}{\eta} &&\C\\
&A\ar[swap]{ur}{\e}&
\end{tikzcd}\]
This compatibility condition is equivalent to that the comultiplication and the counit are algebra homomorphisms, or that the multiplication and the unit are coalgebra homomorphisms.
A \emph{Hopf algebra} is a bialgebra $A$ equipped with an invertible linear map $\kappa:A\to A$, called the \emph{antipode}, satisfying the following hexagonal commutative diagram:
\[\begin{tikzcd}[row sep=small,column sep=tiny]
&A\otimes A\ar{rr}{\kappa\otimes\id}&&A\otimes A\ar{dr}{\delta}& \\
A\ar{rr}{\e}\ar{ur}{\mu}\ar[swap]{dr}{\mu}&&\C\ar{rr}{\eta}&&A \\
&A\otimes A\ar{rr}{\id\otimes\kappa}&&A\otimes A\ar[swap]{ur}{\delta}&
\end{tikzcd}\]
A morphism between Hopf algebras is a linear map preserving the five structure maps $\mu$, $\eta$, $\delta$, $\e$, $\kappa$.

\end{prb}
\chapter{Quantum groups}



\end{document}