\documentclass{../exp}
\usepackage{../../ikany}

\title{Binary Quadratic Forms}

\begin{document}
\maketitle

\section{Equivalence}


\begin{defn}
Two forms are called \emph{equivalent} if they are in a same oribit with respect to $\GL_2(\Z)$-action.
\end{defn}

\begin{defn}
Two forms are called \emph{properly equivalent} if they are in a same oribit with respect to $\SL_2(\Z)$-action.
\end{defn}

For representation problems, $\GL_2(\Z)$-action is important.
For the correspondence with the theory of qudratic fields, $\SL_2(\Z)$ is rather important.
From now, all equivalence relations are by $\SL_2(\Z)$.

\begin{ex}
Two forms $(a,b,c)$ and $(a,-b,c)$ are equivalent but not properly equivalent in general.
\end{ex}
\begin{lem}
For a form $(a,b,c)$ and an integer $n$, we have
\begin{cond}
\item $(a,b,c)\sim(a,\ 2an+b,\ an^2+bn+c)$
\item $(a,b,c)\sim(cn^2+bn+a,\ 2cn+b,\ c)$
\item $(a,b,c)\sim(c,-b,a)$
\end{cond}
\end{lem}

\section{Definite forms}

\begin{prop}
The $\SL_2(\Z)$-action on the definite forms is not faithful, i.e. the kernel is given by a nontrivial group $\{\pm I\}$.
\end{prop}
\begin{prop}
The $\PSL_2(\Z)$-action on the definite forms is faithful.
\end{prop}
The faithfulness is not important though, so we choose $\Gamma=\SL_2(\Z)$ as the modular group instead of $\PSL_2(\Z)$.



\subsection{Positive definite forms}
\begin{prop}
The set of positive definite forms admits the $\SL_2(\Z)$-action.
\end{prop}
\begin{prop}
The $\SL_2(\Z)$-actions on positive definite forms and negative definite forms are isomorphic.
\end{prop}

\begin{defn}
A positive definite form $(a,b,c)$ is \emph{reduced} if it satisfies
\begin{cond}
\item $|b|\le a\le c$,
\item if $|b|=a$ or $a=c$, then $b\ge0$.
\end{cond}
\end{defn}
The term ``reduced'' means that it is considered as the unique representative of each orbit, under the action of $\SL_2(\Z)$.



\section{Indefinite forms}


\section{Class group}
% SL2(Z)는
% - form을 앞뒤로 때린다
% - root를 뫼비우스로 때린다

\end{document}