\documentclass{../exp}
\usepackage{../../ikany}

\title{Finite Group Theory}

\newcommand{\edv}{\mathrel\Vert}

\begin{document}
\maketitle
\tableofcontents

\iffalse
presentation
	quotient of a free group
	homomorphism 잡기
		free group을 정의역으로 먼저 잡고 well-defined 보여서 quotient로 내리기
	element들을 두 제너레이터로 표현하기
isomorphism 보이기
	isomorphism theorem
	order argument
subgroup criterion: 항등원, 역원, 닫힘 순으로 증명
centralizer, center, normalizer
	각 그룹의 계산 -> 기본적으로 노가다, 마지막에 라그랑지 확인
	센트럴라이저의 대칭성
	N(H)/C(H) 정리, G/Z(G)=Inn(G)
stabilizer


----------
#
아벨군: 순환군, n-abelian 등 여러 조건, 기본정리
대칭군: 생성원, 트랜지티브, 교대군과 부호
콕세터: 이면군, 프레젠테이션
선형군: 

#
액션, 실로우: existence, congruence condition
부분군격자: 1. 특정위수 부분군의 존재성, 2. 각 부분군의 컨쥬게이트 개수
	노멀라이저의 크기를 잰다는 것 = 실로우군의 conjugate 개수 세는 것
	- 카운팅: 너무 많은 conjugate 배제하는 법
	- 인덱스: 푸앵카레 정리, least prime ind
	- 노말라이즈되는 부분군 잡아 노말라이저 띄우기
	케이스 나누기에 매우 좋은 조건을 제공
		노말 실로우 -> 바로 반직접곱
http://oeis.org/wiki/Number_of_groups_of_order_n

#
군 확장
컴포지션 시리즈의 이해
반직접: / 계산->아벨군의 자기동형군
중심적: 군코호몰로지 / 계산->보편계수정리

#
단순군: 단순군 아니기 테크닉, 단순군 보이기 테크닉, 교대군과 리타입 선형군

#
p군: 비자명센터, 개수 겁나많음
닐포턴트: 피팅, 프라티니
솔버블?
센트럴 시리즈?


\fi


\section{Special groups}

\subsection{Cyclic groups}
\begin{enumerate}
\item A subgroup is also cyclic.
\item The number of subgroups $=$ the number of divisors of its order.
\item Endomorphism ring is given by $\Z/n\Z$.
\item Automorphism group is given by $(\Z/n\Z)^\x$.
\item The number elements of order $d$ is $\phi(d)$.
\item
\end{enumerate}

\subsection{Abelian groups}
Fundamental theorem of finitely generated abelian groups

\begin{thm}
Let $G$ be a finite group.
If $G/Z(G)$ is cylic, then $G$ is abelian.
\end{thm}
\begin{thm}
Let $G$ be a finite group.
If $x\mapsto x^3$ is a surjective endomorhpism, then $G$ is abelian.
\end{thm}

\subsection{Symmetric groups}
\subsection{Coxeter groups}
\subsection{Linear groups}





\section{Classification of small groups}

\subsection{Sylow theorem}
\begin{defn}[Sylow $p$-subgroup]
Let $G$ be a finite group of order $n=p^am$ for a prime $p\nmid m$.
A \emph{Sylow $p$-subgroup} is a subgroup of order $p^a$.
We are going to denote the set of Sylow $p$-subgroups by $\Syl_p(G)$ and the number of Sylow $p$-subgroups by $n_p(G)$.
\end{defn}

\begin{thm}[Sylow]
Let $G$ be a finite group of order $n=p^am$ for a prime $p\nmid m$.
Then,
\[p\mid n_p-1,\qquad n_p\mid m\]
for some $k\in\N$.
\end{thm}
\begin{pf}
\Step{1}[A Sylow $p$-subgroup exists]
We apply mathematical induction on orders.
The base step is trivial.
Suppose every finite group of order less than $n$ possesses a Sylow $p$-subgroup.

By applying the orbit-stabilizer theorem for the action $G\acts G$ by conjugation, build the class equation
\[n=|Z(G)|+\sum_i|G:C_G(g_i)|.\]
There are two cases: $p\mid|Z(G)|$ or $p\nmid|Z(G)|$.

\Case{1}[$p\mid|Z(G)|$]
The group $G$ has a normal subgroup of order $p$ by applying Cauchy's theorem for abelian groups on the center.
Then, the inverse image of a Sylow $p$-subgroup of the quotient group is also a Sylow $p$-subgroup of $G$.

\Case{2}[$p\nmid|Z(G)|$]
Since $p\mid n$, we have $p\nmid|G:C_G(g)|$ for some $g\in G$.
Then, a Sylow $p$-subgroup of the centralizer is also a Sylow $p$-subgroup of $G$.

Therefore, we are done for Step 1.

\bigskip
\Step{2}[A Sylow $p$-subgroups get action by conjugation]
Let $P$ be a Sylow $p$-subgroup of $G$.
We construct class equations via the orbit-stabilizer theorm for various actions to extract information on $n_p$.
Note that stabilizers in any setwise conjugation action is exactly normalizers.
\begin{cond}
\item The action $P\acts\Syl_p(G)$ gives
\[n_p=1+\sum_i|P:N_P(P_i)|\]
since $P=N_P(P_i)\le N_G(P_i)$ and $P_i\normal N_G(P_i)$ imply and $P=P_i$.
(Pass $P$ though $\pi:N_G(P_i)\to N_G(P_i)/P_i$.)
\item Suppose the action $G\acts\Syl_p(G)$ is not transitive.
Take another Sylow $p$-subgroup $P'$ is not conjugate with $P$ in $G$.
The two actions $P\acts\Orb_G(P)$ and $P'\acts\Orb_G(P)$ gives
\[|\Orb_G(P)|=1+\sum_i|P:N_P(P_i)|=\sum_i|P':N_{P'}(P_i)|.\]
It deduces $|\Orb_G(P)|\equiv0,1\pmod{p}$ simultaneously, which leas a contradiction.
\item The action $G\acts\Syl_p(G)$ gives
\[n_p=|G:N_G(P_i)|\]
for all $P_i\in\Syl_p(G)$ because the action is transitive.
\end{cond}
Then, (1) proves $p\mid n_p-1$, and (3) proves $n_p\mid m$.
\end{pf}

\begin{cor}
Let $G$ be a finite group.
Then,
\begin{cond}
\item every pair of two Sylow $p$-subgroup is conjugate.
\item every $p$-subgroup is contained in a Sylow $p$-subgroup.
\item a Sylow $p$-subgroup is normal if and only if $n_p=1$.
\end{cond}
\end{cor}

\begin{thm}
Alternative proof for existence of $p$-groups.
\end{thm}
\begin{pf}
Let $|G|=p^{a+b}m$.
Let $\cP_{p^a}$ be the set of all $p^a$-sets in $G$.
Give $G\acts\cP_{p^a}$ by left multiplication.
Since $v_p(|\cP_{p^a}|)=v_p({p^a(p^bm)\choose p^a})=b$, there is an orbit $\cO$ such that $v_p(|\cO|)\le b$.
We have transitive action $G\acts\cO$ and the stabilizer $H$ satisfies $p^a\mid|G|/|\cO|=|H|$.
Since $H\acts\cO$ trivially, $H\acts A$ for $A\in\cO\subset\cP_{p^a}$.
It is only possible when $H\subset A$, hence $|H|=p^a$.
\end{pf}

Investigation of a group of a given order is divided into two main parts: the existence of a subgroup of particular orders and the measurement of the size of conjugate subgroups.

In order to show the existence of subgroups of paricular orders:
\begin{cond}
\item $p$-groups always exist,
\item extension theory, (what can subgroups of subgroups do?)
\item normalizers,
\item Poincare theorem: kernel of permutation representation
\end{cond}

In order to find the size of conjugacy classes:
\begin{cond}
\item measure the order of normalizers, (find some groups normalize a subgroup)
\item count elements,
\end{cond}


\subsection{Semidirect product}

\begin{defn}[External semidirect product]
Suppose we have three data: groups $(N,+),(H,\cdot)$ and a group homomorphism $\f:H\to\Aut(N)$.
The \emph{semidirect product} $N\rtimes_\f H$ is a group defined on the set $N\x H$ by
\[(n,h)(n',h')=(n+\f(h)n',hh').\]
\end{defn}
The motivation of the group structure of semidirect product is shown in the following theorem.
\begin{thm}[Internal semidirect product]
Let $N,H$ be subgroups of $G$ such that
\[N\normal G,\quad N\cap H=1,\quad NH=G.\]
Then, $G\cong N\rtimes_\f H$, where the action $\f$ is given by conjugation
\[\f(h):N\to N:n\mapsto hnh^{-1}.\]
\end{thm}




\subsection{Groups of order less than 64}


\subsubsection{Two primes}
\begin{ex}[$|G|=p^2$]
\end{ex}

\begin{ex}[$|G|=pq$]
\end{ex}




\subsubsection{Three primes}
\begin{lem}
Let $N,H$ be groups.
Let $\f_1,\f_2:H\to\Aut(N)$ be group actions.
If there are $\nu\in\Aut(N)$ and $\eta\in\Aut(H)$ such that a diagram
\begin{cd}
H \ar{r}{\f_1}\ar{d}{\eta} & \Aut(N) \ar{d}{\nu\,\cdot\,\nu^{-1}}\\
H \ar{r}{\f_2} & \Aut(N)
\end{cd}
commutes, then a map
\[N\rtimes_\f H\to N\rtimes_{\f'}H:(n,h)\mapsto(\nu(n),\eta(h))\]
is an isomorphism.
\end{lem}
\begin{lem}
Let $Z,G$ be finite groups.
If $Z$ is cyclic, then $\f,\f':Z\to\Aut(G)$ induces the isomorphic semidirect product iff their images are conjugate.
\end{lem}

\begin{ex}[Conjugacy classes of $\GL_2(\F_p)$]
$ $
\begin{cond}
\item $\mat{a&0\\0&b}$: ${q-1\choose 2}=\frac{(q-1)(q-2)}2$ classes of size $\frac{|G|}{(q-1)^2}=q(q+1)$.
\item $\mat{a&0\\0&a}$: $q-1$ classes of size $1$.
\item $\mat{a&1\\0&a}$: $q-1$ classes of size $\frac{|G|}{q(q-1)}=q^2-1$.
\item otherwise, the eigenvalues are in $\F_{q^2}$. So, $\frac{|\F_{q^2}|-|\F_q|}2=\frac{q(q-1)}2$ classes of size $\frac{q(q-1)}2$.
\end{cond}
\end{ex}



\begin{ex}[$|G|=p^3$]
\end{ex}


\begin{ex}[$|G|=p^2q$]
We divide three cases: $p+2\le q$, $p>q$, and $p^2q=12$.
In each case we have a normal Sylow $p$-subgroup, groups are classified by semidirect products of a Sylow $p$-subgroup and a Sylow $q$-subgroup.

\bigskip
\Case{1}[$p+2\le q$]
Sylow's theorem implies $n_q=1$.
\begin{cond}
\item
Let $G\cong Z_q\rtimes Z_{p^2}$, and consider actions of the form
\[\f:Z_{p^2}\to\Aut(Z_q)\cong Z_{q-1}.\]
There are
\[\min\{v_p(q-1),2\}=\begin{cases}2&,p^2\mid q-1,\\1&,p\edv q-1,\\0&,\text{otherwise}\end{cases}\]
nonabelian groups.
\item
Let $G\cong Z_q\rtimes(Z_p\x Z_p)$, and consider actions of the form
\[\f:Z_p\x Z_p\to\Aut(Z_q)\cong Z_{q-1}.\]
There are
\[\min\{v_p(q-1),1\}=\begin{cases}1&,p\mid q-1,\\0&,\text{otherwise}\end{cases}\]
nonabelian groups.
\end{cond}

\bigskip
\Case{2}[$p>q$]
Sylow's theorem implies $n_p=1$.
\begin{cond}
\item
Let $G\cong Z_{p^2}\rtimes Z_q$, and consider actions of the form
\[\f:Z_q\to\Aut(Z_{p^2})\cong Z_{p(p-1)}.\]
There are
\[\min\{v_q(p-1),1\}=\begin{cases}1&,q\mid p-1,\\0&,\text{otherwise}\end{cases}\]
nonabelian groups.
\item
Let $G\cong(Z_p\x Z_p)\rtimes Z_q$, and consider actions of the form
\[\f:Z_q\to\Aut(Z_p\x Z_p)\cong\GL_2(\F_p).\]
Note that $|\GL_2(\F_p)|=(p^2-1)(p^2-p)=(p-1)^2p(p+1)$.
The conjugacy class of subgroups are classified by the Jordan normal forms.

If $q=2$, then the possible conjugacy classes are represented by
\[\mat{1&0\\0&-1},\ \mat{-1&0\\0&-1}\]
There are
\[\begin{cases}2&,q=2\\1&,2\nmid q\mid p+1,\\\frac{q+3}2&,2\nmid q\mid p-1,\\0&,\text{otherwise}\end{cases}\]
nonabelian groups.
Since the number of one-dimensional linear subspaces is $q+1$ and the number of symmetric subspaces is 2 in $\F_q^2$, we have $\frac{(q+1)-2}2+2=\frac{q+3}2$ conjugacy classes of subgroups of order $q$ in $\GL_2(\F_p)$.
\end{cond}

\Case{3}[$p=2$, $q=3$]

\end{ex}




\begin{ex}[$|G|=pqr$]
\end{ex}



\begin{figure}[h!]
\begin{tabular}{c|c|ccccccc}
\hline
$|G|=p^2q\ (p<q)$&12&20&28&44&45&52&63\\
\hline
$\#$ of groups&5&5&4&4&2&5&4\\
\hline
\end{tabular}
\vspace{10pt}

\begin{tabular}{c|cccc}
\hline
$|G|=p^2q\ (p>q)$&18&50&(75)\\
\hline
$\#$ of groups&5&5&3\\
\hline
\end{tabular}
\hspace{10pt}
\begin{tabular}{c|cc}
\hline
$|G|=pqr$&30&42\\
\hline
$\#$ of groups&4&6\\
\hline
\end{tabular}
\end{figure}




\subsubsection{More than four primes}
Under 64, there are some exceptions whose orders are formed by product of more than four primes.
\begin{figure}[h!]
\begin{tabular}{c|c|cccc|c|c}
\hline
$|G|=\prod^4p$&16&24&40&54&56&36&60\\
\hline
$\#$ of groups&14&15&14&15&13&14&13\\
\hline
\end{tabular}
\vspace{10pt}

\begin{tabular}{c|c|c||c}
\hline
$|G|=\prod^{5\text{ or }6}p$&32&48&64\\
\hline
$\#$ of groups&51&52&267\\
\hline
\end{tabular}
\end{figure}






\section{Extension theory}

\begin{prop}
Let $N$ and $H$ be groups.
Then, the following objects have one-to-one correspondences among each other.
\begin{cond}
\item isomorphic types of groups $G$ such that a sequence \begin{es}0\>N\>G\>H\>0\end{es} is exact and right split,
\item isomorphic types of groups $G$ such that $N\normal G\ge H$ with $G=NH$ and $N\cap H=1$,
\item group actions $H\acts N$ preserving the group structure of $N$.
\end{cond}
\end{prop}
\begin{defn}
The group $G$ in the previous proposition is called the \emph{semidirect product} of $N$ and $H$.
\end{defn}


\begin{es}
0\>F\>E\>G\>0.
\end{es}
Four data $G,F,\f:G\to\Aut(F),c:G\x G\to F$ completely determine the extension $E$.

Suppose we have an extension $F\to E\to G$.
There is a \emph{set-theoretic section} $s:G\to E$.
The number of $s$ is $|G||F|$.

Definition of \emph{action} $\f$:
For two sections $s$ and $s'$, $s(g)$ and $s'(g)$ acts on $F$ equivalently.
Thus, we can define a \emph{group homomorphism} $\f:G\to\Aut(F)$ independently on sections.

Definition of \emph{2-cocycle} $c$:
It is a \emph{set-theoretic function} $c:G\x G\to F$ defined by $c(g,g')=s(g)s(g')s(gg')^{-1}$ for a section $s$.
Actually, $c$ depends on the section $s$, and $c$ measures how much $s$ fails to be a group homomorphism.
It requires the cocycle condition for the associativity of group operation, i.e.
\[c(g,h)c(gh,k)=\f_g(c(h,k))c(g,hk)\]
should be satisfied.
Conversely, a map $G\x G\to F$ satisfying the condition the cocycle condition gives a associative group operation on $G$.

If $F$ is abelian, then the set of cocycles forms an abelian group, and is denoted by $Z^2(G,F)$.
The boundaries are also defined in abelian $F$ case.


\begin{cond}
\item $\f$, $c$ is trivial $\iff$ direct product,
\item $c$ is trivial $\iff$ $s$ is a homomorphism $\iff$ semidirect product,
\item $\f$ is trivial $\iff$ central extension.
\end{cond}

Group cohomology is defined for a group $G$ and $G$-module $A$ (three data: $G,A,\f$.
What is important is that the cohomology depends on the action of $G$ on $A$.

If $\f$ is trivial so that $A$ is just an abelian group, then the universal coefficient theorem can be applied.
\end{document}
