\documentclass[a4paper]{article}
\usepackage{../../ikany}
\usepackage[margin=3cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[bitstream-charter,cal]{mathdesign}
\linespread{1.15}


\begin{document}
\tableofcontents



\section{Elliptic curves}
\subsection{Reduction of Weierstrass equations}
In this subsection, we want to investigate the important constants of elliptic curves such as $c_4$, $c_6$, $\Delta$, $j$ by calculating equations with hands.

\textbf{Step 1.}
The Riemann-Roch theorem proves that every curve of genus 1 with a specified base point can be described by the first kind of Weierstrass equation.
Explicitly, the first form of Weierstrass equation is
\[y^2+a_1xy+a_3y=x^3+a_2x^2+a_4x+a_6.\tag{1}\]

\textbf{Step 2.}
\emph{Elimination of $xy$ and $y$}.
Factorize the left hand side
\begin{align*}
y\,(y+a_1x+a_3)=x^3+a_2x^2+a_4x+a_6.
\end{align*}
By translation
\begin{align*}
\boxed{x\mapsto x,\qquad y\mapsto y-\tfrac12(a_1x+a_3)}
\end{align*}
we have
\begin{align*}
y^2-(\tfrac12(a_1x+a_3))^2&=x^3+a_2x^2+a_4x+a_6,\\
y^2&=x^3+(\tfrac14a_1^2+a_2)x^2+(\tfrac12a_1a_3+a_4)x+(\tfrac14a_3^2+a_6),\\
y^2&=x^3+\frac14(a_1^2+4a_2)x^2+\frac12(a_1a_2+2a_4)x+\frac14(a_3^2+4a_6).
\end{align*}
Introduce new coefficients $b$ to write it as
\begin{align*}
y^2=x^3+\frac14b_2x^2+\frac12b_4x+\frac14b_6.
\end{align*}
By scaling
\begin{align*}
\boxed{x\mapsto x,\qquad y\mapsto \tfrac12y}
\end{align*}
we get
\[y^2=4x^3+b_2x^2+2b_4x+b_6.\tag{2}\]

\textbf{Step 3.}
\emph{Elimination of $x^2$}.
By translation
\begin{align*}
\boxed{x\mapsto x-\tfrac1{12}b_2}
\end{align*}
we have
\begin{align*}
y^2=4\left(x^3-3\cdot\frac1{12}b_2x^2+3\cdot\frac1{12^2}b_2^2x-\frac1{12^3}b_2^3\right)&\\
+b_2\left(x^2-2\cdot\frac1{12}b_2x+\frac1{12^2}b_2^2\right)&\\
+2b_4\left(x-\frac1{12}b_2\right)&\\
+b_6,&
\end{align*}
so
\begin{align*}
y^2&=4x^3+\left(4\cdot3\cdot\frac1{12^2}b_2^2-2\cdot\frac1{12}b_2^2+2b_4\right)x+\left(-4\cdot\frac1{12^3}b_2^3+\frac1{12^2}b_2^3-2\cdot\frac1{12}b_2b_4+b_6\right)\\
&=4x^3+\frac1{12}\left(-b_2^2+24b_4\right)x+\frac1{216}\left(b_2^3-36b_2b_4+216b_6\right).
\end{align*}
Write it as
\begin{align*}
y^2=4x^3-\frac1{12}c_4x-\frac1{216}c_6.
\end{align*}
We want to match the coefficients of $y^2$ and $x^3$ but also want the coefficients of $c_4x$ and $c_6$ to be integers.
Iterative scaling implies
\begin{align*}
x\mapsto\tfrac16x:&\qquad 216y^2=4x^3-3c_4x-c_6\\
y\mapsto\tfrac1{36}y:&\qquad y^2=24x^3-18c_4x-6c_6\\
x\mapsto\tfrac16x:&\qquad 9y^2=x^3-27c_4x-54c_6\\
y\mapsto\tfrac13y:&\qquad y^2=x^3-27c_4x-54c_6.
\end{align*}
Thus, we get the famous third form of Weierstrass equation:
\[y^2=x^3-27c_4x-54c_6.\tag{3}\]



\begin{thm}
Let
\[E:y^2=x^3-Ax-B.\]
TFAE:
\begin{parts}
\item A point $(x,y)$ is a singular point of $E$.
\item $y=0$ and $x$ is a double root of $x^3-Ax-B$.
\item $\Delta=0$.
\end{parts}
\end{thm}
\begin{pf}
(1)$\Rightarrow$(2)
$\pd_yf=0$ implies $y=0$. $f=\pd_xf=0$ implies $x$ is a double root of $x^3-Ax-B$.
$A$ determines whether $x$ is either cusp of node.
\end{pf}












\section{Algebraic integer}
\subsection{Quadratic integer}
\begin{thm}
Every quadratic field is of the form $\Q(\sqrt d)$ for a square-free $d$.
\end{thm}
\begin{thm}
Let $d$ be a square-free.
\[\cO_{\Q(\sqrt d)}=\begin{cases}\Z[\sqrt d]&,d\equiv2,3\pmod4\\\Z[\tfrac{1+\sqrt d}2]&,d\equiv1\pmod4\end{cases}\]
\[\Delta_{\Q(\sqrt d)}=\begin{cases}4d&,d\equiv2,3\pmod4\\ d&,d\equiv1\pmod4\end{cases}\]
\end{thm}
\begin{ex}
\[\Delta_{\Q(i)}=-4,\quad\Delta_{\Q(\sqrt2)}=8,\quad\Delta_{\Q(\gamma)}=5,\quad\Delta_{\Q(\omega)}=-3\]
where $\gamma:=\frac{1+\sqrt5}2$ and $\omega=\zeta_3$.
\end{ex}
\begin{thm}
Let $\theta^3=hk^2$ for $h,k$ square-free's.
\[\cO_{\Q(\theta)}=\begin{cases}\Z+\theta\Z+\frac{\theta^2}k\Z&,m\not\equiv\pm1\pmod9\\
\Z+\theta\Z+\frac{\theta^2\pm\theta k+k^2}{3k}\Z&,m\equiv\pm1\pmod9\end{cases}\]
\end{thm}
\begin{cor}
If $\theta^3$ is a square free integer, then
\[\cO_{\Q(\theta)}=\Z[\theta].\]
\end{cor}

\subsection{Integral basis}
\begin{thm}
Let $\alpha\in K$.
$Tr_K(\alpha)\in\Z$ if $\alpha\in\cO_K$.
$N_K(\alpha)\in\Z$ if and only if $\alpha\in\cO_K$.
\end{thm}
\begin{thm}
Let $\{\omega_1,\cdots,\omega_n\}$ be a basis of $K$ over $\Q$.
If $\Delta(\omega_1,\cdots,\omega_n)$ is square-free, then $\{\omega_1,\cdots,\omega_n\}$ is an integral basis.
\end{thm}
\begin{thm}
Let $\{\omega_1,\cdots,\omega_n\}$ be a basis of $K$ over $\Q$ consisting of algebraic integers.
If $p^2\mid\Delta$ and it is not an integral basis, then there is a nonzero algebraic integer of the form
\[\frac1p\sum_{i=1}^n\lambda_i\omega_i.\]
\end{thm}

\subsection{Fractional ideals}
\begin{thm}
Every fractional ideal of $K$ is a free $\Z$-module with rank $[K:\Q]$.
\end{thm}
\begin{pf}
This theorem holds because $K/\Q$ is separable and $\Z$ is a PID.

\end{pf}


\clearpage
\subsection{Frobenius element}
\begin{defn}
Let $L/K$ be abelian.
Let $\fp$ be a prime in $\cO_K$ and $\fq$ be a prime in $\cO_L$ over $\fp$.
The \emph{decomposition group} $D_{\fq|\fp}$ is a subgroup of $\Gal(L/K)$ whose element fixes the prime $\fq$.
Since $L/K$ is Galois, the followings do not depend on the choice of $\fq$ over $\fp$.

By definition, $D_{\fq|\fp}$ acts on the set $\cO_L/\fq$ and fixes $\cO_K$.
\end{defn}
\begin{lem}
The following sequence of abelian groups is exact:
\begin{es} 0 \> I_{\fq|\fp} \> D_{\fq|\fp} \> \Gal(k(\fq)/k(\fp)) \> 0, \end{es}
where $k(\fq):=\cO_L/\fq$ and $k(\fp):=\cO_K/\fp$ are residue fields.
\end{lem}
\begin{pf}
We first show 
\end{pf}
The Frobenius element is defined as an element of $D_{\fq|\fp}/I_{\fq|\fp}\cong\Gal(k(\fq)/k(\fp))$, which is a cyclic group.
\begin{defn}
The Frobenius element is defined by $\phi_{\fq|\fp}\in\Gal(L/K)$ such that $\phi_{\fq|\fp}(\fq)=\fq$ and
\[\phi_{\fq|\fp}(x)\equiv x^{|\cO_K/\fp|}\pmod{\fq}\quad\text{for}\ x\in\cO_L.\]
It gives a generator of the cyclic group $D_{\fq|\fp}/I_{\fq|\fp}$.
\end{defn}
\begin{rmk}
Fermat's little theorem states $\phi_{\fq|\fp}=\id_{\cO_K/\fp}$, i.e.
\[\phi_{\fP|\fp}(x)\equiv x\pmod{\fp}\quad\text{for}\ x\in\cO_K,\]
which means $\phi_{\fP|\fp}$ fixes the field $\cO_K/\fp$ so that $\phi_{\fP|\fp}\in\Gal(k(\fP)/k(\fp))$.
\end{rmk}


\subsection{Quadratic Dirichlet character}
Let $D$ be a quadratic discriminant.
For $\zeta_D=e^{\frac{2\pi i}D}$, it is known that the cyclotomic field $\Q(\zeta_D)$ is the smallest cyclotomic extension of the quadratic field $\Q(\sqrt D)$.
Let $K=\Q(\sqrt{D})$ and $L=\Q(\zeta_D)$.

\begin{cd}[column sep = 0pt]
\sigma_p \dar[|->]{\cdot|_K} &\in& D_{\fq|p} &\le& \Gal(L/\Q) \dar[->>]{\cdot|_K} &\cong& (\Z/|D|\Z)^\times \dar[->>]{\chi_K=\left(\frac D\cdot\right)} & \\
\sigma_p|_K&\in& D_{\fp|p} &\le& \Gal(K/\Q) &\cong& \<\pm1\>.
\end{cd}

For $p\nmid D$ so that $p$ is unramified, let $\sigma_p:=(\zeta_D\mapsto\zeta_D^p)\in\Gal(L/\Q)$.
Then, what is $\sigma_p|_K$ in $\Gal(K/\Q)$?
In other words, which is true: $\sigma_p(\sqrt D)=\pm\sqrt D$?

Notice that $\sigma$ satisfies the condition to be the Frobenius element: $\sigma_pI_{\fq|p}=\phi_{\fq|p}$.
Therefore, $\phi_{\fp|p}=\sigma_p|_K$ is also a Frobenius element.
There are only two cases:
\begin{parts}
\item If $f=|D(\fp/p)|=1$, then $\sigma_p|_K$ is the identity, so $\chi_K(p)=1$
\item If $f=|D(\fp/p)|=2$, then $\sigma_p|_K$ is not trivial, so $\chi_K(p)=-1$
\end{parts}








\section{Diophantine equations}

\subsection{Quadratic equation on a plane}
Ellipse is reduced by finitely many computations.


Especially for hyperbola, here is a strategy to use infinite descent.
\begin{parts}
\item Let midpoint to be origin.
\item Find the subgroup of $\SL_2(\Z)$ preserving the image of hyperbola(which would be isomorphic to $\Z$).
\item Find an impossible region.
\item Assume a solution and reduce it to the either impossible region or the ground solution.
\end{parts}
\begin{ex}[Pell's equation]
Consider\[x^2-2y^2=1.\]
A generator of hyperbola generating group is $g=\begin{pmatrix}3&4\\2&3\end{pmatrix}$.
It has a ground solution $(1,0)$ and impossible region $1<x<3$.
If $(a,b)$ is a solution with $a>0$, then we can find $n$ such that $g^n(a,b)$ is in the region $[1,3)$.
The possible case is $g^n(a,b)=(1,0)$.
\end{ex}
\begin{ex}[IMO 1988, the last problem]
Consider a family of equations\[x^2+y^2-kxy-k=0.\]
By the vieta jumping, a generator is $g:(a,b)\mapsto(b,kb-a)$.
It has an impossible region $xy<0$ : $x^2+y^2-kxy-k\ge x^2+y^2>0$.
If $(a,b)$ is a solution with $a>b$, then we can find $n$ such that $g^n(a,b)$ is in the region $xy\le0$.
Only possible case is $g^n(a,b)=(\sqrt k,0)$ or $g^n(a,b)=(0,-\sqrt k)$.
In ohter words, the equation has a solution iff $k$ is a perfect square.
\end{ex}

\begin{prb}
Consider a family of diophantine equations:
\[x^2+y^2-kxy-k=0\]
for $k\in\Z$.
\begin{parts}
\item Find the smallest three solutions such that $x>y\ge0$ when $k=4$.
\item Show that if $(x,y)$ is a solution, then $(y,ky-x)$ is also a solution.
\item Show that if it has a solution, then at least one solution satisfies $x>0\ge y$.
\item Show that the equation does not have a solution in the region $xy<0$.
\item Show that the equation has a solution if and only if $k$ is a perfect square.
\item Let $a$ and $b$ be integers. Deduce that if $ab+1$ divides $a^2+b^2$, then \[\frac{a^2+b^2}{ab+1}\]is a perfect square.
\end{parts}
\end{prb}
\begin{sol}
\begin{parts}
\item
Try for $y=0,1,\cdots,8$.
Then we get $(2,0)$, $(8,2)$, and $(30,8)$.
\item
By substitution, we have
\[(y)^2+(ky-x)^2-k(y)(ky-x)-k=y^2+x^2-kxy-k.\]
In other words, $(x,y)\mapsto(y,ky-x)$ is an automorphism of this hyperbola.
The desired statement trivially follows.
\item
Suppose not.
By symmetry, we may assume we have a solution with $x>y>0$.
Take the solution such that $x+y$ is minimal.
Note that we have
\[0\le x^2+y^2=k(xy+1)\impl k\ge0,\]
and
\[2x^2>x^2+y^2=kxy+k\ge kxy\impl 2x>ky.\]
As we have seen, $(y,ky-x)$ is a solution, and $ky-x>0$ by the assumption.
Since $x+y>y+(ky-x)$, we obtain a contradiction for the minimality.
\item
Suppose $x,y\in\Z$ satisfy $xy<0$.
Since $xy\le-1$, \[x^2+y^2-kxy-k\ge x^2+y^2+k-k>0.\]
\item
\end{parts}
\end{sol}
\begin{rmk}
In general, the transformation $(x,y)\mapsto(y,ky-x)$ preserving the image of hyperbola is not easy to find.
A strategy to find it in this problem is called the \emph{Vieta jumping} or \emph{root flipping}.
It gets the name by the following reason:
If $(a,b)$ is a solution with $a>b$, then a quadratic equation \[x^2-kbx+b^2-k=0\] has a root $a$, and the other root is $kb-a$ so that $(b,kb-a)$ is also a solution.
The last problem is from the International Mathematical Olympiad 1988, and the Vieta jumping technique was firstly used to solve it.
\end{rmk}


\clearpage


\subsection{The Mordell equations}
(The reciprocity laws let us learn not only which prime splits, but also which prime factors a given polynomial has.)
\[y^2=x^3+k\]
There are two strategies for the Mordell equations:
\begin{itemize}
\item $x^2-2x+4$ has a prime factor of the form $4k+3$
\item $x^3=N(y-a)$ for some $a$.
\end{itemize}
First case: $k=7,-5,-6,45,6,46,-24,-3,-9,-12$.
\begin{ex} Solve $y^2=x^3+7$. \end{ex}
\begin{pf}
Taking mod 8, $x$ is odd and $y$ is even.
Consider
\[y^2+1=(x+2)(x^2-2x+4).\]
Since
\[x^2-2x+4=(x-1)^2+3,\]
there is a prime $p\equiv3\pmod4$ that divides the right hand side.
Taking mod $p$, we have
\[y^2\equiv-1\pmod p,\]
which is impossible.
Therefore, the equation has no solutions.
\end{pf}
\begin{ex} Solve $y^2=x^3-2$. \end{ex}
\begin{pf}
Taking mod 8, $x$ and $y$ are odd.
Consider a ring of algebraic integers $\Z[\sqrt{-2}]$.
We have
\[N(y-\sqrt{-2})=(y-\sqrt{-2})(y+\sqrt{-2})=x^3.\]
For a common divisor $\delta$ of $y\pm\sqrt{-2}$, we have 
\[N(\delta)\mid N((y-\sqrt{-2})-(y+\sqrt{-2}))=N(2\sqrt{-2})=|(2\sqrt{-2})(-2\sqrt{-2})|=8.\]
On the other hand,
\[N(\delta)\mid x^3 \equiv1\pmod2,\]
so $N(\delta)=1$ and $\delta$ is a unit.
Thus, $y\pm\sqrt{-2}$ are relatively prime.
Since the units in $\Z[\sqrt{-2}]$ are $\pm1$, which are cubes, $y\pm\sqrt{-2}$ are cubics in $\Z[\sqrt{-2}]$.

Let
\[y+\sqrt{-2}=(a+b\sqrt{-2})^3=a(a^2-6b^2)+b(3a^2-2b^2)\sqrt{-2},\]
so that $1=b(3a^2-2b^2)$.
We can conclude $b=\pm1$.
The possible solutions are $(x,y)=(3,\pm5)$, which are in fact solutions.
\end{pf}



\section{The local-global principle}
\subsection{The local fields}
Let $f\in\Z[x]$.
\[\text{\emph{Does $f=0$ have a solution in $\Z$?}}\]
\[\text{\emph{Does $f=0$ have a solution in $\Z/(p^n)$ for all $n$?}}\]
\[\text{\emph{Does $f=0$ have a solution in $\Z_p$?}}\]
In the first place, here is the algebraic definition.
\begin{defn}
Let $p\in\Z$ be a prime.
The ring of the $p$-adic integers $\Z_p$ is defined by the inverse limit:
\begin{es}
\Z_p:={\lim\limits_{\substack{\longleftarrow\\n\in\N}}}\Z/p^n\Z  \>  \cdots  \>  \Z/p^3\Z  \>  \Z/p^2\Z  \>  \Z/p\Z.
\end{es}
\end{defn}
\begin{defn}
$\Q_p=\Frac\Z_p$.
\end{defn}
Secondly, here is the analytic definition.
\begin{defn}
Let $p\in\Z$ be a prime.
Define a absolute value $|\cdot|_p$ on $\Q$ by $|p^ma|_p=\frac1{p^m}$.
The local field $\Q_p$ is defined by the completion of $\Q$ with respect to $|\cdot|_p$.
\end{defn}
\begin{defn}
$\Z_p:=\{x\in\Q_p:|x|_p\le1\}$.
\end{defn}

\begin{ex}
Observe
\begin{align*}
3^{-1}&\equiv2_5\pmod5\\
&\equiv32_5\pmod{5^2}\\
&\equiv132_5\pmod{5^3}\\
&\equiv1313132_5\pmod5^7\cdots.
\end{align*}
Therefore, we can write
\[3^{-1}=\overline{13}2_5=2+3p+p^2+3p^3+p^4+\cdots\]
for $p=5$.
Since there is no negative power of 5, $3^{-1}$ is a $p$-adic integer for $p=5$.
\end{ex}
\begin{ex}

\begin{align*}
7&\equiv1_3^2\pmod3\\
&\equiv111_3^2\pmod{3^3}\\
&\equiv20111_3^2\pmod{3^5}\\
&\equiv120020111_3^2\pmod{3^9}\cdots.
\end{align*}
Therefore, we can write
\[\sqrt7=\cdots120020111_3=1+p+p^2+2p^4+2p^7+p^8+\cdots\]
for $p=3$.
Since there is no negative power of 3, $\sqrt7$ is a $p$-adic integer for $p=3$.
\end{ex}


There are some pathological and interesting phenomena in local fields.
Actually note that the values of $|\cdot|_p$ are totally disconnected.
\begin{thm}
The absolute value $|\cdot|_p$ is nonarchimedean: it satisfies $|x+y|_p\le\max\{|x|_p,|y|_p\}$.
\end{thm}
\begin{pf}
Trivial.
\end{pf}

\begin{thm}
Every triangle in $\Q_p$ is isosceles.
\end{thm}

\begin{thm}
$\Z_p$ is a discrete valuation ring: it is local PID.
\end{thm}
\begin{pf}
asdf
\end{pf}

\begin{thm}
$\Z_p$ is open and compact.
Hence $\Q_p$ is locally compact Hausdorff.
\end{thm}
\begin{pf}
$\Z_p$ is open clearly.
Let us show limit point compactness.
Let $A\subset\Z_p$ be infinite.
Since $\Z_p$ is a finite union of cosets $p\Z_p$, there is $\alpha_0$ such that $A\cap(\alpha_0+p\Z_p)$ is infinite.
Inductively, since
\[\alpha_n+p^{n+1}\Z_p=\bigcup_{1\le x<p}(\alpha_n+xp^{n+1}+p^{n+2}\Z_p),\]
we can choose $\alpha_{n+1}$ such that $\alpha_n\equiv\alpha_{n+1}\pmod{p^{n+1}}$ and $A\cap(\alpha_{n+1}+p^{n+2}\Z_p)$ is infinite.
The sequence $\{\alpha_n\}$ is Cauchy, and the limit is clearly in $\Z_p$.
\end{pf}



\subsection{Hensel's lemma}

\begin{thm}[Hensel's lemma]
Let $f\in\Z_p[x]$.
If $f$ has a simple solution in $\F_p$, then $f$ has a solution in $\Z_p$.
\end{thm}
\begin{pf}
asdf
\end{pf}

\begin{rmk}
Hensel's lemma says: for $X$ a scheme over $\Z_p$, $X$ is smooth iff $X(\Z_p)\twoheadrightarrow X(\F_p)$....???
\end{rmk}

\begin{ex}
$f(x)=x^p-x$ is factorized linearly in $\Z_p[x]$.
\end{ex}

\subsection{Sums of two squares}


\begin{thm}[Euler]
A positive integer $m$ can be written as a sum of two squares if and only if $v_p(m)$ is even for all primes $p\equiv3\pmod4$.
\end{thm}
\begin{lem}
Let $p$ be a prime with $p\equiv1\pmod4$.
Every $p$-adic integer is a sum of two squares of $p$-adic integers.
\end{lem}







\section{Dedekind domain}

\begin{rd}
Notherian: & ED \ar{r} & PID \ar{d}\ar{r} & UFD \ar{d} & \\
Non-noetherian: & & B\'ezout \ar{r} & GCD \ar{r} & Euclid's lemma.
\end{rd}

\begin{prop}
Let $A$ be a Dedekind domain.
Then, $A$ is a PID if and only if Euclid's lemma holds.
\end{prop}

If $R$ satisfies the \emph{ascending chain condition for principal ideals}, then $R$ is a PID iff $R$ is a B\'ezout domain, and $R$ is a UFD iff Euclid's lemma holds in $R$.

Every valuation ring is a B\'ezout domain.









\section{Category Theory for Homological Algerba}


\subsection{Additive category}

There are three main concepts that we are going to grasp in this note:
\begin{parts}
\item zero morphisms and zero object;
\item biproduct;
\item additive functors and enriched functors.
\end{parts}

\subsubsection{Zeros}

Let us get started from the definitions of zero morphisms and zero objects.
\begin{defn}
A \emph{zero object} is an object which is initial and terminal.
\end{defn}
\begin{defn}
A category is said to have \emph{zero morphisms} if every hom-set contains a specified morphism denoted by 0 that satisfies $0f=0$ and $f0=0$ for all morphisms $f$.
\end{defn}


In other words, we can say that the existence of zero morphisms is equivalent to $\mathbf{Set_*}$-enrichment.


Here are definitions of categories in which we are interested.
\begin{defn}
A \emph{pointed category} is a cateogry with a zero object.
A \emph{semiadditive category} is a $\mathbf{CMon}$-enriched category with a zero object.
A \emph{additive category} is a $\mathbf{Ab}$-enriched category with a zero object.
A \emph{preadditive category} is another name of $\mathbf{Ab}$-enriched category.
\end{defn}
Note that we have of course several possible ways to give some equivalent definitions.
For example, the following proposition is well-admitted as the definition of semiadditive category.



\begin{rd}
Additive category \dar\rar & Semiadditive category \dar\rar & Pointed category \dar \\
$\mathbf{Ab}$-enriched category \rar\uar[dashed, bend left]{zero object} & $\mathbf{CMon}$-enriched category \rar\uar[dashed, bend left]{zero object} & $\mathbf{Set_*}$-enriched category \uar[dashed, bend left]{zero object}\\
\end{rd}


\subsubsection{Biproducts}
Simply saying, biproducts is something that is both product and coproduct.
To define biproduct, we need zero morphisms, so the $\mathbf{Set_*}$-enrichment will be assumed in all statements in this subsection.
\begin{defn}
A \emph{canonical morphism from coproduct to product} is a morphism blabla
\end{defn}
\begin{defn}[Biproduct]
If the canonical morphism from coproduct to product is an isomorphism, then we call it by the \emph{biproduct}.
\end{defn}
There is a counterexample that coproduct and product are isomorphic but it is not the biproduct.




The following two theorems must be highlightened.
The first theorem captures the familiar isomorphisms between direct sum and direct product of finitely many modules.
\begin{thm}
In a $\mathbf{CMon}$-enriched cateogry, finitary product is also the coproduct so that it forms the biproduct, and vice versa.
\end{thm}

\begin{thm}
A category is semiadditive if and only if it has all finite biproducts.
\end{thm}



\end{document}


