\documentclass{../../large}
\usepackage{../../ikhanchoi}

\newcommand{\Prim}{\operatorname{Prim}}

\begin{document}
\title{C$^*$-Algebras}
\author{Ikhan Choi}
\maketitle
\tableofcontents

\part{Constructions}


\chapter{Completely positive maps}
\section{Operator systems and spaces}


\begin{prb}[Choi-Effros characterization]

\end{prb}

\begin{prb}[Von Neumann inequality]
\end{prb}



\begin{prb}[$n$-positive maps]
Let $S$ be an operator system.
Let $A$ and $B$ be C$^*$-algebras.
\begin{parts}
\item (Cauchy-Schwarz inequality)
Let $\f:A\to B$ be a 2-positive map.
Then,
\[\f(a)^*\f(a)\le\lim_\alpha\|\f(e_\alpha)\|\f(a^*a)\] for all $a\in A$, where $e_\alpha$ be an approximate unit of $A$.
In particular, $\lim_\alpha\|\f(e_\alpha)\|=\|\f\|$.
\item (Multiplicative domain)
Let $\f:A\to B$ be a 4-positive map with $\|\f\|=1$.
If $a\in A$ satisfies $\f(a)^*\f(a)=\f(a^*a)$, then $\f(b)\f(a)=\f(ba)$ for all $b\in A$.
In particular, if $\f:B\to C$ is an extension of a $*$-homomorphism $\pi:A\to C$, then $\f(ab)=\pi(a)\f(b)$ and $\f(ba)=\f(b)\pi(a)$ for $a\in A$ and $b\in B$.
\end{parts}
\end{prb}
\begin{pf}
(a)
Consider $B$ to act on a Hilbert space $H$ non-degenerately and faithfully.
The 2-positivity of $\f$ and
\[\mat{e_\alpha^2&e_\alpha a\\a^*e_\alpha&a^*a}=\mat{e_\alpha&a\\0&0}^*\mat{e_\alpha&a\\0&0}\ge0\]
implies
\[\mat{\f(e_\alpha^2)&\f(e_\alpha a)\\\f(a^*e_\alpha)&\f(a^*a)}\ge0,\]
which is equivalent to have
\[\<\f(e_\alpha^2)\xi,\xi\>+2\Re\<\f(e_\alpha a)\eta,\xi\>+\<\f(a^*a)\eta,\eta\>\ge0\]
for any $\xi,\eta\in H$.
We put $\xi:=-(\|\f(e_\alpha)\|+\e)^{-1}\f(e_\alpha a)\eta$ for $\e>0$ to get
\begin{align*}
(\|\f(e_\alpha)\|+\e)\f(a^*a)
&\ge\f(e_\alpha a)^*(2-(\|\f(e_\alpha)\|+\e)^{-1}\f(e_\alpha^2))\f(e_\alpha a)\\
&\ge\f(e_\alpha a)^*\f(e_\alpha a).
\end{align*}
We have the desired inequality by taking limits for $\alpha$ and $\e$.

(b)
The 2-positivity of $\f_2$ gives
\[\f_2\left(\mat{a&b\\0&0}\right)^*\f_2\left(\mat{a&b\\0&0}\right)\le\f_2\left(\mat{a^*a&a^*b\\b^*a&b^*b}\right),\]
so
\[\mat{0&\f(a^*b)-\f(a^*)\f(b)\\\f(b^*a)-\f(b^*)\f(a)&\f(b^*b)-\f(b^*)\f(b)}\ge0,\]
which implies $\f(b^*a)-\f(b^*)\f(a)=0$ for any $b\in A$.

Note that $\|\pi\|=1$ if $\pi$ is not trivial.
Using the above argument for $a$ and $a^*$, we are done.
\end{pf}




\begin{prb}[Russo-Dye theorem]
If $C(X)\to B$ is positive, then it is c.p.
\end{prb}


\begin{prb}[Completely positive maps for matrix algebras]
Let $A$ be a C$^*$-algebra.
\begin{parts}
\item Choi matrix
\item
There is a one-to-one correspondence
\[\mathrm{CP}(M_n(\C),A)\to M_n(A)_+:\f\mapsto[\f(e_{ij})].\]
\item
Let $A$ be unital.
There is a one-to-one correspondence
\[\mathrm{CP}(A,M_n(\C))\to M_n(A)^*_+:\f\mapsto(s_\f:[a_{ij}]\mapsto\sum_{i,j}\<\f(a_{ij})e_j,e_i\>).\]
\item The above correspondences are (maybe?) isometric if we endow the complete norm on $\mathrm{CP}$.
\end{parts}
\end{prb}
\begin{pf}
(b)


\end{pf}

\section{Dilations and Extensions}

\begin{prb}[Stinespring dilation]
Let $A$ be a C$^*$-algebra and $\f:A\to B(H)$ is a c.p.~map.
There exist a representation $\pi:A\to B(K)$ and a bounded linear operator $V:H\to K$ such that $\f(a)=V^*\pi(a)V$ for $a\in A$.
\[\begin{tikzcd}
B(K) \ar{dr}{V^*\cdot V} &\\
A \ar[swap]{r}{\f} \ar{u}{\pi} & B(H)
\end{tikzcd}\]
\begin{parts}
\item If $\|\f\|=1$, then $V$ is an isometry.
\item 
\item We can take $\pi$ to be minimal in the sense that $\bar{\pi(A)VH}=K$.
\end{parts}
\end{prb}
\begin{pf}

\end{pf}



\begin{prb}[Arveson extension]
Let $A\subset B$ be C$^*$-algebras.
Let $\f:A\to B(H)$ be a c.p.~map and consider the following diagram:
\[\begin{tikzcd}
B\ar[dashed]{dr}{\tilde\f}&\\
A\ar{u}\ar[swap]{r}{\f}&B(H).
\end{tikzcd}\]
\begin{parts}
\item The norm preserving c.p.~extension $\tilde\f$ of $\f$ exists if $B$ is unital and $1_B\in A$.
\item The norm preserving c.p.~extension $\tilde\f$ of $\f$ exists if $\cA$ is unital and $B=A\oplus\C$.
\item The norm preserving c.p.~extension $\tilde\f$ of $\f$ exists if $\cA$ is non-unital and $B=\tilde\cA$.
\item The norm preserving c.p.~extension $\tilde\f$ of $\f$ always exists.
\end{parts}
\end{prb}

\begin{prb}[Representation extension]
Let $I$ be a closed ideal of a C$^*$-algebra $B$.
For a representation $\pi:I\to B(H)$, there is a representation $\tilde\pi:B\to B(H)$ which extends $\pi$.
If $\pi$ is non-degenerate, the extension is unique and $\pi(e_\alpha b)\to\tilde\pi(b)$ and $\pi(be_\alpha)\to\tilde\pi(b)$ strongly for $b\in B$, where $e_\alpha$ is an approximate unit of $I$.
\end{prb}
\begin{pf}
We may assume $\pi$ is non-degenerate by replacing $H$ to $\bar{\pi(I)H}$.
Define $\tilde\pi:B\to B(H)$ such that
\[\tilde\pi(b)(\pi(a)\xi):=\pi(ba)\xi,\qquad a\in I,\ \xi\in H.\]
The well-definedness is from
\[\|\pi(ba)\xi\|^2=\<\pi(a^*b^*ba)\xi,\xi\>\le\|b\|^2\<\pi(a^*a)\xi,\xi\>=\|b\|^2\|\pi(a)\xi\|^2.\]
It is clearly a $*$-homomorphism and extends $\pi$.

For the uniqueness, if $\pi$ is non-degenerate and $\tilde\pi$ is a $*$-homomorphism which extends $\pi$, then
\[\tilde\pi(b)(\pi(a)\xi)=\tilde\pi(b)\tilde\pi(a)\xi=\tilde\pi(ba)\xi=\pi(ba)\xi,\]
which is unique by the density of $\pi(I)H$ in $H$.
\end{pf}

extension of representations for ideals

unique extension of c.p.~maps for hereditary subalgebras.



\section{Completely bounded maps}




\section{Tensor products}

\begin{prb}[Maximal tensor products]
Let $A$ and $B$ be C$^*$-algebras.
\begin{parts}
\item (restrictions) A commuting pair of $*$-homomorphisms $\pi:A\to B(H)$ and $\pi':B\to B(H)$ corresponds to a $*$-homomorphism $\Pi:A\odot B\to B(H)$ via the relation $\Pi(a\otimes b)=\pi(a)\pi'(b)$.
\item $A\odot B$ admits a $*$-representation and every norms induced from these $*$-representations are uniformly bounded. So, we can define a maximal tensor norm on $A\odot B$.
\item $a\otimes-:B\to A\odot B$ is a bounded linear map for each $a\in A$ with respect to any C$^*$-norm on $A\odot B$. [BO, 3.2.5]
\end{parts}
\end{prb}


\begin{prb}[Minimal tensor product]
spatiality
\end{prb}
\begin{prb}[Takesaki theorem]
\end{prb}

Tensors with $M_n(\C)$, $C_0(X)$.


\begin{prb}[Haagerup tensor product]
\end{prb}

Trick

\section*{Exercises}
\begin{prb}
Let $A$ be a hereditary C$^*$-subalgebra of a C$^*$-algebra $B$ and let $b\in B_+$.
If for any $\e>0$ there is $a\in A_+$ such that $b-a\le\e$, then $b\in A$.
\end{prb}
\begin{pf}
For $a\in A_+$ satisfying $b\le a+\e\le(a^{\frac12}+\e^{\frac12})^2$, define
\[a_\e:=a^{\frac12}(a^{\frac12}+\e^{\frac12})^{-1}ba^{\frac12}(a^{\frac12}+\e^{\frac12})^{-1}\in A.\]
Then, 
\[\|b^{\frac12}-b^{\frac12}a^{\frac12}(a^{\frac12}+\e^{\frac12})^{-1}\|^2=\e\|(a^{\frac12}+\e^{\frac12})^{-1}b(a^{\frac12}+\e^{\frac12})^{-1}\|\le\e.\]
Thus $a_\e\to b$ in norm as $\e\to0$.
\end{pf}









\chapter{Hilbert modules}

\section{Operator algebraic modules}

\begin{prb}[Banach modules]
Let $A$ be a Banach algebra.
A \emph{Banach $A$-module} is a Banach space $\cE$ which is a $A$-module such that the action is bounded.
\begin{parts}
\item (Cohen factorization theorem) If $A$ has a left approximate unit, then $A\cE$ is closed in $\cE$.
\end{parts}
\end{prb}
\begin{pf}
Suppose $\xi$ belongs to the closure of $A\cE$ and take $\e>0$.
We will construct a decreasing sequence $a_n$ in the unitization $\tilde A$ such that $a_n^{-1}\xi$ and $a_n$ are both Cauchy.
In order to do this, we first need to check $a_n^{-1}\in\tilde A\setminus A$ can act on $\cE$, which is easy anyway.

Let $a_0=1$ and suppose we have defined $a_n\ge 2^{-n}$.
Take $b\in A$ and $\eta$ such that $\|\xi-b\eta\|<\e2^{-(2n+1)}$.
Take $e\in A$ such that $\|a_n^{-1}b-ea_n^{-1}b\|\|\eta\|<\e2^{-(n+1)}$.
Now inductively define
\[a_{n+1}:=a_n-2^{-(n+1)}(1-e)\in\tilde A\]
so that $a_{n+1}\ge2^{-(n+1)}$ is invertible.

Then, we can check $a_n$ is Cauchy whose limit point belongs to $A$, and
$a_n^{-1}\xi$ is Cauchy because by the identity
\[a_{n+1}^{-1}-a_n^{-1}=a_{n+1}^{-1}(a_n-a_{n+1})a_n^{-1}=a_{n+1}^{-1}2^{-(n+1)}(1-e)a_n^{-1}\]
we get
\begin{align*}
\|a_{n+1}^{-1}\xi-a_n^{-1}\xi\|
&\le\|a_{n+1}^{-1}-a_n^{-1}\|\|\xi-b\eta\|+\|(a_{n+1}^{-1}-a_n^{-1})b\|\|\eta\|\\
&\le2^n\cdot\e2^{-(2n+1)}+\e2^{-(n+1)}=\e2^{-n}.
\end{align*}
\end{pf}

\begin{prb}[Finsler modules]
Let $A$ be a C$^*$-algebra.
\end{prb}

\begin{prb}[Hilbert modules]
Let $A$ be a C$^*$-algebra.
A \emph{Hilbert $A$-module} is a complex linear space $\cE$ which is a right $A$-module together with a
\begin{enumerate}[(i)]
\item a ring homomorphism $A^{op}\to\End_\C(\cE)$,
\item an $A$-valued inner product $\<\cdot,\cdot\>:\cE\times\cE\to A$ which is $A$-linear in second argument,
\end{enumerate}
which is complete with respect to the norm $\|\xi\|:=\|\<\xi,\xi\>\|^{\frac12}$.
\begin{parts}
\item
\end{parts}
\end{prb}



constructions:
direct sum, tensor product, localization

examples:
A itself


\section{Multiplier algebras}
\begin{prb}[Double centralizer characterization]
Let $A$ be a C$^*$-algebra.
A \emph{double centralizer} of $A$ is a pair $(L,R)$ of bounded linear maps on $A$ such that $aL(b)=R(a)b$ for all $a,b\in A$.
The \emph{multiplier algebra} $M(A)$ of $A$ is defined to be the set of all double centralizers of $A$.
There is another characterization $M(A):=L_A(A)$, the set of adjointable operators to itself.
\end{prb}


\begin{prb}[Strict topology]
Let $a_\alpha$ be a net in $M(A)$
\begin{parts}
\item $\|\pi(a-e_\alpha a)\xi\|^2$
\item If $a_\alpha$ are unitary, the convergences in the strict topology and the weak topology(how to define this?) coincide.
\item If $a_\alpha$ are increasing, the convergences in the strict topology and the weak topology(how to define this?) coincide.
\end{parts}
\end{prb}

\begin{prb}[Essential ideals]
\begin{parts}
\item Hilbert C$^*$-module description
\end{parts}
\end{prb}


\begin{prb}[Examples of multiplier algebras]
\begin{parts}
\item $M(K(H))\cong B(H)$.
\item $M(C_0(\Omega))\cong C_b(\Omega)$.
\end{parts}
\end{prb}
\begin{pf}
(a)

(b)
First we claim $C_0(\Omega)$ is an essential ideal of $C_b(\Omega)$.
Since $C_b(\Omega)\cong C(\beta\Omega)$, and since closed ideals of $C(\beta\Omega)$ are corresponded to open subsets of $\beta\Omega$, $C_0(\Omega)\cap J$ is not trivial for every closed ideal $J$ of $C_b(\Omega)$.

Now we have an injective $*$-homomorphism $C_b(\Omega)\to M(C_0(\Omega))$, for which we want to show the surjectivity.
Let $g\in M(C_0(\Omega))_+$.
\end{pf}


\begin{prb}[Morphisms]
Let $A$ and $B$ be C$^*$-algebras.
A \emph{morphism} from $A$ to $B$ is defined to be a non-degenerate $*$-homomorphism $A\to M(B)$.
\begin{parts}
\item The inclusion of a proper closed ideal is never a morphism. A surjective $*$-homomorphism $A\to B$ is always a morphism.
\end{parts}
\end{prb}


Every morphism $A\to M(B)$ induces the following?:
\[\begin{tikzcd}
PS(B) \rar[->>]\dar & \hat B \rar[->>]\dar & \Prim(B) \dar \\
PS(A) \rar[->>] & \hat A \rar[->>] & \Prim(A).
\end{tikzcd}\]

For a short exact sequence
\[\begin{tikzcd}[column sep=small]0\rar&I\rar&A\rar&B\rar&0\end{tikzcd},\]
we have
\[\begin{tikzcd}[row sep=small]
PS(I) \dar[->>]\rar[hook] & PS(A) \dar[->>] & PS(B) \dar[->>]\lar[hook'] \\
\hat I \dar[->>]\rar[hook,shorten >= 10, shorten <= 10] & \hat A \dar[->>] & \hat B \dar[->>]\lar[hook',shorten >= 10, shorten <= 10] \\
\Prim(I) \rar[hook,swap]{\text{open}} & \Prim(A) & \Prim(B) \lar[hook']{\text{closed}}
\end{tikzcd}\]



\section{Pimsner algebras}


\begin{prb}[C$^*$-correspondences]
Let $A$ be a C$^*$-algebra.
A \emph{C$^*$-correspondence} over $A$ is a right Hilbert $A$-module $\cE$ together with a $*$-homomorphism $\f:A\to B(\cE)$, called the \emph{left action}.
We say $\cE$ is \emph{faithful} or \emph{non-degenerate} if $\f$ is faithful or non-degenerate, respectively.
\begin{parts}
\item If $\f:A\to M(B)$ is a unital completely positive map, then we can construct a natural $A$-$B$-correspondence $\cE$ by mimicking the GNS construction on $A\odot B$.
\item If $\f:A\to M(B)$ is a non-degenerate $*$-homomorphism, $\f\in\Mor(A,B)$ in other words, then we can associate a canonical $A$-$B$-correspondence $B$ such that the left action is realized with $\f$.
More precisely, $\iota:\cE\to B:a\otimes b\mapsto\f(a)b$ provides a well-defined linear isomorphism (surjectivity follows from the density of $\f(A)B$ in $B$ and the Cohen factorization theorem) and the two actions on $\cE$ is described by $\iota(a\xi b)=\f(a)\iota(\xi)b$.
\end{parts}
\end{prb}


\begin{prb}
Let $\cE$ be a C$^*$-correspondence over a C$^*$-algebra $A$.
Let $B$ be a C$^*$-algebra and see it as a trivial C$^*$-correspondence over $B$.
A \emph{representation} of $\cE$ on $B$ is a pair $(\pi,\tau)$ of a $*$-homomorphism $\pi:A\to B$ and a linear map $\tau:\cE\to B$ such that
\[\pi(\<\xi,\eta\>)=\tau(\xi)^*\tau(\eta),\qquad\tau(\f(a)\xi)=\pi(a)\tau(\xi).\]
We define the \emph{Katsura ideal}
\[J(\cE):=\f^{-1}(K(\cE))\cap\f^{-1}(0)^\perp.\]

A \emph{covariant representation} is a representation of $\cE$ such that
\[\psi(\f(a))=\pi(a),\qquad a\in J(\cE).\]
\begin{parts}
\item
Let $(A,\Z,\alpha)$ be a C$^*$-dynamical system and consider the canonical C$^*$-correspondence $A$ over $A$ with the left action $\f:=\alpha_1\in\Aut(A)\subset\Mor(A)$.
This correspondence is full, faithful, and non-degenerate.
Note that also we have $J(A)=\f^{-1}(A)\cap A=A$.
If $(\pi,\tau)$ is an any representation of this C$^*$-correspondence $A$ on $B$, then 
\end{parts}
\end{prb}

How can we decribe representations of C$^*$-correspondence $A$ with left action $\f\in\Aut(A)$ in terms of covariant representations of the C$^*$-dynamical system $(A,\Z,\alpha)$ with $\alpha_n=\f^n$?



as a morphism
sub and quotient, direct sum, tensor product,

Toeplitz-Cuntz
Toeplitz-Pimsner
Cuntz-Pimsner
Cuntz-Krieger



Subproduct systems


\section{Morita equivalence}



Induced representations?







\chapter{Examples}



\section{Crossed products}


\begin{prb}[Group algebras]
\end{prb}



type I, subhomogeneous


crystallographic
discrete heisenberg
free groups
projectionless of $C_r^*(F_2)$



\begin{prb}[Enveloping C$^*$-algeberas]
Let $A$ be a $*$-algebra.
A \emph{C$^*$-norm} is an submultiplicative norm satisfying the C$^*$-identity.
Does $A$ have enough $*$-representations?
\begin{parts}
\item A complete C$^*$-norm is unique if it exists.
\item For every C$^*$-norm $\alpha$ on $A$, there is a $*$-isometry $\pi:A\to B(H)$.
\item For maximal C$^*$-norm, there is a universal property. The maximal C$^*$-norm can be obtained by running through cyclic representations.
\end{parts}
\end{prb}




\begin{prb}[C$^*$-dynamical system]
Let $G$ be a locally compact group.
A \emph{C$^*$-dynamical system} or a \emph{$G$-C$^*$-algebra} is a C$^*$-algebra $A$ together with a group homomorphism $\alpha:G\to\Aut(A)$ that is continuous in the point-norm topology.
We will often write a triple $(A,G,\alpha)$ instead of $A$ to refer a C$^*$-dynamical system.
\begin{parts}
\item There is an equivalence between categories of locally compact transformation groups and C$^*$-dynamical system on abelian C$^*$-algebras.
\end{parts}
\end{prb}


On $U(H)$, the strict topology and the strong operator topology are equal.
Therefore, we have three topologies to consider: strong, weak, and $\sigma$-weak.

\begin{prb}[Covariant representation]
Let $G$ be a locally compact group.

A \emph{covariant representation} of a C$^*$-dynamical system $(A,G,\alpha)$ is a $G$-equivariant $*$-homomorphism $\pi:(A,G,\alpha)\to(B(H),G,\beta)$ for a C$^*$-dynamical system $(B(H),G,\beta)$, where a Hilbert space $H$.
\begin{parts}
\item
There exists a unitary representation $u:G\to B(H)$ such that $\pi(\alpha_sa)=u_s\pi(a)u_s^*$.
\item (Integrated form)
There is a one-to-one correspondence between covariant representations of $(A,G,\alpha)$ and $*$-representations of $L^1(G,A)$. (non-degenerate)
\end{parts}
\end{prb}

Note that we have a homeomorphism $\Aut(K(H))\cong PU(H)$ between the point-norm topology and the strong operator topology.

$\Z$-action, $\Homeo$-action, left multiplication of subgroup
induced representation
regular representation $(C_0(G),G,\lambda)\to(B(L^2(G)),G,\lambda)$.


commutative case




\section{Graph algebras}






\section{Groupoid algebras}





\section{Free products}






\part{Properties}
\chapter{Approximation properties}
\section{Nuclearity and exactness}

finite dimensional[BO, 3.3.2], abelian, AF
permanence properties


\begin{prb}[Completely positive approximation property]
Let $A$ be a C$^*$-algebra.
\begin{parts}
\item If $A$ has the CPAP, then $A$ is nuclear.
\item If $A$ is nuclear, then $A$ has the CPAP.
\end{parts}
\end{prb}
\begin{pf}

(b)



Let $E\subset A$ and $F\subset A^*$ be finite subsets and fix $\e>0$.
We want to find completely positive contractions $\f:A\to M_n(\C)$ and $\psi:M_n(\C)\to A$ such that
\[|l(a)-l(\psi\circ\f(a))|<\e\]
for $a\in E$ and $l\in F$.
To implement the approximation, we would like to regard a bounded linear operator on $A$ as a state of a tensor product of C$^*$-algebras, which maps $\theta\in B(A)$ to the linear functional characterized by $a\otimes l\mapsto l(\theta(a))$.
However, since $A^*$ is not a C$^*$-algebra, we embed $A^*$ locally in $B(H)$ through the Radon-Nikodym type result.
Let $\pi:A\to B(H)$ be the cyclic representation obtained from a positive linear functional that dominates $F$ and $\Omega$ the cyclic vector such that there is a linear map $\pi':F\to\pi(A)'$ satisfying
\[l(a)=\omega_\Omega(\pi(a)\pi'(l))=\<\pi(a)\pi'(l)\Omega,\Omega\>\]
for $a\in E$ and $l\in F$.

Since $A$ is nuclear, we have a well-defined representation
\[\pi\times i:A\otimes_{\min}\pi(A)'\to B(H).\]
If we take any faithful representation $\rho:A\to B(K)$, then we obtain a fathful representation
\[\rho\otimes i:A\otimes_{\min}\pi(A)'\to B(K\otimes H).\]
By the Hahn-Banach separation, the state $\omega_\Omega\circ(\pi\times i)$ on $A\otimes_{\min}\pi(A)'$ can be approximated weakly$^*$ by convex combinations of vector states in $B(K\otimes H)$.
In particular, by the density of $\pi(A)\Omega$ in $H$, we have algebraic tensors $(\tau_k)_{k=1}^m\subset K\odot\pi(A)\Omega$ such that
\[\Bigl|\omega_\Omega((\pi\times i)(a\otimes\pi'(l)))-\sum_{k=1}^m\lambda_k\omega_{\tau_k}((\rho\otimes i)(a\otimes\pi'(l)))\Bigr|<\e\tag{\dagger}\]
for all $a\in E$ and $l\in F$, where $\lambda_k\ge0$, $\sum_{k=1}^m\lambda=1$.

If we write each element $\tau\in K\odot\pi(\cA)\Omega$ as
\[\tau=\sum_{i=1}^n\eta_i\otimes\pi(b_i)\Omega,\]
then
\begin{align*}
\omega_\tau((\rho\otimes i)(a\otimes\pi'(l)))
&=\left\<(\rho(a)\otimes\pi'(l))\Bigl(\sum_{j=1}^n\eta_j\otimes\pi(b_j)\Omega\Bigr),\Bigl(\sum_{i=1}^n\eta_i\otimes\pi(b_i)\Omega\Bigr)\right\>\\
&=\sum_{i,j=1}^n\<\rho(a)\eta_j,\eta_i\>\<\pi'(l)\pi(b_i^*b_j)\Omega,\Omega\>\\
&=l\Bigl(\sum_{i,j=1}^n\<\rho(a)\eta_j,\eta_i\>b_i^*b_j\Bigr).
\end{align*}
If we define completely positive contractions $\f:A\to M_n(\C)$ and $\psi:M_n(\C)\to A$ for each $\tau$ such that
\[\f(a):=[\<\rho(a)\eta_j,\eta_i\>],\quad\psi([e_{ij}]):=b_i^*b_j,\]
then we have $\omega_\tau(a\otimes\pi'(l))=l(\psi\circ\f(a))$.

Since $\mu(a\otimes\pi'(l))=l(a)$ and since the completely positive contractions which factor through a matrix algebra form a convex set, we have completely positive contractions $\f:A\to M_n(\C)$ and $\psi:M_n(\C)\to A$ such that the inequality (\dagger) is rewritten as
\[|l(a)-l(\psi\circ\f(a))|<\e,\]
so we are done.
\end{pf}





quotients of nuclear
local reflexivity


a separable C$^*$-algebra is nuclear if and only if every factor representation is hyperfinite.

Extension properties
weak expectation property
relatively weakly injective
maximal tensor product inclusion problem




\section{Quasi-diagonality}

\begin{prb}[Weyl-von Neumann theorem]
A self-adjoint bounded operator is quasi-diagonal.
\end{prb}

\begin{prb}[Glimm lemma]
If a state $\omega$ of $B(H)$ vanishes on $K(H)$, then it is a weak$^*$ limit of vector states.
\end{prb}

\begin{prb}[Voiculescu theorem]
\end{prb}


\begin{prb}[Quasi-diagonal algebras]
An operator $a\in B(H)$ is called \emph{quasi-diagonal} if there is a net of projections $p_i\in B(H)$ such that $[p_i,a]\to0$ in norm and $p_i\uparrow\id_H$ strongly.
A C$^*$-algebra is called \emph{quasi-diagonal} if it admits a faithful representation whose image is quasi-diagonal.
\end{prb}

faithful non-degenerate essential representations of a quasi-diagonal C$^*$-algebra are all quasi-diagonal

locally quasi-diagonal

\section{AF-embeddability}













\chapter{Amenability}


\section{Amenable groups}


\section{Amenable actions}
crossed products
$Z_2$-grading
Connes-Feldman-Weiss
Anantharaman-Delaroche
Gromov boundaries
approximately central structure?
dynamical Kirchberg-Phillips

stably finite
dynamical Elliott program

Ornstein-Weiss-Rokhlin lemma

\section{Exact groups}
Exact groups

\section{Other properties}
Kazdahn property (T)
factorization property
Haagerrup property


Kaplansky conjecture












\chapter{Simplicity}


Furstenburg boundary



















\part{Invariants}
\chapter{Operator K-theory}


\section{Homotopy of C$^*$-algebras}

\begin{prb}[Homotopy of $*$-homomorphisms]
Let $A,B$ be C$^*$-algebras.
Two $*$-homomorphisms in $\Mor(A,B)$ are said to be \emph{homotopic} if they are connected by a path in $\Mor(A,B)$ that is continuous with the point-norm topology.
\begin{parts}
\item For pointed compact Hausdorff spaces $(X,x_0),(Y,y_0)$, two pointed maps $\f_0,\f_1:X\to Y$ are homotopic if and only if $\f_0^*,\f_1^*:C_0(Y\setminus\{y_0\})\to C_0(X\setminus\{x_0\})$ are homotopic.
\end{parts}
\end{prb}
\begin{pf}
(a)
Suppose $\f_0$ and $\f_1$ are connected by a homotopy $\f_t$.
Fixing $g\in C_0(Y)$ and $t_0\in I$, we want to show
\[\lim_{t\to t_0}\sup_{x\in X}|g(\f_t(x))-g(\f_{t_0}(x))|=0.\]
Since the function $g$ is uniformly continuous, with respect to an arbitrarily chosen uniformity on $Y$, so that there is an entourage $E\subset Y\times Y$ such that $(y,y')\in E\circ E$ implies $|g(y)-g(y')|<\e$.
Using compactness we have a finite sequence $(y_i)_{i=1}^n\subset Y$ such that for every $y$ there is $y_i$ satisfying $(y,y')\in E$.
Then, $\f^{-1}(E[y_i])$ is a finite open cover of $X\times I$, so we have $\delta$ such that $|t-t_0|<\delta$ implies for any $x\in X$ the existence of $i$ satisfying $(\f_t(x),y_i)\in E$ and $(\f_{t_0}(x),y_i)\in E$, which deduces the desired inequality.

Conversely, suppose $\f_0^*$ and $\f_1^*$ are connected by a homotopy $\f_t^*$.
By taking dual, we can induce $\f_t:X\to Y$ such that $g(\f_t(x))=(\f_t^*g)(x)$ for each $g\in C(Y)$ from $\f_t^*$ via the embedding $X\to M(X)$ by Dirac measures.
Let $V$ be an open neighborhood of $\f_{t_0}(x_0)$ and take $g\in C(Y)$ such that $g(\f_{t_0}(x_0))=1$ and $g(y)=0$ for $y\notin V$.
Now we have an open neighborhood $U$ of $x_0$ such that $x\in U$ implies $|(\f_{t_0}^*g)(x)-(\f_{t_0}^*g)(x_0)|<\frac12$.
Also we have $\delta>0$ such that $|t-t_0|<\delta$ implies $\|\f_t^*g-\f_{t_0}^*g\|<\frac12$.
Therefore, $(x,t)\in U\times(t_0-\delta,t_0+\delta)$ implies $g(\f_t(x))>0$, hence $\f_t(x)\in V$, which means $X\times I\to Y:(x,t)\mapsto\f_t(x)$ is continuous.
\end{pf}

We have $\tilde K^n(X,x_0)=K_n(C_0(X\setminus\{x_0\}))$ for a pointed compact Hausdorff space $X$.
Now then since the inclusion $\{x_0\}\to X$ induces the section so that
\[0\to K_0(C_0(X\setminus\{x_0\}))\to K_0(C(X))\to K_0(\{x_0\})\to0\]
splits, we have
\[K^0(X)=\tilde K^0(X,x_0)\oplus\Z=K_0(C_0(X\setminus\{x_0\}))\oplus K_0(\{x_0\})=K_0(C(X))\]
for a compact connected Hausdorff space $X$.
The additivity of $K_0$ and $K^0$ removes the connectedness condition.

\[K_0(\C)=\Z,\quad K_0(C_0(\R))=0,\quad K_1(C_0(\R))=K_0(C_0(\R^2))=\Z\]
\[K^0(*)=\Z,\quad K^0(S^1)=\Z,\quad K^1(S^1)=K^0(S^2)=\Z[x]/(x-1)^2\]

\section{$K_0$ groups}

local Banach algebras

homotopy invariance
relative, reduced theory
partially ordered abelian group


\section{$K_1$ groups}

unitary
Bott periodicity
six-term exact sequence


\section{Equivariant K-theory}
\begin{prb}[Pimsner-Voiculescu exact sequence]
\end{prb}
Connes' Thom isomorphism




\chapter{KK-theory}

\section{Cuntz pairs}

\section{Kasparov modules}






\chapter{Cuntz semigroup}

nuclear dimension










\part{Classification}
\chapter{Simple nuclear algebras}


\section{AF-algebras}

Glimm's classification of UHF algebras
Bratteli diagram
Elliott's intertwining argument

Separable AF-algebras are classified by pointed ordered $K_0$.


\section{Kirchberg-Phillips theorem}

\section{Classifiability}
Jiang-Su stability
Universal coefficient theorem

Toms-Winter conjecture
strongly self-absorbing
nuclear dimension




successful in Kirchberg algebras


https://arxiv.org/pdf/2307.06480.pdf

Elliott classification problem
Kirchberg-Phillipes theorem

operator K-theory and its pairing with traces

$\cZ$-stability, Rosenberg-Schochet universal coefficient theorem

Connes-Haagerup classification of injective factors

Kirchberg: unital simple separable $\cZ$-stable algebra is either purely infinte or stably finite.
Haagerup, Blackadar, Handelman: unital simple stably finite algebra has a trace.

Glimm: uniformly hyperfinite algebras
Murray-von Neumann: hyperfinite II$_1$ factors




\section{Inclusions}










\chapter{Continuous fields}


\section{Banach bundles}

\begin{prb}[Banach bundles]
A \emph{Banach bundle}, introduced by Fell, is a continuous open surjection $\pi:E\to X$ between topological spaces together with Banach space structure on each fiber $\pi^{-1}(x)$ such that:
\begin{enumerate}[(i)]
\item the addition $\{(e,e'):\pi(e)=\pi(e')\}\subset E\times E\to E:(e,e')\mapsto e+e'$ is continuous,
\item the scalar multiplication $\C\times E\to E:(\lambda,e)\mapsto\lambda e$ is continuous,
\item the norm $E\to\R_{\ge0}:e\mapsto\|e\|$ is continuous,
\item the family of subsets
\[\{e\in B:\pi(e)\in U,\ \|e\|<r\}_{U\in N(x),r>0}\]
forms a neighborhood basis of $0\in\pi^{-1}(x)$ in $E$.
\end{enumerate}
The forth condition is equivalent to that if $\|e_i\|\to0$ and $\pi(e_i)\to x$ then $e_i\to 0_x\in\pi^{-1}(x)$.
\begin{parts}
\item For a Banach bundle $E\to X$, if $X$ is locally compact Hausdorff and every fiber $E_x$ shares a same finite dimension, then the bundle is locally trivial.
\end{parts}
\end{prb}


\begin{prb}[Continuous fields of Banach spaces]
\end{prb}



\begin{prb}[Hilbert bundles]
A \emph{Hilbert bundle} is a Banach bundle whose norm function satisfies the parallelogram law.

\begin{parts}
\item On a compact $X$, there is an equivalence between the category of Hilbert $C(X)$-modules and the category of Hilbert bundles over $X$.
\item On a compact $X$, there is an equivalence between the category of algebraically finitely generated Hilbert $C(X)$-modules and the category of classical locally trivial finite-rank complex vector bundle over $X$.
It is due to that finitely generatedness implies the projectivity and the Serre-Swan theorem.
\end{parts}
\end{prb}


\section{Primitive ideal space}

\begin{prb}[Left ideals]
\end{prb}

\begin{prb}[Primitive ideals]
hull kernel topology
\[PS(A)\cong\{(\pi,\psi)\}/\sim_u,\qquad\hat A\cong\{\pi\}/\sim_u.\]

\[\begin{array}{c|ccc}
A & PS(A) & \hat A & \Prim(A) \\\hline
C(X) & X & X & X \\
K(H) & PH & * & * \\
\tilde K(H) & ? & ? & \{0,K(H)\} \\
B(H) &&&
\end{array}\]
\begin{parts}
\item $\Prim(A)$ is locally compact T$_0$ space.
\item Two maps $PS(A)\to\hat A\to\Prim(A)$ are continuous surjective open maps
\item If $A$ is type I, then $\hat A\to\Prim(A)$ is an homeomorphism.
\end{parts}

\end{prb}

\begin{prb}[Dauns-Hoffman theorem]
\end{prb}


\section{Dixmier-Douady theory}


Fell's condition

A C$^*$-algebra $A$ is called \emph{continuous trace} if the set of all $a\in\cA$ such that $\hat A\to\R_{\ge0}:\pi\mapsto\tr(\pi(a^*a))$ is continuous is dense in $A$.



Dadarlat-Pennig theory


Coactions and Fell bundles




\end{document}