\documentclass[11pt]{article}
\usepackage{../../ikany}
\usepackage[margin=100pt]{geometry}
\linespread{1.1}
\usepackage[bitstream-charter,cal]{mathdesign}
\let\circledS\undefined
\usepackage[T1]{fontenc}

\setcounter{secnumdepth}{1}

\begin{document}
\tableofcontents

\newpage
\part*{Preliminaries}
\section{Calculus}
\section{Linear algebra}
\section{Set theory and number systems}




\newpage
\part{Analysis}
\setcounter{section}{0}

\section{Foundation of Calculus}
	\subsection{Sequences}
	\begin{prb}
	Show that for a nonnegative sequence $a_n$ if $\sum a_n$ diverges then $\sum\frac{a_n}{1+a_n}$ also diverges.
	\end{prb}

	\begin{prb}
	Show that every real sequence has a monotonic subsequence that converges to the limit superior of the original sequence.
	\end{prb}

	\begin{prb}
	Show that if a decreasing nonnegative sequence $a_n$ converges to 0 and satisfies $S_n\le1+na_n$ then $S_n$ is bounded by 1.
	\end{prb}

	\subsection{Functions}
	\begin{prb}
	Let $f:\R\to\R$ be differentiable.
	Show that $f$ is identically zero if $f'(x)=f(x)^2$ for all $x$.
	\end{prb}

	\begin{prb}
	Show that if both limits of a real function and its derivative at infinity exist then the function vanishes at infinity.
	\end{prb}

	\begin{prb}
	Let $f$ be a real $C^2$ function with $f''(c)\ne0$. Defined a function $\xi$ such that $f(x)-f(c)=f'(\xi(x))(x-c)$ with $|\xi-c|\le|x-c|$, show that $\xi'(c)=1/2$.
	\end{prb}

	\begin{prb}
	Let $f$ be a $C^2$ function such that $f(0)=f(1)=0$. Show that $\|f\|\le\frac18\|f''\|$.
	\end{prb}

	\begin{prb}
	Show that the set of local minima of a convex real function is connected.
	\end{prb}

	\begin{prb}
	Show that a smooth function such that for each $x$ there is $n$ having the $n$th derivative vanish is a polynomial.
	\end{prb}

	\begin{prb}
	Show that if a real $C^1$ function $f$ satisfies $f(x)\ne0$ for $x$ such that $f'(x)=0$, then in a bounded set there are only finite points at which $f$ vanishes.
	\end{prb}

	\begin{prb}
	Let a real function $f$ be differentiable. For $a<a'<b<b'$ show that there exist $a<c<b$ and $a'<c'<b'$ such that $f(b)-f(a)=f'(c)(b-a)$ and $f(b')-f(a')=f'(c')(b'-a')$.
	\end{prb}

	\begin{prb}*
	Show that if a sequence of real functions $f_n\colon[0,1]\to[0,1]$ satisfies $|f(x)-f(y)|\le|x-y|$ whenever $|x-y|\ge\frac1n$, then the sequence has a uniformly convergent subsequence.
	\end{prb}

	\begin{prb}
	Let $f$ be a differentiable function on the unit closed interval. Show that if $f(0)=0$ there is $c$ such that $cf'(c)=f(c)$. (Flett)
	\end{prb}

	\begin{prb}
	Let $f$ be a differentiable function on the unit closed interval. Show that if $f(0)=0$ there is $c$ such that $cf(c)=(1-c)f'(c)$.
	\end{prb}

	\begin{prb}
	Let $f:\R\to\R$ be continuous. Show that $f(x)=c$ cannot have exactly two solutions for every constant $c\in\R$.
	\end{prb}

	\begin{prb}
	Show that a continuous function that takes on no value more than twice takes on some value exactly once.
	\end{prb}

	\begin{prb}
	Let $f$ be a function that has the intermediate value property. Show that if the preimage of every singleton is closed, then f is continuous.
	\end{prb}

	\subsection{Integration}
	\begin{prb}
	Find the value of $\lim_{n\to\infty}\frac1n\left(\sum_{k=1}^n\frac1nf\left(\frac kn\right)-\int_0^1f(x)\,dx\right)$.
	\end{prb}

	\begin{prb}
	Show that if $xf'(x)$ is bounded and $x^{-1}\int_0^xf\to L$ then $f(x)\to L$ as $x\to\infty$.
	\end{prb}

	\subsection{Multivariable calculus}




\section{Lebesgue theory}
	\subsection{Measure theory}
	\begin{prb}*
	Show that a measurable subset of $\R$ with positive measure contains an arbitrarily long subsequence of an arithmetic progression.
	\end{prb}


\section{General topology}
	\begin{prb}
	Show that if $A^\circ\subset B$ and $B$ is closed, then $(A\cup B)^\circ\subset B$.
	\end{prb}

\section{Harmonic analysis}
\section{Complex analysis}

	\begin{prb}
	Show that if a holomorphic function has positive real parts on the open unit disk then $|f'(0)|<2\Re f(0)$.
	\end{prb}

	\begin{prb}
	Show that if at least one coefficient in the power series of a holomorphic function at each point is 0 then the function is a polynomial.
	\end{prb}

	\begin{prb}
	Show that if a holomorphic function on a domain containing the closed unit disk is injective on the unit circle then so is on the disk.
	\end{prb}

	\begin{prb}
	Show that for a holomorphic function $f$ and every $z_0$ in the domain there are $z_1\ne z_2$ such that $\frac{f(z_1)-f(z_2)}{z_1-z_2}=f'(z_0)$.
	\end{prb}

	\begin{prb}
	For two linearly independent entire functions, show that one cannot dominate the other.
	\end{prb}

	\begin{prb}
	Show that uniform limit of injective holomorphic function is either constant or injective.
	\end{prb}

	\begin{prb}
	Suppose the set of points in a domain $U\subset\C$ at which a sequence of bounded holomorphic functions $(f_n)$ converges has a limit point. Show that $(f_n)$ compactly converges.
	\end{prb}



\section{Functional analysis}
	\subsection{Topological vector spaces}
	\begin{prb}
	Let $T$ be an invertible linear operator on a normed space.
	Show that $T^{-2}+\|T\|^{-2}$ is injective if it is surjective.
	\end{prb}

	\subsection{Weak topologies}
	\subsection{Spectral theory}
	\subsection{Operator algebras}
	\begin{prb}*
	Let $f(x)=x(1+x)^{-1}$ be a function on $\R_{\ge0}$.
	Show that a C$^*$-algebra $\cA$ is commutative if and only if $f$ is operator subadditive in $\cA$.
	\end{prb}
%L\"owner-Heinz inequality

\section{Proability theory}

	\begin{prb}
	Find the probability that arbitrarily chosen positive integers are coprime.
	\end{prb}


\section{Linear partial differential equations}


	\begin{prb}*
	Find the range of the operator $T:\cE'(\R^d)\to\cD'(\R^d)$ defined by $Tf=\Phi*f$, where $\Phi$ is the fundamental solution of Laplace's equation.
	\end{prb}









\newpage
\part{Algebra}
\setcounter{section}{0}

\section{Algebraic structures}

	\subsection{Groups}

	\begin{prb}
	Show that a finite symmetric group has two generators.
	\end{prb}

	\begin{prb}
	Show that a group of order $2p$ for a prime $p$ has exactly two isomorphic types.
	\end{prb}

	\begin{prb}
	Show that a group $G$ is abelian if $|G|=p^2$ for a prime $p$.
	\end{prb}

	\begin{prb}
	Show that a group $G$ is abelian if it has a surjective cube map.
	\end{prb}

	\begin{prb}
	Let $G$ be a finite group of order $n$ and $p$ the smallest prime divisor of $n$. Show that a subgroup of $G$ of index $p$ is normal in $G$.
	\end{prb}

	\begin{prb}
	Find all $n$ such that $(\Z/n\Z)^\times$ is cyclic.
	\end{prb}

	\begin{prb}
	Show that a nontrivial normalizer of a $p$-group meets its center out of identity.
	\end{prb}

	\begin{prb}
	Show that a proper subgroup of a finite $p$-group is a proper subgroup of its normalizer. In particular, every finite $p$-group is nilpotent.
	\end{prb}

	\begin{prb}
	Show that a finite group $G$ satisfying $\sum_{g\in G}\ord(g)\le2n$ is abelian.
	\end{prb}

	\begin{prb}
	Show that the order of a group with trivial automorphism group is either 1 or 2.
	\end{prb}

	\begin{prb}
	Find all homomorphic images of $A_4$ up to isomorphism.
	\end{prb}

	\begin{prb}
	Show that in a group of order 105 is a single Sylow $p$-subgroup for $p=5,7$.
	\end{prb}

	\begin{prb}
	Show that the number of Sylow $p$-subgroups of $\SL_3(\F_p)$ is $(p^2+p+1)(p+1)$.
	\end{prb}

	\subsection{Rings}
	\begin{prb}
	Show that a finite integral domain is a field.
	\end{prb}

	\begin{prb}
	Show that every ring of order $p^2$ for a prime $p$ is commutative.
	\end{prb}

	\begin{prb}
	Show that a semiring with multiplicative identity and cancellative addtion has commutative addition.
	\end{prb}

	\begin{prb}
	Show that the complement of a saturated monoid in a commutative ring is a union of prime ideals.
	\end{prb}

	\subsection{Vector spaces}
	\begin{prb}
	Show that normal nilpotent matrix equals zero.
	\end{prb}

	\begin{prb}
	Show that two matrices $AB$ and $BA$ have same nonzero eigenvalues whose both multiplicities are coincide...
	\end{prb}

	\begin{prb}
	Show that if $A$ is a square matrix whose characteristic polynomial is minimal then a matrix commuting $A$ is a polynomial in $A$.
	\end{prb}

	\begin{prb}
	Show that the order of $2\times 2$ integer matrices divide 12 if it is finite.
	\end{prb}

	\begin{prb}
	Let $X$ be a square matrix. Show that there is another matrix $Y$ such that $X+Y$ is invertible.
	\end{prb}

	\begin{prb}
	Show that a determinant-preserving linear map is rank-preserving.
	\end{prb}




\section{Galois theory}

	\begin{prb}
	Show that the Galois group of a quintic over $\Q$ having exactly three real roots is isomorphic to $S_5$.
	\end{prb}


\section{Category theory}
\section{Commutative algebra}
\section{Representation theory}
\section{Homological algebra}
\section{Discrete mathematics}
\section{Number theory}
	\begin{prb}
	Show that there is no integral solution of the equation $x^7+7=y^2$.
	\end{prb}

	\begin{prb}
	Show that if $(x^2+y^2+z^2)/(xy+yz+zx)$ is an integer, then it is not divided by 3.
	\end{prb}
	
	\begin{prb}
	Show that there is no non-trivial integral solution of $x^4-y^4=z^2$.
	\end{prb}

\section{Algebraic number theory}









\newpage
\part{Geometry and Topology}
\setcounter{section}{0}

\section{Smooth surfaces}

\section{Differential topology}

	\begin{prb}
	Show that the tangent space of the unitary group at the identity is identified with the space of skew Hermitian matrices.
	\end{prb}

	\begin{prb}
	Prove the Jacobi formula for matrix.
	\end{prb}

	\begin{prb}
	Show that $S^3$ and $T^2$ are parallelizable.
	\end{prb}

	\begin{prb}
	Show that $\R P^n=S^n/Z_2$ is orientable if and only if $n$ is odd.
	\end{prb}

\section{Geometric analysis}


\section{Algebraic curves}
\section{Algebraic geometry}
\section{Complex geometry}

\section{Surface topology}
\section{Algebraic topology}
\section{Geometric topology}

\end{document}