\documentclass{../crs}
\usepackage{../../ikany}

\title{Analysis II : General Topology}

\begin{document}
\maketitle
\tableofcontents

\frontmatter
\input{preface}

\mainmatter
\input{ch1}






% CHAPTER 2
\chapter{Continuity}


% SECTION 2-1
\section{Continuous functions}

\subsection{Various continuity}
continuity, Cauchy continuity, uniform continuity, 

Lipschitz continuity
\begin{ex}
An isometry between metric spaces is Lipschitz continuous with costant 1.
\end{ex}

\subsection{Sequential continuity}




\section{Continuous maps}

\subsection{Mono and epi}

\subsection{Subspaces and quotient spaces}

\subsection{Product space}

\subsection{Homeomorphisms}
continuous bijection
open map
how to show two spaces are not homeomorphic
- topological property: connected, compact


\section{Connectedness}

\subsection{Connected spaces}
component
\subsection{Path connected spaces}

\subsection{Locally connected spaces}

\subsection{Homotopy}













\chapter{Convergence}

\section{Nets}

product of two directed sets
projection is monotone final
uniformity is itself an upward directed set by reverse inclusion, like $\R_{\ge0}$.
cofinality and subsequence

eventuality filter, three definitions of subnets

\section{Sequences}
sequential spaces, first countable

\section{Completeness}
completion















\chapter{Compactness}


\begin{defn}
Let $X$ be a topological space.
A \emph{cover} of a subset $A\subset X$ is a collection $\{U_\alpha\}_{\alpha\in\cA}$ of subsets of $X$ such that $A\subset\bigcup_{\alpha\in\cA}U_\alpha$.
If $U_\alpha$ are all open, then it is called \emph{open cover}.
\end{defn}
\begin{defn}
Let $X$ be a topological space.
A subset $K\subset X$ is called \emph{compact} if every open cover of $K$ has a finite subcover.
\end{defn}
\begin{prop}
Let $X$ be a topological space with a basis $\mathcal{B}$.
A subset $K\subset X$ is compact if and only if every cover of the form $\{B_x\in\mathcal{B}\}_{x\in K}$ has a finite subcover.
\end{prop}
\begin{rmk}
Let $\cP$ be a property of a fuction $f\colon X\to Y$, such as continuity
If we say $f$ has $\cP$ at a point $x$, then it would implies that $x$ has a neighborhood $U$ such that 
\end{rmk}

\subsection{Properties of compactness}
\begin{thm}
Let $X$ and $Y$ be topological spaces.
For a continuous map $f\colon X\to Y$, the image $f(K)$ is compact for compact $K\subset X$.
\end{thm}

\begin{rmk}
This is why the term ``compact space'' is widely used.
\end{rmk}

\begin{cor}[The extreme value theorem]
A continuous function on a closed interval has a global maximum and
\end{cor}

Heine-Cantor,



\subsection{Characterizations of compactness}

\begin{rd}[column sep=large,row sep=large]
net compact \ar{d} & sequentially compact \ar{d} & \\
compact \ar{u}\ar{r} & countably compact \ar{r}\lds{l}{\block{metrizable\\\emph{or} 2nd countable}}\rds{u}{sequential} & limit point compact \lds{l}{$T_1$}
\end{rd}






























\chapter{Separation axioms}

\section{Separation axioms}
\section{Metrization theorems}









\chapter{Function spaces}




\section{Compact-open topology}

% 6-1-1
\subsection{Definition}

\begin{defn}
Let $X$ and $Y$ be topological spaces.
The \emph{continuous functions space} $C(X,Y)$ is the set of continuous functions from $X$ to $Y$.
If $Y=\mathbb{R}$ or $\mathbb{C}$, then the continuous function space is denoted by $C(X)$.
\end{defn}

% 6-1-2
\subsection{Compact convergence}
topology of compact convergence
metrizability and hemicompact
topology of uniform convergence
uniform structure of pointwise convergence
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In considering the continuous function space, $Y$ will be assumed to be a metric space because of its usefulness in most applications.
Then, there are two useful topologies on $C(X,Y)$.
Since there is a difficulty to deal with open sets or basis directly in a function space, the convergence will be a reliable alternative to describe the topologies.
Before giving definition of the topologies, define pseudometrics $\rho_K$ on $C(X,Y)$ by
\[\rho_K(f,g)=\sup_{x\in K}d(f(x),g(x))\]
for $K\subset X$ compact.

\begin{defn}
Let $X$ and $Y$ be topological spaces.
The \emph{topology of pointwise convergence} on $C(X,Y)$ is a subspace topology inherited from the product topology on $Y^X$.
\end{defn}

\begin{prop}
Let $X$ be a topological space and $Y$ be a metric space.
The topology of pointwise convergence on $C(X,Y)$ is generated by pseudometrics $\rho_{\{x\}}$, namely all $\{g:d(f(x),g(x))<\e\}$ for $f\in C(X,Y)$, $\e>0$, and $x\in X$.
\end{prop}

\begin{defn}
Let $X$ be a topological space and $Y$ be a metric space.
The \emph{topology of compact convergence} on $C(X,Y)$ is a topology generated by pseudometrics $\rho_K$, namely all $\{g:\rho_K(f,g)<\e\}$ for $f\in C(X,Y)$, $\e>0$, and compact $K\subset X$.
\end{defn}

\begin{prop}
Let $C(X,Y)$ be a continuous function space for a topological space $X$ and a metric space $Y$.
A functional sequence in $C(X,Y)$ converges in the topology of compact convergence if and only if the functional sequence converges compactly.
\end{prop}

\begin{thm}
Let $X$ be a topological space and $Y$ be a metric space.
If $X$ is hemicompact, in other words, $X$ has a sequence of compact subsets $\{K_n\}_{n\in\N}$ such that every compact subset of $X$ is contained in $K_n$ for some $n\in\N$, then the topology of compact convergence on $C(X,Y)$ is metrizable.
\end{thm}

\begin{proof}
bounding and merging pseudometrics
\end{proof}



% 6-1-3
\subsection{Exponentiability}
locally compact Hausdorff spaces
exponential space






$\frac\e3$ argument





% SECTION 6-2
\section{Rings of continuous functions}
\subsection{$C(X), C_0(X), C_b(X)$}



\section{Important theorems on function space}

\subsection{The Arzela-Ascoli theorem}

The Arzela-Ascoli theorem is a main technique to verify compactness of a subspace of continuous function space.
The theorem requires the notion of equicontinuity, which lifts pointwise compactness up onto compactness in topology of compact convergence.

\begin{defn}
Let $X$ be a topological space and $Y$ be a metric space.
A subset $\mathcal{F}\subset C(X,Y)$ is called \emph{(pointwise or locally) equicontinuous} if for every $\e>0$ and each $x_0\in X$, there is an open neighborhood $U$ of $x_0$ such that $x\in U\impl d(f(x),f(x_0))<\e$ for all $f\in\cF$.
\end{defn}
Compare with the following definition:
\begin{defn}
Let $X$ be a metric space and $Y$ be a metric space.
A subset $\mathcal{F}\subset C(X,Y)$ is called \emph{uniformly equicontinuous} if for every $\e>0$ there exists $\delta>0$ such that $d(x,y)<\delta\impl d(f(x),f(y))<\e$ for all $f\in\cF$.
\end{defn}
The uniform equicontinuity is what the Rudin's book says it just equicontinuous.

\begin{thm}[Arzela-Ascoli, conventional version]
Let $X$ be a compact space.
For $(f_n)_{n\in\N}\subset C(X)$, if it is equicontinuous and pointwisely bounded, then there is a subsequence that uniformly converges.
\end{thm}


\begin{thm}[Arzela-Ascoli, metrized version]
Let $X$ be a hemicompact space and $Y$ be a metric space.
Let $\cT_p$ and $\cT_c$ be the topology of pointwise and compact convergence on $C(X,Y)$ relatively.
For $\cF\subset C(X,Y)$, if $\cF$ is equicontinuous and relatively compact in $\cT_p$, then $\cF$ is relatively compact in $\cT_c$.
\end{thm}
\begin{pf}
Let $\{f_n\}_{n\in\N}$ be a sequence in $\cF$ and $K\subset X$ be a compact.
By equicontinuity, for each $k\in\N$ a finite open cover $\{U_s\}_{s\in S_k}$ with a finite set $S_k\subset K$ can be taken such that $x\in U_s\,\impl\,d(f(x),f(s))<\frac1k$ for all $f\in\cF$.
By the pointwise relative compactness, we can extract a subsequence $\{f_m\}_{m\in\N}$ of $\{f_n\}_n$ such that $\{f_m(s)\}_m$ is Cauchy for each $s\in\bigcup_{k\in\N}S_k$ by the diagonal argument.

For every $\e>0$, let $k=\ceil{(\frac\e3)^{-1}}$ and $m_0=\max\{m_{0,s}:s\in S_k\}$ where $m_{0,s}$ satisfies that $m,m'>m_{0,s}\impl d(f_m(s),f_{m'}(s))<\frac\e3$.
By taking $s\in S_k$ such that $x\in U_s$ for arbitrary $x\in K$, we obtain, for $m,m'>m_0$,
\[d(f_m(x),f_{m'}(x))\le d(f_m(x),f_m(s))+d(f_m(s),f_{m'}(s))+d(f_{m'}(s),f_{m'}(x))<\e.\]
Thus, $\{f_m\}_m$ is a subsequence of $\{f_n\}_n$ that is uniformly Cauchy on $K$.
\end{pf}


converse of Arzela-Ascoli




\subsection{The Stone-Weierstrass theorem}








\end{document}












Limiting inequality
dependency diagram
double limit table










